---
title: "COVIDMINDER Example Notebook:"
subtitle: "DAR Fall 2020"
author: "John S. Erickson"
date: "09/01/2020"
output: html_document
---


```{r setup, include=FALSE}
# Set the default CRAN repository
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "../")
```

```{r echo = F, results = 'hide',  warning=FALSE, message=FALSE}
#### Library and Data Imports ####

## Load essential R packages
source("modules/Source.R")

## Load stored data (see `data` subdirectory)
source("modules/data_load.R")

## Create dataframes; perform desparity index calcuations; prep for plotting
source("modules/preprocessing.R")

```

## INTRODUCTION

This R Notebook and its related R scripts provide a very basic introduction to the **COVIDMINDER** application, which you can find at:

* Public "production" version: https://covidminder.idea.rpi.edu/

The github repository for all the code required for this notebook, including a snapshot of the **COVIDMINDER** application, can be found at:

* https://github.com/TheRensselaerIDEA/COVID-Notebooks

The **COVIDMINDER** github repository can be found at:

* https://github.com/TheRensselaerIDEA/COVIDMINDER

**NOTE:** To contribute or submit to these repositories you must have a github.com ID and must send it to John Erickson at `erickj4@rpi.edu`. **PLEASE DO THIS IMMEDIATELY BEFORE READING ANY FURTHER!!**

## DARL Assignment: CLONING A NOTEBOOK AND UPDATING THE REPOSITORY

In this assignment we're asking you to...

* clone the `COVID-Notebook` github repository...
* create a personal branch using git, and...
* make additions to the repository by creating a new, customized notebook. 

The instructions which follow explain how to accomplish this. 

**For DAR Fall 2020** you *must* be using RStudio Server on the IDEA Cluster. Instructions for accessing "The Cluster" appear at the end of this notebook. Don't forget to send your github ID to `erickj4@rpi.edu` 

The recommended procedure for cloning and using this repository is as follows:

* Access the RPI network via VPN	
    * See https://itssc.rpi.edu/hc/en-us/articles/360008783172-VPN-Connection-and-Installation for information

* Access RStudio Server on the IDEA Cluster at http://lp01.idea.rpi.edu/rstudio-ose/
    * You must be on the RPI VPN!!
* Access the Linux shell on the IDEA Cluster by clicking the **Terminal** tab of RStudio Server. `cd` into your home (login) directory using: `cd ~`
    * Advanced users may use `ssh` to directly access the Linux shell
* `git clone https://github.com/TheRensselaerIDEA/COVIDMINDER.git` in your `home` directory, resulting in a new directory `COVIDMINDER`
* In the Linux shell, `cd` to `COVIDMINDER/DAL-2020-Notebooks` 
* In the Linux shell, `git checkout -b hacl-yourrcs` where `yourrcs` is your RCS id
    * For example, if your RCS is `erickj4`, your new branch should be `hacl-erickj4`
    * It is critical that you include your RCS id in your branch id
* In the RStudio Server UI, navigate to the `COVIDMINDER/DARL-2020-Notebooks` directory via the **Files** panel
    * Set this to be your R working directory (under "More" menu)
* **REQUIRED**: 
    * Make a <b>copy</b> of this notebook (ie `covid-notebook-hacl.Rmd`) file using a *new, original, descriptive* filename that **includes your RCS ID!**
    * Edit your new notebook; save
    * Use the RStudio `knit` comment to creat an HTML file; repeat as necessary
    * In Linux, `git add` each new file you want to add to the repository, esp. your new `Rmd` file and the `html` you created when you knitted
    * When you're ready, in Linux: `git commit -a -m "some comment"` where "some comment" is a useful comment describing your changes
    * Finally, `git push origin hacl-yourrcs` (where `hacl-yourrcs` is the branch you're working on) 
* **REQUIRED**: On github, select your branch (from the branch drop-down) and submit a pull request.

**REQUIRED:** For this assignment you will be asked to confirm the following in LMS:

    * The location of the github:
    * Your github ID:
    * The name of your new branch:
    * The location where you committed your new (copied) notebook:

Please also see this handy github "cheatsheet": https://education.github.com/git-cheat-sheet-education.pdf

## UNDERSTANDING THE DATA

* All of the data used for this notebook and the **COVIDMINDER** app is located in the `data/` directory hierarchy, mostly under `data/csv/` and `data/csv/time_series/`
* Feel free to browse the directory tree using RStudio or on the web via github
* Most of the nationwide data is under `data/csv`
* Most of the nationwide time series data and New York per-county data is under `data/csv/time_series/`
    * This layout may change
* We will be expanding our data archive, esp. using social determinatns data from <b>County Health Rankings</b>
    * See https://www.countyhealthrankings.org/explore-health-rankings/measures-data-sources/2020-measures 

## WHAT SHOULD I WORK ON?!?!?

* Choose an existing issue: https://github.com/TheRensselaerIDEA/COVIDMINDER/issues
    * Ask questions about the issue in the "Comments" section of that issue
    * "Claim" the issue by self-assigning 
* OR, create your own issue; click "New Issue"
* OR, ask Prof. Bennett or Dr. Erickson for an issue to work on!

## HOW TO SHARE YOUR WORK OR ASK QUESTIONS

* For class-related questions, use the `data-incite-2020` slack channel under The Rensselaer IDEA
* For COVIDMINDER questions use the `idea_covidminder` stack channel 
    * Contact Dr. Erickson to be added (if you haven't already)

## WHAT TO INCLUDE IN YOUR NOTEBOOK
* The code in your notebook should be well commented
* You should include thorough discussions of your methods and explanations of your results in the **markdown** sections (the non-code sections)
* You should always include enough detail for someone else to reproduce (and re-use!) your work!
* **ALWAYS* include useful titles and legends for your plots and tables!
* Nicely-formatted tables are always a bonus
* Your "default" for knitting notebooks should be HTML; this makes it easier to view and reduces errors. 

<hr>

```{r echo = F, results = 'hide',  warning=FALSE, message=FALSE}
### Text used for captions and explanations

ldi_explanation_text <- "<h4><b>EXPLANATION OF VISUALIZATIONS:</b></h4> The goal of these visualizations is to examine 
nationwide disparities in COVID-19 factors having to do with risks, mediations (e.g. testing, hospital beds), 
and outcomes (e.g. deaths, cases). A common measure, the <i>disparity index</i> is used to represent the 
difference between the observed rate in the state and some baseline rate.</p>
<p>The advantage of the disparity index is that represents how far off a target standard the observed rate is. </p>
<p>Mathematically,
<code>DI = log(x/y)</code> or <code>DI = log(y/x)</code>
depending upon whether being above or below the target is preferred. 
<ul>
<li>In the case of hospital beds or rate of testing, <i>x</i> would be some state's rate , and <i>y</i> would be the US rate or some rate 
we're comparing against (e.g. South Korea's testing or Italy's hospital beds).</li>
<li>In the case of mortality rates, <i>x</i> would be the target rate (e.g. some national rate, including the US), and <i>y</i> would be the individual state's rate.</li>
</ul>
</p>
<p>&nbsp;</p>"

rpi_accessibility_link <- "<div class='center'><p><a href='https://info.rpi.edu/statement-of-accessibility'>Rensselaer Statement of Accessibility</a></p></div>"

### OUTCOMES: COVID-19 Mortality Rates (USA)
us_mortality_rates_text <- "<h4><b>How do COVID-19 mortality rates compare across the United States?</b></h4>
<i>This map compares the COVID-19 mortality rates of individual states with the US rate.
This map is updated daily.</i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
state's COVID-19 mortality rate is higher than the US rate<br><br> 
Data source: <a href='https://bit.ly/3dMWRP6'>JHU daily reports</a> (04-07-2020)"

### MEDIATION: COVID-19 Testing (USA)

us_testing_rates_text <- "<h4><b>How do COVID-19 testing rates across the US compare with South Korea?</b></h4>
<i>This map compares rates of COVID-19 tssting in US states vs South Korea's testing rate. 
This map is updated daily.</i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
state's testing rate is lower than the South Korean rate<br><br>
Data source: <a href='https://covidtracking.com/api'>The COVID Tracking Project daily reports</a> (04-07-2020)"

### MEDIATION: Hospital Beds (USA)

us_hospital_beds_text <- "<h4><b>How does the availability of hospital beds across the United States compare with Italy?</b></h4>
<i>This map compares the availability of hospital beds in US states vs the rate in Italy (3.2 beds/1000). 
This map uses recent historical figures and does not reflect 'surge' capacity.</i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
state's hospital bed availablity is lower than the rate in <b>Italy</b><br/><br>
Data sources: <br/><a href='https://data.oecd.org/healtheqt/hospital-beds.htm'> Organisation for Economic Co-operation and Development</a>
and <a href='https://bit.ly/2V0CYLU'>Kaiser Family Foundation</a>"

### DETERMINANT: Cardiovascular Diseases (USA)

us_cardio_deaths_rates_text <- "<h4><b>How do cardiovascular mortality rates across the US compare with the national average?</b></h4>
<i>The map compares individual state mortality rates related to cardiovascular diseases (per 100k)
with the US rate. In recent literature, COVID-19 risk has been
linked to certain cardiovascular diseases, including hypertension. 
This map uses recent historical figures. </i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
state's mortality rate from total cardiovascular diseases is 
<b>higher</b> than the US rate<br/><br>
Data source: <br/><a href='https://bit.ly/2V1Zl3I'>CDC (2017)</a>"

us_diabetes_text <- "<div style='font-weight:bold;line-height:1.3;'>
Determinant: What are the disparities between states in rate of diabetes patients 
per 100k population per state when compared to the average United States rate? </div><br>
<div style='font-size:90%;line-height:1.2;'>
Diabetes puts patients at increased risk of contracting and dying from COVID-19, 
so areas with higher diabetes rates may face increased COVID-19 burdens. <br><br>
The  rate of diabetes deaths per 100k in a state is<br>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #BD0026; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> Higher</strong> than US avg. rate for disparity index &gt; 0.2</div>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #ffffff; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> About equal</strong> to US avg. rate for -0.2 &lt;disparity index &lt; 0.2</div>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #253494; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> Lower</strong> than US avg. rate for disparity index &lt; -0.2</div>
<i>Darker shades indicate greater disparity.</i><br><br>
<strong>Diabetes Rate</strong> = number of diabetic patients per 100K population <br>
<strong>Diabetes Disparity Index</strong> = log(Diabetes Rate in state/average Diabetes Rate in US)<br>
<strong>Date: </strong> 2020<br><br>
<b>DATA SOURCE:</b> <a href='https://bit.ly/34mYLBP'>County Health Rankings</a> and 
<a href='https://bit.ly/2V1Zl3I'>CDC</a><br>
</div>"
                            
NY_diabetes_text <- "<div style='font-weight:bold;line-height:1.3;'>
Determinant: What are the disparities between New York counties in the rate 
of diabetes patients per 100k population when compared to the average United 
States rate?</div><br>
<div style='font-size:90%;line-height:1.2;'>
Diabetes puts patients at increased risk of contracting and dying from COVID-19, 
so areas with higher diabetes rates may face increased COVID-19 burdens. <br><br>
The  rate of diabetes patients per 100k in a county  is<br>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #BD0026; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> Higher</strong> than US avg. rate for disparity index &gt; 0.2</div>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #ffffff; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> About equal</strong> to US avg. rate for -0.2 &lt; disparity index &lt; 0.2</div>
<div>&nbsp;&nbsp;&nbsp;<span style='background: #253494; border-radius: 50%; font-size: 11px; opacity: 0.7;'>&nbsp&nbsp&nbsp&nbsp</span><strong> Lower</strong> than US avg. rate for disparity index &lt; -0.2</div>
<i>Darker shades indicate greater disparity.</i><br><br>
<strong>Diabetes Rate</strong> = number of diabetic patients  per 100K population <br>
<strong>Diabetes Disparity Index</strong> = log(Diabetes Rate in state/average Diabetes Rate in US)<br>
<strong>Date: </strong> 2020<br><br>
<b>DATA SOURCE:</b> <a href='https://bit.ly/34mYLBP'>County Health Rankings</a> and 
<a href='https://bit.ly/2V1Zl3I'>CDC</a><br>
</div>"

### OUTCOME: COVID-19 mortality rates (NY)

NY_mortality_rates_text <- "<h4><b>How do COVID-19 mortality rates compare across New York State?</b></h4>
<i>This map compares the COVID-19 mortality rates of NY counties with the NY average. 
This map is updated daily. </i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
county's COVID-19 mortality rate is higher than the NY rate.<br>
Data source: <a href='https://bit.ly/3dMWRP6'>JHU daily reports</a> (04-06-2020)"

### OUTCOME: COVID-19 Cases (NY)

NY_covid_cases_text <- "<h4><b>How do COVID-19 cases compare across New York State?</b></h4>
<i>This map compares the COVID-19 cases for NY counties with the NY average. 
This map is updated daily. </i><br><br>
Here, <span style='color:#b2182b'><b>shades of red</b></span> indicate that a 
county's COVID-19 case count is higher than the NY rate.<br>
Data source: <a href='https://bit.ly/3dMWRP6'>JHU daily reports</a> (04-06-2020)"

### OUTCOME: COVID-19 Cases Time Series (NY)

NY_covid_cases_TS_text <- "<h4><b>How have COVID-19 cases increased across New York State?</b></h4>
<i>This plot shows the growth of COVID-19 cases across NY counties since early 2020. 
This data is updated daily. </i><br><br>
Mouse over the plot to identify individual counties.<br>
Data source: <a href='https://bit.ly/3dMWRP6'>JHU daily reports</a> (04-06-2020)"

```

`r ldi_explanation_text`

`r us_mortality_rates_text`

```{r echo = F}
    colors <- c("grey","#426C85","#67a9cf","#d1e5f0","#f7f7f7","#fddbc7","#ef8a62","#b2182b")
    bins <- c(5, 2, 1, .2, -.2, -1, -2, -5,-Inf)
    pal2 <- leaflet::colorBin(colors, domain = states$Mortality_rate_ldi, bins = bins, reverse=FALSE)
    labels2 <- sprintf(
      "<strong>%s</strong><br/>
      COVID-19 Mortality Rate DI: %.2g",
      states$NAME, states$Mortality_rate_ldi
    ) %>% lapply(htmltools::HTML)
    
    leaflet(states.shapes) %>%
      setView(-96, 37.8, 4) %>% 
      addPolygons(
        fillColor = ~pal2(states$Mortality_rate_ldi),
        weight = 2,
        opacity = 1,
        color = "white",
        dashArray = "3",
        fillOpacity = 0.7,
        highlight = highlightOptions(
          weight = 5,
          color = "#666",
          dashArray = "",
          fillOpacity = 0.7,
          bringToFront = TRUE),
        label = labels2,
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>% 
      addLegend(pal = pal2, 
                values = ~states$Mortality_rate_ldi, 
                opacity = 0.7, 
                title = "Disparity Index<br/>US COVID-19 Mortality Rates",
                position = "bottomright"
                ) %>%
      addProviderTiles("MapBox", options = providerTileOptions(
        id = "mapbox.light",
        accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
```

  `r us_testing_rates_text` 

```{r echo = F}
    country <- "US"

    # modify states to have selected columns for our plot
    Testing_rate_ldi <- states %>% 
      select(starts_with("Testing_rate_ldi")) 
    
    states <- data.frame(states, "Testing_rate_ldi"=unlist(Testing_rate_ldi)) # Append to states
    
    colors <- c("#253494","#4575B4", "#74ADD1","#ABD9E9","#f7f7f7","#FDAE61","#F46D43", "#D73027", "#BD0026")
    bins <- c(5, 3, 2, 1, .2, -.2, -1, -2, -3, -5)
    pal2 <- leaflet::colorBin(colors, domain = states$Testing_rate_ldi, bins = bins, reverse=TRUE)
#    browser()
    labels2 <- sprintf(
      paste0("<strong>%s</strong> State<br/>
      Testing Rate vs ", toupper(country)," DI: %.2g<br>
      Testing Rate: %.1f /1000"),
      states$NAME, states$Testing_rate_ldi, states$tests_per_1000*1000
    ) %>% lapply(htmltools::HTML)
    
    leaflet(states.shapes) %>%
      setView(-96, 37.8, 4) %>% # TODO: Doesn't seem to do anything
      addPolygons(
        fillColor = ~pal2(states$Testing_rate_ldi),
        weight = 1,
        opacity = 1,
        color = "#330000",
        dashArray = "1",
        fillOpacity = 0.7,
        highlight = highlightOptions(
          weight = 5,
          color = "#666",
          dashArray = "",
          fillOpacity = 0.7,
          bringToFront = TRUE),
        label = labels2,
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>% 
      addLegend(pal = pal2, 
                values = ~states$Testing_rate_ldi, 
                opacity = 0.7, 
                title = paste0("Disparity Index<br/>US Total Tests vs. ",toupper(country)),
                position = "bottomright",
                labFormat = function(type, cuts, p) { n = length(cuts) 
                   cuts[n] = paste0(cuts[n]," lower") 
                   # for (i in c(1,seq(3,(n-1)))){cuts[i] = paste0(cuts[i],"—")} 
                   for (i in c(1,seq(2,(n-1)))){cuts[i] = paste0(cuts[i]," — ")} 
                   cuts[2] = paste0(cuts[2]," higher") 
                   paste0(str_remove(cuts[-n],"higher"), str_remove(cuts[-1],"—"))
                }
                ) %>%
      addProviderTiles("MapBox", options = providerTileOptions(
        id = "mapbox.light",
        accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
```

  `r us_cardio_deaths_rates_text` 

```{r echo = F}

# UPDATED: 28 April 2020
    colors <- c("#253494","#4575B4", "#74ADD1","#ABD9E9","#f7f7f7","#FDAE61","#F46D43", "#D73027", "#BD0026")
    bins <- c(5, 3, 2, 1, .2, -.2, -1, -2, -3, -5)
    pal2 <- leaflet::colorBin(colors, domain = states$cardio_death_rate_BNH_ldi, bins = bins, reverse=FALSE)
    labels2 <- sprintf(
      "<strong>%s</strong><br/>
      Heart Disease Death Rate DI (BNH): %.2g<br/>
      Heart Disease Death Rate (BNH): %.1f per 100k",
      states$NAME, states$cardio_death_rate_BNH_ldi, states$cardio_deaths_p_Black_Non_Hispanic
    ) %>% lapply(htmltools::HTML)
    
    leaflet(states.shapes) %>%
      setView(-96, 37.8, 4) %>% 
      addPolygons(
        fillColor = ~pal2(states$cardio_death_rate_BNH_ldi),
        weight = 1,
        opacity = 1,
        color = "#330000",
        dashArray = "1",
        fillOpacity = 0.7,
        highlight = highlightOptions(
          weight = 5,
          color = "#666",
          dashArray = "",
          fillOpacity = 0.7,
          bringToFront = TRUE),
        label = labels2,
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>% 
      addLegend(pal = pal2, 
                values = ~states$cardio_death_rate_BNH_ldi, 
                opacity = 0.7, title = "Disparity Index<br/>US Heart Disease Death Rate (BNH)",
                position = "bottomright",
                labFormat = function(type, cuts, p) { n = length(cuts) 
                cuts[n] = paste0(cuts[n]," lower") 
                # for (i in c(1,seq(3,(n-1)))){cuts[i] = paste0(cuts[i],"—")} 
                for (i in c(1,seq(2,(n-1)))){cuts[i] = paste0(cuts[i]," — ")} 
                cuts[2] = paste0(cuts[2]," higher") 
                paste0(str_remove(cuts[-n],"higher"), str_remove(cuts[-1],"—"))
                }) %>%
      addProviderTiles("MapBox", options = providerTileOptions(
        id = "mapbox.light"))
    #Remove personal API key

```

  `r us_hospital_beds_text` 

```{r echo = F}

# UPDATED: 28 Apr 2020
    colors <- c("#253494","#4575B4", "#74ADD1","#ABD9E9","#f7f7f7","#FDAE61","#F46D43", "#D73027", "#BD0026")
    bins <- c(5, 3, 2, 1, .2, -.2, -1, -2, -3, -5)
    pal2 <- leaflet::colorBin(colors, domain = states$hosp_beds_ldi, bins = bins, reverse=TRUE)
    labels2 <- sprintf(
      "<strong>%s</strong><br/>
      Hospital Beds vs Italy DI: %.2g",
      states$NAME, states$hosp_beds_ldi
    ) %>% lapply(htmltools::HTML)
    
    leaflet(states.shapes) %>%
      setView(-96, 37.8, 4) %>% 
      addPolygons(
        fillColor = ~pal2(states$hosp_beds_ldi),
        weight = 1,
        opacity = 1,
        color = "#330000",
        dashArray = "1",
        fillOpacity = 0.7,
        highlight = highlightOptions(
          weight = 5,
          color = "#666",
          dashArray = "",
          fillOpacity = 0.7,
          bringToFront = TRUE),
        label = labels2,
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>% 
      addLegend(pal = pal2, 
                values = ~states$hosp_beds_ldi, 
                opacity = 0.7, 
                title = "Disparity Index<br/>US Hospital Beds vs Italy",
                position = "bottomright",
                labFormat = function(type, cuts, p) { n = length(cuts) 
                cuts[n] = paste0(cuts[n]," lower") 
                # for (i in c(1,seq(3,(n-1)))){cuts[i] = paste0(cuts[i],"—")} 
                for (i in c(1,seq(2,(n-1)))){cuts[i] = paste0(cuts[i]," — ")} 
                cuts[2] = paste0(cuts[2]," higher") 
                paste0(str_remove(cuts[-n],"higher"), str_remove(cuts[-1],"—"))
                }
                ) %>%
      addProviderTiles("MapBox", options = providerTileOptions(
        id = "mapbox.light"))

    
```


`r NY_covid_cases_TS_text` 

```{r echo=F}

    # selected.region <- input$NYRegion
    selected.region <- "All Regions"
    # select.size <- 2
    if (selected.region == "All Regions") {
      selected.region <- NY_counties_regions$Region
      select.size <- 1
    }
    highlight_points <- covid_NY_TS_plot.cases %>% 
      dplyr::filter( 
        County == "Albany" & date == as.Date("2020-04-26") |
          # County == "Allegany" & date == as.Date("2020-03-29") |
          County == "Bronx" & date == as.Date("2020-04-25") |
          County == "Broome" & date == as.Date("2020-04-12") |
          # County == "Cattaraugus" & date == as.Date("2020-03-30") |
          County == "Cayuga" & date == as.Date("2020-04-12") |
          County == "Chautauqua" & date == as.Date("2020-04-10") |
          # County == "Chemung" & date == as.Date("2020-04-10") |
          County == "Chenango" & date == as.Date("2020-04-12") |
          County == "Clinton" & date == as.Date("2020-04-26") |
          # County == "Columbia" & date == as.Date("2020-03-29") |
          County == "Cortland" & date == as.Date("2020-04-25") |
          # County == "Delaware" & date == as.Date("2020-04-02") |
          County == "Dutchess" & date == as.Date("2020-04-12") |
          County == "Erie" & date == as.Date("2020-04-02") |
          # County == "Essex" & date == as.Date("2020-04-10") |
          # County == "Franklin" & date == as.Date("2020-04-10") |
          # County == "Fulton" & date == as.Date("2020-04-12") |
          County == "Genesee" & date == as.Date("2020-04-26") |
          # County == "Greene" & date == as.Date("2020-03-29") |
          County == "Hamilton" & date == as.Date("2020-04-25") |
          County == "Herkimer" & date == as.Date("2020-04-12") |
          # County == "Jefferson" & date == as.Date("2020-03-30") |
          County == "Kings" & date == as.Date("2020-04-12") |
          # County == "Lewis" & date == as.Date("2020-04-10") |
          # County == "Livingston" & date == as.Date("2020-04-10") |
          County == "Madison" & date == as.Date("2020-04-12") |
          # County == "Monroe" & date == as.Date("2020-03-26") |
          # County == "Montgomery" & date == as.Date("2020-03-29") |
          County == "Nassau" & date == as.Date("2020-04-15") |
          County == "New York" & date == as.Date("2020-04-10") |
          County == "New York State" & date == as.Date("2020-04-12") |
          County == "Manhattan" & date == as.Date("2020-04-10") |
          County == "Niagara" & date == as.Date("2020-04-12") |
          County == "Oneida" & date == as.Date("2020-04-10") |
          County == "Onondaga" & date == as.Date("2020-04-10") |
          # County == "Ontario" & date == as.Date("2020-04-12") |
          County == "Orange" & date == as.Date("2020-04-18") |
          County == "Orleans" & date == as.Date("2020-04-01") |
          County == "Oswego" & date == as.Date("2020-04-25") |
          County == "Otsego" & date == as.Date("2020-04-12") |
          County == "Putnam" & date == as.Date("2020-04-20") |
          County == "Queens" & date == as.Date("2020-04-12") |
          County == "Rensselaer" & date == as.Date("2020-04-10") |
          County == "Richmond" & date == as.Date("2020-04-11") |
          County == "Rockland" & date == as.Date("2020-04-12") |
          County == "St. Lawrence" & date == as.Date("2020-04-26") |
          County == "Saratoga" & date == as.Date("2020-04-01") |
          County == "Schenectady" & date == as.Date("2020-04-25") |
          County == "Schoharie" & date == as.Date("2020-04-12") |
          County == "Schuyler" & date == as.Date("2020-04-10") |
          County == "Seneca" & date == as.Date("2020-04-12") |
          # County == "Steuben" & date == as.Date("2020-04-10") |
          County == "Suffolk" & date == as.Date("2020-04-10") |
          County == "Sullivan" & date == as.Date("2020-04-12") |
          # County == "Tioga" & date == as.Date("2020-03-26") |
          County == "Tompkins" & date == as.Date("2020-04-10") |
          County == "Ulster" & date == as.Date("2020-04-20") |
          # County == "Warren" & date == as.Date("2020-04-02") |
          # County == "Washington" & date == as.Date("2020-03-30") |
          # County == "Wayne" & date == as.Date("2020-04-02") |
          County == "Westchester" & date == as.Date("2020-04-10") |
          # County == "Wyoming" & date == as.Date("2020-04-10") |
          County == "Yates" & date == as.Date("2020-04-12")
      )
    
    NY_region_palette.df <- NY_counties_regions %>%
      dplyr::select(Region,Color) %>% 
      dplyr::distinct(Region,Color)
    
    NY_region_palette <- setNames(as.character(NY_region_palette.df$Color), as.character(NY_region_palette.df$Region))
    
    covid_NY_TS_plot.cases %>%
      ggplot(aes(date, 
                 cases, 
                 color = Region,
                 group=County)) +
      scale_color_manual(values=NY_region_palette) +
      geom_line(size=1) +
      scale_y_continuous(
        trans = "log10",
        breaks = c(10,100,500,1000,5000,10000, 50000)
      ) +
      scale_x_datetime(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%b %d") +
      ylab("Cumulative Number of Cases") + 
      ggtitle("New York State COVID-19 Cases per County (Mar-Apr 2020)")  +  
      gghighlight(NY_counties_regions[NY_counties_regions$County %in% County,"Region"] %in% selected.region, use_direct_label=FALSE) +
      geom_line(size=select.size) + 
      geom_label_repel(data=highlight_points,  aes(label=County), box.padding = unit(1.75, 'lines')) +
      # coord_cartesian(xlim = ranges$x, ylim = ranges$y, expand = FALSE) +
      geom_vline(aes(xintercept=as_datetime("2020-03-20"), linetype="Gov. Cuomo issues stay-at-home order"), color = "black") + 
      scale_linetype_manual(name = "Events", 
                            values = c(2), 
                            guide = guide_legend(override.aes = list(color = c("black")))) +
      NULL


```

## Accessing RStudio Server on the IDEA Cluster

The IDEA Cluster provides five compute nodes (4x 48 cores, 1x 80 cores, 1x storage server)

* RCS credentials (via registration in class); email John Erickson for problems `erickj4@rpi.edu`
* RStudio, Jupyter, MATLAB, GPUs (on two nodes); lots of storage and computes
* Access via RPI physical network or VPN only

RStudio GUI Access:

* http://lp01.idea.rpi.edu/rstudio-ose/  or http://lp01.idea.rpi.edu/rstudio-ose-3/ (RStudio)
* Linux terminal accessible from within RStudio "Terminal" or via ssh (below)

Shared Data on Cluster:

* All idea_users have access to shared storage via `/data` ("data" in your home directories)
* Shell access to nodes: You must access "landing pad" first, then compute node:
* `ssh your_rcs@lp01.idea.rpi.edu`  For example: `ssh erickj4@lp01.idea.rpi.edu`
* Then, `ssh` to the desired compute node, e.g.: `ssh idea-node-02`
