---
title: "CDC imputation Notebook"
output: html_notebook
---

Introduction:

We will impute the determinant matrix directly, using the package `Amelia` (Explanation in Appendix), which can help us to set the bounds of each determinant. However, we don't know the bounds for each determinant exactly, so the imputed determinants matrix may not be useful. But we impute them anyway and set the bound of each determinant to their existing range.
We do the Amelia fitting, and produce 2 imputed output get mean as final result. If both imputation fails, replace it by state mean or random rate that is closer to other non-missing mortality rates in this county. If one imputation fails, use the success one.
The function will finally return a calculated R data with the same format as the input data.


Start of imputation part:

Functions:

cdc.mort.mat:
for cdc data if state not declared, tmp is state data, else use all data, 
drop all trash data (county fips is zero)
use only county_fips, death_rate and period
change matrix for calculation:
  county_fips, death_rate, period               county_fips period1 period2
a                                             a    
b                                    =====>   b  
c                                             c 




```{r}
cdc.mort.mat <- function(cdc.data.long, state.abbr, death.cause = "Despair") {
  
  tmp <- cdc.data.long
  if (state.abbr != "ALL") {
    tmp <- dplyr::filter(cdc.data.long, state_abbr == state.abbr)
  }
  
  dplyr::filter(tmp, death_cause == death.cause) %>%
    tidyr::drop_na(county_fips) %>%
    dplyr::select(county_fips, death_rate, period) %>%
    tidyr::spread(key = period, value = death_rate) %>%
    dplyr::arrange(county_fips)
}
```


cdc.mort.state.mat:
same as cdc.mort.mat

```{r}
cdc.mort.state.mat <- function(cdc.data.state.long, state.abbr, death.cause = "Despair") {
  
  tmp <- cdc.data.state.long
  if (state.abbr != "ALL") {
    tmp <- dplyr::filter(cdc.data.state.long, state_abbr == state.abbr)
  }
  
  dplyr::filter(tmp, death_cause == death.cause) %>%
    tidyr::drop_na(state_fips) %>%
    dplyr::select(state_fips, state_abbr, death_rate, period) %>%
    tidyr::spread(key = period, value = death_rate) %>%
    dplyr::arrange(state_fips)
}
```

cdc.pop.mat:
In order to get population 

```{r}
cdc.pop.mat <- function(cdc.data.long, state.abbr, death.cause = "Despair") {
  tmp <- cdc.data.long
  if (state.abbr != "ALL") {
    tmp <- dplyr::filter(cdc.data.long, state_abbr == state.abbr)
  }
}
```



cdc.impute:
arguments:
1 cdc.data.long: R data get from Loader_CDC.R
2 cdc.data.state.long: R data get from Loader_CDC.R
3 state.abbr: "All" or abbreviate of a state
4 death.cause

Amelia:
low bound: 0
high_bound: random(0~9)/(population*10^5) if population is NA set it to Inf
calculate times: 2





```{r}
cdc.impute <- function(cdc.data.long, cdc.data.state.long, state.abbr, death.cause = "Despair") {
  
  # > cdc.data.wide <- cdc.mort.mat(cdc.data, "ALL", "Despair")
  # > cdc.supp.wide <- cdc.pop.mat(cdc.data, "ALL", "Despair")
  # > cdc.data.state.wide <- cdc.mort.state.mat(cdc.data.despair.state, "ALL", "Despair")
  
  cdc.data.wide <- cdc.mort.mat(cdc.data.long, state.abbr, death.cause)
  cdc.data.wide[is.na(cdc.data.wide)] <- NaN
  
  cdc.supp.wide <- cdc.pop.mat(cdc.data.long, state.abbr, death.cause)
  
  cdc.data.state.wide <- cdc.mort.state.mat(cdc.data.state.long, state.abbr, death.cause)
  
  county.data <- unique( cdc.data %>% 
    dplyr::select(state_name, state_abbr, county_name, county_fips, urban_2013) 
    )
  
  rownames(cdc.data.state.wide) <- cdc.data.state.wide$state_abbr
  
  hi_bound <- as.data.frame(matrix(Inf, nrow=nrow(cdc.data.wide), ncol=6))   # fips as row ,period as col
  
  colnames(hi_bound) <- colnames(cdc.data.wide)[-1] 
  rownames(hi_bound) <- cdc.data.wide$county_fips
  
  random1 <- hi_bound
  random2 <- hi_bound
  
  set.seed(123)
  
  miss_index <- which(is.na(cdc.data.wide[,-1]),arr.ind=TRUE)
  get_pop_index <- t(matrix(c(0,8), nrow=ncol(miss_index), ncol=nrow(miss_index)))
  hi_bound[miss_index] <- 
    dplyr::if_else( is.na(cdc.supp.wide[(miss_index+get_pop_index)]), Inf,
                    9 / as.numeric( cdc.supp.wide[(miss_index+get_pop_index)] ) * 10^5)
    
  random1[miss_index] <- 
    dplyr::if_else( is.na(cdc.supp.wide[(miss_index+get_pop_index)]), Inf,
                    sample(c(0:9), 1, replace=TRUE) / 
                      as.numeric( cdc.supp.wide[(miss_index+get_pop_index)] ) * 10^5)

  random2[miss_index] <- 
    dplyr::if_else( is.na(cdc.supp.wide[(miss_index+get_pop_index)]), Inf,
                    sample(c(0:9), 1, replace=TRUE) / 
                      as.numeric( cdc.supp.wide[(miss_index+get_pop_index)] ) * 10^5)
  
  # imputation
  
  cdc.states.split <- split(cdc.data.wide, cdc.supp.wide$state_abbr) #splite by state
  
  complt.df <- data.frame()
  
  # for each state
  for (i in 1:length(cdc.states.split)) {
    
    state_name <- names(cdc.states.split[i])
    state <- cdc.states.split[[i]]
    rownames(state) <- state$county_fips
    
    # category a) complete informations
    
    complt <- state[complete.cases(state), -1]
    
    # category b) have missing value and have more than 4 valid value
    
    part <- state[ !complete.cases(state) & rowSums(is.na(state)) <= 4 , -1] 
    
    state_mean <- cdc.data.state.wide[state_name,c(-1,-2)]
    
    #if (nrow(complt) == nrow(state)) {
    #  complt.df <- rbind(complt.df, complt)
    #  next
    #}
    
    if (nrow(part) > 0) {
      for (j in 1:nrow(part)) {
        county <- part[j,]
        complt <- rbind(complt, county)
        
        miss_i <- which(is.na(county))
        lo_bound <- rep(0, length(miss_i))
        up_bound <- as.numeric(hi_bound[rownames(county), miss_i])

        bound <- cbind(miss_i, lo_bound, up_bound)
        
        county_nonmiss_mean <- rowMeans(county[,-miss_i])
        
        amelia_impute <- Amelia::amelia(complt, m=2, parallel="multicore", bounds=bound, p2s=0)
        amelia_out1 <- amelia_impute$imputations$imp1
        amelia_out2 <- amelia_impute$imputations$imp2
        
        amelia_list <- list(amelia_out1, amelia_out2)
        
        amelia_result <- Reduce("+", amelia_list) / length(amelia_list)
        
        # If both imputation fails, replace it by state mean or random rate that is closer
        # to other non-missing mortality rates in this county
        if (length(amelia_result) == 0) {
          
          less_i <- which( is.na(complt[rownames(county),]) &
                           (state_mean <= hi_bound[rownames(county),]) )
          random_i <- which( is.na(complt[rownames(county),]) &
                             (state_mean > hi_bound[rownames(county),]) )
          
          complt[rownames(county),less_i] <- state_mean[,less_i]
          
          complt[rownames(county),random_i] <- 
            sapply(rbind(random1[rownames(county),], random2[rownames(county),]), 
                   function(x) {
                     x[ which( abs(x-county_nonmiss_mean) == 
                                 min(abs(x-county_nonmiss_mean) ) ) ]
                   }
            )[random_i]
        }
        # If one of the imputations failed, use the successful one
        else if (xor(length(amelia_out1) == 1, length(amelia_out2) == 1)) {
          if (length(amelia_out1) == 1){
            amelia_result <- amelia_out2
          }
          else{
            amelia_result <- amelia_out1
          }
          complete <- amelia_result
        }
        # If both imputations succeed, use the mean output
        else {
          complt <- amelia_result
        }
      }
    }

    # category c)
    
    miss_more <- state[ rowSums(is.na(state)) > 4 , -1] 
    
    if (nrow(miss_more) > 0) {
      for (k in 1:nrow(miss_more)) {
        county <- miss_more[k,]
        less_i <- which( is.na(county) & 
                           (state_mean <= hi_bound[rownames(county),]) )
        random_i <- which( is.na(county) & 
                             (state_mean > hi_bound[rownames(county),]) )
        county[,less_i] <- state_mean[,less_i]
        county[,random_i] <- 
          colMeans(rbind(random1[rownames(county),], 
                         random2[rownames(county),])
          )[random_i]
        complt <- rbind(complt, county)
      }
    }
    
    complt.df <- rbind(complt.df, complt)
    print(i)
  }
    
  final.df <- 
    
    # combine all info for counties (fips, state, death_num, population, etc.)
    dplyr::mutate(complt.df,county_fips = rownames(complt.df)) %>% 
    dplyr::inner_join(dplyr::select(cdc.supp.wide, -state_abbr), by="county_fips") %>%
    dplyr::inner_join(county.data, by="county_fips") %>% 
    
    # before gather, combine all death info, easier to structure
    tidyr::unite(`2000-2002`, `2000-2002`, `2000-2002.death_num`, `2000-2002.population`, sep=",") %>% 
    tidyr::unite(`2003-2005`, `2003-2005`, `2003-2005.death_num`, `2003-2005.population`, sep=",") %>% 
    tidyr::unite(`2006-2008`, `2006-2008`, `2006-2008.death_num`, `2006-2008.population`, sep=",") %>% 
    tidyr::unite(`2009-2011`, `2009-2011`, `2009-2011.death_num`, `2009-2011.population`, sep=",") %>% 
    tidyr::unite(`2012-2014`, `2012-2014`, `2012-2014.death_num`, `2012-2014.population`, sep=",") %>% 
    tidyr::unite(`2015-2017`, `2015-2017`, `2015-2017.death_num`, `2015-2017.population`, sep=",") %>% 
    
    # gather we convert data from wide to long
    tidyr::gather(key="period", value="death_info", 1:6) %>%    
    
    # seperate the death info so we have three columns
    tidyr::separate("death_info", c("death_rate","death_num","population"), sep=",") %>% 
    
    # make int death_num
    dplyr::mutate( death_rate = as.numeric(death_rate), 
                   death_num = as.numeric(death_num), 
                   population = as.numeric(population) ) %>%
    
    # convert the death_rate to the nearest integer num/pop rate
    dplyr::mutate( death_num = round(death_rate*population/10^5) ) %>%
    dplyr::mutate( 
      death_rate = dplyr::if_else(is.na(population), death_rate, death_num/population*10^5),
      death_cause = death.cause ) %>%
    
    # Rearrangement
    dplyr::arrange(county_fips) %>% 
    dplyr::select(
      # Rearrangement
      period, state_name, state_abbr, county_name, 
      county_fips, urban_2013, population, death_num, death_rate, death_cause
    ) %>% 
    as.data.frame()

}
```

