---
title: "GWAS"
author: "mouh"
date: "7/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Principal Component Analysis

```{r}
# PCA
pca.func <- function(data.mat, row.name, seed = 20) {
  set.seed(seed)
  pca.result <- prcomp(data.mat, retx = TRUE, center = FALSE)
  pca.result[["row.name"]] <- row.name
  return(pca.result)
}

```

## filtering 

```{r}
# km.func

#' Kmeans clustering function
#'
#' @param data.mat data.frame in which one column is "county_fips" and other columns
#'                  are data to cluster by
#' @param cluster.num number of clusters to form 
#' @param seed random seed to use, is variable so that results can be replicated
#'
#' @return a tribble with two columns:
#'    county_fips: unique identifier for each county
#'    cluster: number corresponding to cluster county belongs to
#'
#' @examples
#' cdc.data %>%
#'   cdc.mort.mat(input$state_choice, input$death_cause) %>%
#'   km.func(4)
#'   
#' km.func(cdc.mort.mat(cdc.data, "NY", "Despair"), 5)
#' 
#' @author 
#' @export
km.func <- function(data.mat, cluster.num=3, seed=200) {
  
  set.seed(seed)
  cluster.num <- min(nrow(data.mat) - 1, cluster.num)
  data.mat <- na.omit(data.mat)
  
  km.result <- kmeans(dplyr::select(data.mat, -county_fips), cluster.num)
  return(
    tibble(
      county_fips = dplyr::pull(data.mat, county_fips),
      cluster = as.character(km.result$cluster)
    )
  )
}


# diana.func

#' Diana clustering function
#'
#' @param data.mat data.frame in which one column is "county_fips" and other columns
#'                  are data to cluster by
#' @param cluster.num number of clusters to form 
#' @param seed random seed to use, is variable so that results can be replicated
#'
#' @return a tribble with two columns:
#'    county_fips: unique identifier for each county
#'    cluster: number corresponding to cluster county belongs to
#'    
#' @examples
#' cdc.data %>%
#'   cdc.mort.mat(input$state_choice, input$death_cause) %>%
#'   diana.func(4)
#'   
#'   
#' diana.func(cdc.mort.mat(cdc.data, "NY", "Despair"), 5)
#'    
#' @author Ross DeVito
#' @export
diana.func <- function(data.mat, cluster.num=3, seed=200) {
  set.seed(seed)
  data.mat <- na.omit(data.mat)
  
  diana.tree <- diana(dplyr::select(data.mat, -county_fips), 
                     metric = "euclidean", 
                     stand = FALSE,
                     stop.at.k = FALSE,
                     trace.lev = 0)
  diana.clusters <- cutree(as.hclust(diana.tree), k = cluster.num)
  return(tibble(county.fips = data.mat$county_fips, cluster = diana.clusters))
}


# cluster.counties

#' Clusters counties using some specified clustering method
#' 
#' @note implemented in this way so that if/when additional clustering method
#'        is added, it can be added to function in an else if
#'
#' @param county.data data.frame in which one column is "county_fips" and other columns
#'                     are data to cluster by
#' @param cluster.method method to be used to cluster counties. One of set {"kmeans", "diana"}
#' @param cluster.num optional argument used by clustering methods where you must provide
#'                      desired number of clusters (e.g. kmeans)
#' @param seed random seed to be used by clustering algorithm
#'
#' @return a tribble with (num counties in state) rows and two columns:
#'    county_fips: unique identifier for each county
#'    cluster: number corresponding to cluster county belongs to
#'    
#'    e.g.
#'    # A tibble: 67 x 2
#'    county_fips cluster
#'    <chr>       <chr>  
#'  1 01001       1      
#'  2 01003       4      
#'  3 01005       2      
#'  4 01007       4      
#'  5 01009       4      
#'  6 01011       2      
#'  7 01013       2      
#'  8 01015       1      
#'  9 01017       1      
#'  10 01019       4      
#'  # … with 57 more rows
#'
#' @examples
#' state <- "AL"
#' death.cause <- "Despair"
#' cluster.counties(cdc.mort.mat(cdc.data, state, death.cause),
#'                  cluster.method="kmeans",
#'                  cluster.num=4)
#' 
#' 
#' cluster.counties(cdc.mort.mat(cdc.data, input$state_choice, input$death_cause),
#'                  cluster.method="diana",
#'                  cluster.num=4)
#' 
#' @author Ross DeVito
#' @export
cluster.counties <- function(county.data, cluster.method="kmeans", cluster.num=4, seed=200) {
  if (cluster.method == "kmeans"){
    return(km.func(county.data, cluster.num, seed))
  } else if (cluster.method == "diana") {
    return(diana.func(county.data, cluster.num, seed))
  }
}

#cdc.mort.mat

#' Used in app.R and/or elsewhere
#' 
#' @note Importing and Conversion
#'
#' @param cdc.data.long
#' @param state.abbr
#' @param death.cause
#'
#' @return 
#'
#' @examples
#' 
#' @author John Erickson (based on others)
#' @export

cdc.mort.mat <- function(cdc.data.long, state.abbr, death.cause = "Despair") {
  
  tmp <- cdc.data.long
  if (state.abbr != "US") {
    tmp <- dplyr::filter(cdc.data.long, state_abbr == state.abbr)
  }else {
    tmp <- cdc.data.long
  }
  
  dplyr::filter(tmp, death_cause == death.cause) %>%
    tidyr::drop_na(county_fips) %>%
    dplyr::select(county_fips, death_rate, period) %>%
    tidyr::spread(key = period, value = death_rate) %>%
    dplyr::arrange(county_fips)
}


# order.county.clusters

#' Given a dataframe of counties and their original cluster and data.frame that can
#'  be used to map from original cluster to ordered cluster, returns a data.frame that
#'  gives counties with their ordered cluster
#'
#' @param county.clusters a data.frame or tribble in the form returned by cluster.counties()
#' @param cluster.order.map a data.frame that has the original cluster names as the row names
#'                           and the ordered clusters in a column "ord". Data.frames returned
#'                           by get.cluster.order.map are of this form
#'
#' @return a tribble with (num counties in state) rows and two columns:
#'    county_fips: unique identifier for each county
#'    cluster: number corresponding to cluster county belongs to, ordered such that 1 has the
#'              lowest deathrate the highest cluster number (the number of clusters) the highest
#'              
#'    Same format at cluster.counties(). See for example
#'
#' @examples
#' state <- "AL"
#' death.cause <- "Despair"
#' county.clusters <- cluster.counties(cdc.mort.mat(cdc.data, state, death.cause),
#'                                      cluster.method="kmeans",
#'                                      cluster.num=4)
#' cluster.deathrates <- get.cluster.deathrate.during.time(county.clusters, cdc.data, death.cause)
#' cluster.order.map <- get.cluster.order.map(cluster.deathrates)
#' county.clusters.ordered <- order.county.clusters(county.clusters, cluster.order.map)
#' 
#' 
#' order.county.clusters(mort.cluster.raw(), mort.cluster.map())
#' 
#' @author Ross DeVito
#' @export
#' order.county.clusters(mort.cluster.raw(), mort.cluster.map())
order.county.clusters <- function(county.clusters, cluster.order.map) {
  return(
    dplyr::mutate(county.clusters, cluster = cluster.order.map[cluster, "ord"])
  )
}


# Filtering out social determinants that are less relevant for Deaths of Despair using Benjamin Hochberg's method for multiple hypothesis testing.


state = "US"
death_cause_despair = "Despair"

mort.cluster.raw <- function(){
  n.clusters <- 6
  cluster.counties(cdc.mort.mat(cdc.data, "US", death_cause_despair),
                   cluster.method="kmeans",
                   cluster.num=n.clusters)
}
# Weighed Avg by UNORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are UNORDERED
mort.avg.cluster.raw <- function(){
  head(cdc.data)
  cdc.data %>%
    dplyr::filter(death_cause == death_cause_despair) %>%
    dplyr::right_join(mort.cluster.raw(), by = "county_fips") %>%
    dplyr::group_by(period, cluster) %>%
    dplyr::summarise(
      death_rate = sum(death_num) / sum(population) * 10^5,
      count = n()
    ) %>% 
    dplyr::ungroup()
}


# MAPPING from UNORDERED mortality trend label to ORDERED mortality trend label
 # Variables:
  #   - ord
  # Notes:
  #   - This is a mapping from raw cluster label to ORDERED cluster.
  #       Row names are the original cluster and `ord` are the reordered cluster
mort.cluster.map <- function(){
  mort.avg.cluster.raw() %>% 
    dplyr::filter(period == "2015-2017") %>%
    dplyr::arrange(death_rate) %>% 
    dplyr::mutate(ord = as.character(1:n())) %>% 
    dplyr::select(-c(period, death_rate)) %>% 
    textshape::column_to_rownames("cluster")
}

# ORDERED mortality trend cluster label calculation
# Variables:
  #   - county_fips
  #   - cluster
mort.cluster.ord <- function(){
  order.county.clusters(mort.cluster.raw(), mort.cluster.map())
}


# Weighed Avg by ORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are ORDERED
mort.avg.cluster.ord <- function(){
  dplyr::mutate(mort.avg.cluster.raw(), cluster = mort.cluster.map()[cluster, "ord"])
}


#Extracting the mortality rates for all states and counties for years "2015-2017"
mort.rate <- function(){
  cdc.data %>% dplyr::filter(
    death_cause == death_cause_despair,
    period == "2015-2017"
  ) %>%
    dplyr::mutate(
    ) %>%
    dplyr::select(county_fips, death_rate)
  
}
# Kendall Correlation Between raw mortality rates and county health rankings social determinants
kendall.cor <- mort.rate() %>% 
      dplyr::mutate(VAR = death_rate) %>%
      kendall.func(chr.data.2019) %>%
      dplyr::mutate(
        DIR = dplyr::if_else(
          kendall_cor <= 0,
          "Protective",
          "Destructive"
        )
        #chr_code = chr.namemap.2019[chr_code, 1]
      ) %>% na.omit() %>% 
      dplyr::arrange(desc(kendall_cor)) %>% 
      dplyr::mutate(chr_code = reorder(chr_code, kendall_cor))

selected_SDs_despair <- cbind(kendall.cor, state = state)

#using Benjamin Hochberg's p.adjust() method to adjust P-values for multiple hypothesis testing to filter out factors that are less relevant.
corrected_pvalues <- p.adjust(selected_SDs_despair$kendall_p)
selected_SDs_despair <- cbind(selected_SDs_despair, Corrected_P_Vals = corrected_pvalues)
selected_SDs_despair <- selected_SDs_despair %>%
  dplyr::filter(Corrected_P_Vals < 0.05) %>% 
  dplyr::arrange(desc(kendall_cor))

#Printing out the few selected factors for deaths of despair.
print(selected_SDs_despair)
```

## Filtering out social determinants that are less relevant for Cancer using Benjamin Hochberg's method for multiple hypothesis testing.

```{r}
state = "US"
death_cause_cancer = "Cancer"

# UNORDERED mortality trend cluster label calculation
# Variables:
  #   - county_fips
  #   - cluster
mort.cluster.raw <- function(){
  n.clusters <- 6
  cluster.counties(cdc.mort.mat(cdc.data, "US", death_cause_cancer),
                   cluster.method="kmeans",
                   cluster.num=n.clusters)
}


# Weighed Avg by UNORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are UNORDERED
mort.avg.cluster.raw <- function(){
  head(cdc.data)
  cdc.data %>%
    dplyr::filter(death_cause == death_cause_cancer) %>%
    dplyr::right_join(mort.cluster.raw(), by = "county_fips") %>%
    dplyr::group_by(period, cluster) %>%
    dplyr::summarise(
      death_rate = sum(death_num) / sum(population) * 10^5,
      count = n()
    ) %>% 
    dplyr::ungroup()
}


# MAPPING from UNORDERED mortality trend label to ORDERED mortality trend label
 # Variables:
  #   - ord
  
  # Notes:
  #   - This is a mapping from raw cluster label to ORDERED cluster.
  #       Row names are the original cluster and `ord` are the reordered cluster
  
mort.cluster.map <- function(){
  mort.avg.cluster.raw() %>% 
    dplyr::filter(period == "2015-2017") %>%
    dplyr::arrange(death_rate) %>% 
    dplyr::mutate(ord = as.character(1:n())) %>% 
    dplyr::select(-c(period, death_rate)) %>% 
    textshape::column_to_rownames("cluster")
}


# ORDERED mortality trend cluster label calculation
 # Variables:
  #   - county_fips
  #   - cluster
mort.cluster.ord <- function(){
  order.county.clusters(mort.cluster.raw(), mort.cluster.map())
  
}


# Weighed Avg by ORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are ORDERED
mort.avg.cluster.ord <- function(){
  dplyr::mutate(mort.avg.cluster.raw(), cluster = mort.cluster.map()[cluster, "ord"])
}


#Extracting the mortality rates for all states and counties for years "2015-2017"
mort.rate <- function(){
  
  cdc.data %>% dplyr::filter(
    death_cause == death_cause_cancer,
    period == "2015-2017"
  ) %>%
    dplyr::mutate(
    ) %>%
    dplyr::select(county_fips, death_rate)
  
}


# Kendall Correlation Between raw mortality rates and county health rankings social determinants
kendall.cor <- mort.rate() %>% 
      dplyr::mutate(VAR = death_rate) %>%
      kendall.func(chr.data.2019) %>%
      dplyr::mutate(
        DIR = dplyr::if_else(
          kendall_cor <= 0,
          "Protective",
          "Destructive"
        )
        #chr_code = chr.namemap.2019[chr_code, 1]
      ) %>% na.omit() %>% 
      dplyr::arrange(desc(kendall_cor)) %>% 
      dplyr::mutate(chr_code = reorder(chr_code, kendall_cor))

selected_SDs_cancer <- cbind(kendall.cor, state = state)

#using Benjamin Hochberg's p.adjust() method to adjust P-values for multiple hypothesis testing to filter out factors that are less relevant.
corrected_pvalues <- p.adjust(selected_SDs_cancer$kendall_p)
selected_SDs_cancer <- cbind(selected_SDs_cancer, Corrected_P_Vals = corrected_pvalues)
selected_SDs_cancer <- selected_SDs_cancer %>%
  dplyr::filter(Corrected_P_Vals < 0.05) %>% 
  dplyr::arrange(desc(kendall_cor))

#Printing out the few selected factors for cancer.
print(selected_SDs_cancer)
```


## Filtering out social determinants that are less relevant for Assault using Benjamin Hochberg's method for multiple hypothesis testing.

```{r}
state = "US"
death_cause_assault = "Assault"


# UNORDERED mortality trend cluster label calculation
# Variables:
  #   - county_fips
  #   - cluster

mort.cluster.raw <- function(){
  n.clusters <- 6
  cluster.counties(cdc.mort.mat(cdc.data, "US", death_cause_assault),
                   cluster.method="kmeans",
                   cluster.num=n.clusters)
}


# Weighed Avg by UNORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are UNORDERED
mort.avg.cluster.raw <- function(){
  head(cdc.data)
  cdc.data %>%
    dplyr::filter(death_cause == death_cause_assault) %>%
    dplyr::right_join(mort.cluster.raw(), by = "county_fips") %>%
    dplyr::group_by(period, cluster) %>%
    dplyr::summarise(
      death_rate = sum(death_num) / sum(population) * 10^5,
      count = n()
    ) %>% 
    dplyr::ungroup()
}


# MAPPING from UNORDERED mortality trend label to ORDERED mortality trend label
mort.cluster.map <- function(){
  mort.avg.cluster.raw() %>% 
    dplyr::filter(period == "2015-2017") %>%
    dplyr::arrange(death_rate) %>% 
    dplyr::mutate(ord = as.character(1:n())) %>% 
    dplyr::select(-c(period, death_rate)) %>% 
    textshape::column_to_rownames("cluster")
}


# ORDERED mortality trend cluster label calculation
# Variables:
  #   - county_fips
  #   - cluster
mort.cluster.ord <- function(){
  order.county.clusters(mort.cluster.raw(), mort.cluster.map())
}



# Weighed Avg by ORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are ORDERED
mort.avg.cluster.ord <- function(){
  dplyr::mutate(mort.avg.cluster.raw(), cluster = mort.cluster.map()[cluster, "ord"])
}


#Extracting the mortality rates for all states and counties for years "2015-2017"
mort.rate <- function(){
  cdc.data %>% dplyr::filter(
    death_cause == death_cause_assault,
    period == "2015-2017"
  ) %>%
    dplyr::mutate(
      # death_rate = death_num / population * 10^5
      #death_rate = cut(death_rate, bin.geo.mort(death_cause_assault))
    ) %>%
    dplyr::select(county_fips, death_rate)
  
}

# Kendall Correlation Between raw mortality rates and county health rankings social determinants
kendall.cor <- mort.rate() %>% 
      dplyr::mutate(VAR = death_rate) %>%
      kendall.func(chr.data.2019) %>%
      dplyr::mutate(
        DIR = dplyr::if_else(
          kendall_cor <= 0,
          "Protective",
          "Destructive"
        )
        #chr_code = chr.namemap.2019[chr_code, 1]
      ) %>% na.omit() %>% 
      dplyr::arrange(desc(kendall_cor)) %>% 
      dplyr::mutate(chr_code = reorder(chr_code, kendall_cor))

selected_SDs_assault <- cbind(kendall.cor, state = state)

#using Benjamin Hochberg's p.adjust() method to adjust P-values for multiple hypothesis testing to filter out factors that are less relevant.
corrected_pvalues <- p.adjust(selected_SDs_assault$kendall_p)
selected_SDs_assault <- cbind(selected_SDs_assault, Corrected_P_Vals = corrected_pvalues)
selected_SDs_assault <- selected_SDs_assault %>%
  dplyr::filter(Corrected_P_Vals < 0.05) %>% 
  dplyr::arrange(desc(kendall_cor))

#Printing out the few selected factors for assault
print(selected_SDs_assault)
```

## Filtering out social determinants that are less relevant for Cardiovascular deaths using Benjamin Hochberg's method for multiple hypothesis testing.

```{r}
state = "US"
death_cause_cardiovascular = "Cardiovascular"

# UNORDERED mortality trend cluster label calculation
# Variables:
  #   - county_fips
  #   - cluster
mort.cluster.raw <- function(){
  n.clusters <- 6
  cluster.counties(cdc.mort.mat(cdc.data, "US", death_cause_cardiovascular),
                   cluster.method="kmeans",
                   cluster.num=n.clusters)
}


# Weighed Avg by UNORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are UNORDERED
mort.avg.cluster.raw <- function(){
  head(cdc.data)
  cdc.data %>%
    dplyr::filter(death_cause == death_cause_cardiovascular) %>%
    dplyr::right_join(mort.cluster.raw(), by = "county_fips") %>%
    dplyr::group_by(period, cluster) %>%
    dplyr::summarise(
      death_rate = sum(death_num) / sum(population) * 10^5,
      count = n()
    ) %>% 
    dplyr::ungroup()
}


# MAPPING from UNORDERED mortality trend label to ORDERED mortality trend label
# Variables:
  #   - ord
  
  # Notes:
  #   - This is a mapping from raw cluster label to ORDERED cluster.
  #       Row names are the original cluster and `ord` are the reordered cluster
mort.cluster.map <- function(){
  mort.avg.cluster.raw() %>% 
    dplyr::filter(period == "2015-2017") %>%
    dplyr::arrange(death_rate) %>% 
    dplyr::mutate(ord = as.character(1:n())) %>% 
    dplyr::select(-c(period, death_rate)) %>% 
    textshape::column_to_rownames("cluster")
}


# ORDERED mortality trend cluster label calculation
 # Variables:
  #   - county_fips
  #   - cluster
mort.cluster.ord <- function(){
  order.county.clusters(mort.cluster.raw(), mort.cluster.map())
}


# Weighed Avg by ORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are ORDERED
mort.avg.cluster.ord <- function(){
  dplyr::mutate(mort.avg.cluster.raw(), cluster = mort.cluster.map()[cluster, "ord"])
}

#Extracting the mortality rates for all states and counties for years "2015-2017"
mort.rate <- function(){
  cdc.data %>% dplyr::filter(
    death_cause == death_cause_cardiovascular,
    period == "2015-2017"
  ) %>%
    dplyr::mutate(
      # death_rate = death_num / population * 10^5
      #death_rate = cut(death_rate, bin.geo.mort(death_cause_cardiovascular))
    ) %>%
    dplyr::select(county_fips, death_rate)
  
}
# Kendall Correlation Between raw mortality rates and county health rankings social determinants
kendall.cor <- mort.rate() %>% 
      dplyr::mutate(VAR = death_rate) %>%
      kendall.func(chr.data.2019) %>%
      dplyr::mutate(
        DIR = dplyr::if_else(
          kendall_cor <= 0,
          "Protective",
          "Destructive"
        )
        #chr_code = chr.namemap.2019[chr_code, 1]
      ) %>% na.omit() %>% 
      dplyr::arrange(desc(kendall_cor)) %>% 
      dplyr::mutate(chr_code = reorder(chr_code, kendall_cor))

selected_SDs_cardiovascular <- cbind(kendall.cor, state = state)

#using Benjamin Hochberg's p.adjust() method to adjust P-values for multiple hypothesis testing to filter out factors that are less relevant
corrected_pvalues <- p.adjust(selected_SDs_cardiovascular$kendall_p)
selected_SDs_cardiovascular <- cbind(selected_SDs_cardiovascular, Corrected_P_Vals = corrected_pvalues)
selected_SDs_cardiovascular <- selected_SDs_cardiovascular %>%
  dplyr::filter(Corrected_P_Vals < 0.05) %>% 
  dplyr::arrange(desc(kendall_cor))

#Printing out the few selected factors for cardiovascular deaths
print(selected_SDs_cardiovascular)
```


## Filtering out social determinants that are less relevant for all causes of death using Benjamin Hochberg's method for multiple hypothesis testing.

```{r}
state = "US"
death_cause_allcause = "All Cause"

# UNORDERED mortality trend cluster label calculation
 # Variables:
  #   - county_fips
  #   - cluster
mort.cluster.raw <- function(){
  n.clusters <- 6
  cluster.counties(cdc.mort.mat(cdc.data, "US", death_cause_allcause),
                   cluster.method="kmeans",
                   cluster.num=n.clusters)
}


# Weighed Avg by UNORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are UNORDERED
mort.avg.cluster.raw <- function(){
  head(cdc.data)
  cdc.data %>%
    dplyr::filter(death_cause == death_cause_allcause) %>%
    dplyr::right_join(mort.cluster.raw(), by = "county_fips") %>%
    dplyr::group_by(period, cluster) %>%
    dplyr::summarise(
      death_rate = sum(death_num) / sum(population) * 10^5,
      count = n()
    ) %>% 
    dplyr::ungroup()
}


# MAPPING from UNORDERED mortality trend label to ORDERED mortality trend label
# Variables:
  #   - ord
  
  # Notes:
  #   - This is a mapping from raw cluster label to ORDERED cluster.
  #       Row names are the original cluster and `ord` are the reordered cluster
mort.cluster.map <- function(){
  mort.avg.cluster.raw() %>% 
    dplyr::filter(period == "2015-2017") %>%
    dplyr::arrange(death_rate) %>% 
    dplyr::mutate(ord = as.character(1:n())) %>% 
    dplyr::select(-c(period, death_rate)) %>% 
    textshape::column_to_rownames("cluster")
}


# ORDERED mortality trend cluster label calculation
 # Variables:
  #   - county_fips
  #   - cluster
mort.cluster.ord <- function(){
  order.county.clusters(mort.cluster.raw(), mort.cluster.map())
}


# Weighed Avg by ORDERED cluster
# Variables:
  #   - period
  #   - cluster
  #   - death_rate
  #   - count
  
  # Notes:
  #   - The cluster labels are ORDERED
mort.avg.cluster.ord <- function(){
  dplyr::mutate(mort.avg.cluster.raw(), cluster = mort.cluster.map()[cluster, "ord"])
}


mort.rate <- function(){
  
  cdc.data %>% dplyr::filter(
    death_cause == death_cause_allcause,
    period == "2015-2017"
  ) %>%
    dplyr::mutate(
      # death_rate = death_num / population * 10^5
      #death_rate = cut(death_rate, bin.geo.mort(death_cause_allcause))
    ) %>%
    dplyr::select(county_fips, death_rate)
  
}

# Kendall Correlation Between raw mortality rates and county health rankings social determinants
kendall.cor <- mort.rate() %>% 
      dplyr::mutate(VAR = death_rate) %>%
      kendall.func(chr.data.2019) %>%
      dplyr::mutate(
        DIR = dplyr::if_else(
          kendall_cor <= 0,
          "Protective",
          "Destructive"
        )
        #chr_code = chr.namemap.2019[chr_code, 1]
      ) %>% na.omit() %>% 
      dplyr::arrange(desc(kendall_cor)) %>% 
      dplyr::mutate(chr_code = reorder(chr_code, kendall_cor))

selected_SDs_allcause <- cbind(kendall.cor, state = state)

#using Benjamin Hochberg's p.adjust() method to adjust P-values for multiple hypothesis testing to filter out factors that are less relevant.
corrected_pvalues <- p.adjust(selected_SDs_allcause$kendall_p)
selected_SDs_allcause <- cbind(selected_SDs_allcause, Corrected_P_Vals = corrected_pvalues)
selected_SDs_allcause <- selected_SDs_allcause %>%
  dplyr::filter(Corrected_P_Vals < 0.05) %>% 
  dplyr::arrange(desc(kendall_cor))

#Printing out the few selected factors for all causes of death
print(selected_SDs_allcause)
```


## Combining all the influential social determinants that are are found in all causes of death. We are combining them by taking the union.

```{r}
selected_SDs_final <- union(selected_SDs_despair$chr_code, selected_SDs_cancer$chr_code)
selected_SDs_final <- union(selected_SDs_final, selected_SDs_assault$chr_code)
selected_SDs_final <- union(selected_SDs_final, selected_SDs_cardiovascular$chr_code)
selected_SDs_final <- union(selected_SDs_final, selected_SDs_allcause$chr_code)
print(selected_SDs_final)
```

## Creating a dataframe that only contains the final selected social determinants

```{r}
selected_SDs_final <- selected_SDs_final[-1]
saveRDS(selected_SDs_final, "reduced.chr.list.rds")

reduced.chr.list <- readRDS("reduced.chr.list.rds")
reduced.chr.list <- append(reduced.chr.list, "county_fips", after = 0)
chr.data.2019_fewer_SDs <- chr.data.2019 %>%
  as_data_frame %>%
  select(reduced.chr.list)
head(chr.data.2019_fewer_SDs)

saveRDS(chr.data.2019_fewer_SDs, "chr.data.2019.reduced.rds")
```

## Reading the factors data from an RDS file that only has the few selected factors (just to test it out)

```{r}
reduced.chr.list <- readRDS("chr.data.2019.reduced.rds")
print(reduced.chr.list)
```

## Calculating the percentage missing values for each factor (social determinant)

```{r}
colMeans(is.na(chr.data.2019))
```

