---
title: "COVID Mortality Rate per 100K and Chronic Respiratory Disease Mortality Rate"
output: html_notebook
---
Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

COVID Mortality Rate per 100K for each NY County
```{r}
#set working directory as COVID-Notebooks/data/csv/time_series
#import data from covid_NY_counties.death.csv and NY_populations.csv

covid_NY_counties_deaths <- read.csv(file.choose()) #choose file in the time_series folder
NY_populations <- read.csv("NY_population.csv")

#merge the two data frames by county
#this new data frame is called "myfulldata"
myfulldata = merge(covid_NY_counties_deaths , NY_populations, by.x="county", by.y="County")

#divide the number of deaths with the county's population to find the mortality rate
mortality_rate_sa = myfulldata$deaths/myfulldata$Population
myfulldata$mortality_rate <- c(mortality_rate_sa)

#plot of crude rate
ggplot(data=myfulldata, aes(x=county, y=mortality_rate))+geom_point()+  ylim(c(0, .004))+xlab("NY Counties")+ ylab ("Crude COVID Mortality Rate")+ ggtitle("Crude COVID Mortality Rate for Every NY County")

#each mortality is mulitpled by 100K for easier comparison and added into the myfulldata data frame
stadper100000 = mortality_rate_sa *100000
myfulldata$mortality_per_100000 <- c(stadper100000)

#plot of per100K rate with no excluded points
ggplot(data=myfulldata, aes(x=county, y=mortality_per_100000))+geom_point()+  ylim(c(0, 350))+xlab("NY Counties")+ ylab ("COVID Mortality Rate (per 100K)")+ ggtitle("COVID Mortality Rate (per 100K) for Every NY County")

#plot of per100K rate with exclusion of points under the value 10
ggplot(data=myfulldata, aes(x=county, y=mortality_per_100000))+geom_point()+  ylim(c(10, 350))+xlab("NY Counties")+ ylab ("COVID Mortality Rate (per 100K)")+ ggtitle("COVID Mortality Rate (per 100K) for NY Counties with Rates Greater Than 10")
```


Compare the COVID Mortality Rate and Chronic Repsiratory Disease Mortality Rate for each NY County
```{r}
#set working directory as COVID-Notebooks/data/csv
#import data from chronicrespiratorydiseases_counties.csv
chronicrespiratorydiseases_counties #file in COVID-Notebooks/data/csv

#merged data from chronicrespiratorydiseases_counties.csv into the data frame "myfulldata" by the FIPS and renamed the data frame as "myfulldataresp" 
myfulldataresp = merge(myfulldata , chronicrespiratorydiseases_counties, by="FIPS")

#correlation test and plot between COVID mortality rate and respiratory diesease mortality rate
cor.test(myfulldataresp$mortality_per_100000,myfulldataresp$MortalityRate2014)
#correlation: -0.7791952

plot(myfulldataresp$MortalityRate2014, myfulldataresp$mortality_per_100000, xlab="Chronic Respiratory Disease Mortality Rate", ylab="COVID Mortality Rate", main="COVID Mortality Rate VS Chronic Respiratory Disease Mortality Rate")

lm(myfulldataresp$mortality_per_100000~myfulldataresp$MortalityRate2014)
```

**No longer works
Compare the COVID mortality rate and Chronic Repsiratory Disease Mortality Rate for Each State.
```{r}
#files found COVID-Notebooks/data/csv
#chronic respiratory disease vs COVID in states
#merged data from covid_data_states.csv and chronicrespiratorydiseases_counties into a data frame called dataforstatesresp by the state names
covid_data_states<- read.csv("covid_data_states.csv")
dataforstatesresp = merge(covid_data_states, chronicrespiratorydiseases_counties, by.x="NAME", by.y="CNTY")


stateper100000 = dataforstatesresp$Mortality_rate *100000
dataforstatesresp$mortality_per_100K <- c(stateper100000)

#correlation test and plot between COVID mortality rate and respiratory diesease mortality rate
cor.test(dataforstatesresp$Mortality_rate,dataforstatesresp$MortalityRate2014)
plot(dataforstatesresp$MortalityRate2014, dataforstatesresp$Mortality_rate,xlab ="Chronic Respiratory Disease Mortality Rate", ylab ="COVID Mortality Rate", main="Correlation of National COVID Mortality Rate and Chronic Respiratory Disease Mortality Rate")


```


