---
title: "ahns-Determinants_Stacked_Bar"
output: html_notebook
---
I abandoned my work in the Determinants_Graphing.Rmd because of time deficiency. Also, the data frame does not allow me to separate what determinants showed up as destructive and protective.
This time, I counted the frequency of protective and destructive for each determinant and added them to the data frame.

creating new data frame with determinants, number of occurrence, and frequency of protective/destructive
```{r}
library(plyr)
library(ggplot2)
library(dbplyr)
library(reshape2)
library(tidyr)

#states with not enough data: UT,VT,DE,ME,MD,MA,NH,NJ
#states that did not work with above code: AK,MI,RI,WY

#combined all of state data into a data frame called "prtdescombined"
#same data frame used in Determinants_Graphing.Rmd
prtdescombined = rbind(dataAL , dataAR,dataAZ,dataCA, dataCO, dataFL, dataGA, dataIA, dataID,dataIL,dataIN,dataKS, dataKY, dataLA, dataMI, dataMN, dataMO, dataMS, dataMT, dataNC, dataND, dataNE, dataNJ, dataNM, dataNY, dataOH,dataOK,dataOR,dataPA,dataSC,dataSD, dataTN,dataTX,dataVA,dataWA,dataWI,dataWV)

#SubDataFrames for each Significant Determinant Pattern
#1st line: create detdeterminant_name data frame by selecting only that determinant in the prtdescombined dataframe
#2nd line: create count_determinant_name data frame by counting number of determinant's occurrence 
#3rd line: create freqdeterminant_name data frame by deleting rows 2 and 3 in the count_determinant_name data frame
#4th line: create new column with name of determinants in freqdeterminant_name data frame
#5th line: create prtdeterminant_name data frame by coutning number of protective occurrences of determinant
#6th line: create freqprtdeterminant_name data frame by deleting rows 1 and 2 in the prtdeterminant_name data frame
#7th line: add new column with frequency of protective occurrences in freqdeterminant_name data frame
#8th line: create desdeterminant_name data frame by coutning number of destructive occurrences of determinant
#9th line: create freqdesdeterminant_name data frame by deleting rows 1 and 2 in the desdeterminant_name data frame
#10th line: add new column with frequency of destructive occurrences in freqdeterminant_name data frame

#Confirmed 
detconfirmed = subset(prtdescombined, y == "Confirmed")
count_confirmed<- ldply(detconfirmed,function(c) sum(c=="Confirmed"))
freqconfirmed = count_confirmed[-c(2, 3),]
freqconfirmed$Determinants = "Confirmed"
prtconfirmed = ldply(detconfirmed, function(c) sum(c == "Protective"))
freqprtconfirmed = prtconfirmed[-c(1,2),]
freqconfirmed$Protective = freqprtconfirmed
desconfirmed = ldply(detconfirmed, function(c) sum(c == "Destructive"))                
freqdesconfirmed = desconfirmed[-c(1,2),]
freqconfirmed$Destructive = freqdesconfirmed

#Active
detactive = subset(prtdescombined, y == "Active")
count_active<- ldply(detactive,function(c) sum(c=="Active"))
freqactive = count_active[-c(2, 3),]
freqactive$Determinants= "Active"
prtactive = ldply(detactive, function(c) sum(c == "Protective"))
freqprtactive = prtactive[-c(1,2),]
freqactive$Protective = freqprtactive
desactive = ldply(detactive, function(c) sum(c == "Destructive"))                
freqdesactive = desactive[-c(1,2),]
freqactive$Destructive = freqdesactive

#Case Fatality Ratio
detcase.fatality = subset(prtdescombined, y == "Case.Fatality_Ratio")
count_case.fatality<- ldply(detcase.fatality,function(c) sum(c=="Case.Fatality_Ratio"))
freqcase.fatality = count_case.fatality[-c(2, 3),]
freqcase.fatality$Determinants= "Case Fatality Ratio"
prtcase.fatality = ldply(detcase.fatality, function(c) sum(c == "Protective"))
freqprtcase.fatality = prtcase.fatality[-c(1,2),]
freqcase.fatality$Protective = freqprtcase.fatality
descase.fatality = ldply(detcase.fatality, function(c) sum(c == "Destructive"))                
freqdescase.fatality = descase.fatality[-c(1,2),]
freqcase.fatality$Destructive = freqdescase.fatality

#Teen Birth Rate
detteenbirth = subset(prtdescombined, y == "Teen Birth Rate")
count_teenbirth<- ldply(detteenbirth,function(c) sum(c=="Teen Birth Rate"))
freqteenbirth = count_teenbirth[-c(2, 3),]
freqteenbirth$Determinants= "Teen Birth Rate"
prtteenbirth = ldply(detteenbirth, function(c) sum(c == "Protective"))
freqprtteenbirth = prtteenbirth[-c(1,2),]
freqteenbirth$Protective = freqprtteenbirth
desteenbirth = ldply(detteenbirth, function(c) sum(c == "Destructive"))                
freqdesteenbirth = desteenbirth[-c(1,2),]
freqteenbirth$Destructive = freqdesteenbirth

#Overcrowding
detovercrowding = subset(prtdescombined, y == "Overcrowding")
count_overcrowding<- ldply(detovercrowding,function(c) sum(c=="Overcrowding"))
freqovercrowding = count_overcrowding[-c(2, 3),]
freqovercrowding$Determinants= "Overcrowding"
prtovercrowding = ldply(detovercrowding, function(c) sum(c == "Protective"))
freqprtovercrowding = prtovercrowding[-c(1,2),]
freqovercrowding$Protective = freqprtovercrowding
desovercrowding = ldply(detovercrowding, function(c) sum(c == "Destructive"))                
freqdesovercrowding = desovercrowding[-c(1,2),]
freqovercrowding$Destructive = freqdesovercrowding

#% less than 18 years of age
detlessthan18 = subset(prtdescombined, y == "% less than 18 years of age")
count_lessthan18<- ldply(detlessthan18,function(c) sum(c=="% less than 18 years of age"))
freqlessthan18 = count_lessthan18[-c(2, 3),]
freqlessthan18$Determinants= "% less than 18 years of age"
prtlessthan18 = ldply(detlessthan18, function(c) sum(c == "Protective"))
freqprtlessthan18 = prtlessthan18[-c(1,2),]
freqlessthan18$Protective = freqprtlessthan18
deslessthan18 = ldply(detlessthan18, function(c) sum(c == "Destructive"))                
freqdeslessthan18 = deslessthan18[-c(1,2),]
freqlessthan18$Destructive = freqdeslessthan18

#% Not Proficient in English
detnotproficientinenglish = subset(prtdescombined, y == "% Not Proficient in English")
count_notproficientinenglish<- ldply(detnotproficientinenglish,function(c) sum(c=="% Not Proficient in English"))
freqnotproficientinenglish = count_notproficientinenglish[-c(2, 3),]
freqnotproficientinenglish$Determinants= "% Not Proficient in English"
prtnotproficientinenglish = ldply(detnotproficientinenglish, function(c) sum(c == "Protective"))
freqprtnotproficientinenglish = prtnotproficientinenglish[-c(1,2),]
freqnotproficientinenglish$Protective = freqprtnotproficientinenglish
desnotproficientinenglish = ldply(detnotproficientinenglish, function(c) sum(c == "Destructive"))
freqdesnotproficientinenglish = desnotproficientinenglish[-c(1,2),]
freqnotproficientinenglish$Destructive = freqdesnotproficientinenglish

#Pediatric Asthma
detpediatricasthma = subset(prtdescombined, y == "PediatricAsthma")
count_pediatricasthma<- ldply(detpediatricasthma,function(c) sum(c=="PediatricAsthma"))
freqpediatricasthma = count_pediatricasthma[-c(2, 3),]
freqpediatricasthma$Determinants= "Pediatric Asthma"
prtpediatricasthma = ldply(detpediatricasthma, function(c) sum(c == "Protective"))
freqprtpediatricasthma = prtpediatricasthma[-c(1,2),]
freqpediatricasthma$Protective = freqprtpediatricasthma
despediatricasthma = ldply(detpediatricasthma, function(c) sum(c == "Destructive"))             
freqdespediatricasthma = despediatricasthma[-c(1,2),]
freqpediatricasthma$Destructive = freqdespediatricasthma

#% Uninsured 1
detuninsured1 = subset(prtdescombined, y == "% Uninsured_1")
count_uninsured1<- ldply(detuninsured1,function(c) sum(c=="% Uninsured_1"))
frequninsured1 = count_uninsured1[-c(2, 3),]
frequninsured1$Determinants= "% Uninsured 1"
prtuninsured1 = ldply(detuninsured1, function(c) sum(c == "Protective"))
freqprtuninsured1 = prtuninsured1[-c(1,2),]
frequninsured1$Protective = freqprtuninsured1
desuninsured1 = ldply(detuninsured1, function(c) sum(c == "Destructive"))      
freqdesuninsured1 = desuninsured1[-c(1,2),]
frequninsured1$Destructive = freqdesuninsured1

#% Uninsured 2
detuninsured2 = subset(prtdescombined, y == "% Uninsured_2")
count_uninsured2<- ldply(detuninsured2,function(c) sum(c=="% Uninsured_2"))
frequninsured2 = count_uninsured2[-c(2, 3),]
frequninsured2$Determinants= "% Uninsured 2"
prtuninsured2 = ldply(detuninsured2, function(c) sum(c == "Protective"))
freqprtuninsured2 = prtuninsured2[-c(1,2),]
frequninsured2$Protective = freqprtuninsured2
desuninsured2 = ldply(detuninsured2, function(c) sum(c == "Destructive"))      
freqdesuninsured2 = desuninsured2[-c(1,2),]
frequninsured2$Destructive = freqdesuninsured2

#Mean Winter Temperature
detmeanwintertemp = subset(prtdescombined, y == "mean_winter_temp")
count_meanwintertemp<- ldply(detmeanwintertemp,function(c) sum(c=="mean_winter_temp"))
freqmeanwintertemp = count_meanwintertemp[-c(2, 3),]
freqmeanwintertemp$Determinants= "Mean Winter Temperature"
prtmeanwintertemp = ldply(detmeanwintertemp, function(c) sum(c == "Protective"))
freqprtmeanwintertemp = prtmeanwintertemp[-c(1,2),]
freqmeanwintertemp$Protective = freqprtmeanwintertemp
desmeanwintertemp = ldply(detmeanwintertemp, function(c) sum(c == "Destructive"))      
freqdesmeanwintertemp = desmeanwintertemp[-c(1,2),]
freqmeanwintertemp$Destructive = freqdesmeanwintertemp

#Mean Summer Temperature
detmeansummertemp = subset(prtdescombined, y == "mean_summer_temp")
count_meansummertemp<- ldply(detmeansummertemp,function(c) sum(c=="mean_summer_temp"))
freqmeansummertemp = count_meansummertemp[-c(2, 3),]
freqmeansummertemp$Determinants= "Mean Summer Temperature"
prtmeansummertemp = ldply(detmeansummertemp, function(c) sum(c == "Protective"))
freqprtmeansummertemp = prtmeansummertemp[-c(1,2),]
freqmeansummertemp$Protective = freqprtmeansummertemp
desmeansummertemp = ldply(detmeansummertemp, function(c) sum(c == "Destructive"))      
freqdesmeansummertemp = desmeansummertemp[-c(1,2),]
freqmeansummertemp$Destructive = freqdesmeansummertemp

#Longitude
detlong = subset(prtdescombined, y == "Long_")
count_long<- ldply(detlong,function(c) sum(c=="Long_"))
freqlong = count_long[-c(2, 3),]
freqlong$Determinants= "Long_"
prtlong = ldply(detlong, function(c) sum(c == "Protective"))
freqprtlong = prtlong[-c(1,2),]
freqlong$Protective = freqprtlong
deslong = ldply(detlong, function(c) sum(c == "Destructive"))      
freqdeslong = deslong[-c(1,2),]
freqlong$Destructive = freqdeslong

#Older Percent
detolderpecent = subset(prtdescombined, y == "older_pecent")
count_olderpecent<- ldply(detolderpecent,function(c) sum(c=="older_pecent"))
freqolderpecent = count_olderpecent[-c(2, 3),]
freqolderpecent$Determinants= "Older Percent"
prtolderpecent = ldply(detolderpecent, function(c) sum(c == "Protective"))
freqprtolderpecent = prtolderpecent[-c(1,2),]
freqolderpecent$Protective = freqprtolderpecent
desolderpecent = ldply(detolderpecent, function(c) sum(c == "Destructive"))      
freqdesolderpecent = desolderpecent[-c(1,2),]
freqolderpecent$Destructive = freqdesolderpecent

#Mid Percent
detmidpecent = subset(prtdescombined, y == "mid_pecent")
count_midpecent<- ldply(detmidpecent,function(c) sum(c=="mid_pecent"))
freqmidpecent = count_midpecent[-c(2, 3),]
freqmidpecent$Determinants= "Mid Percent"
prtmidpecent = ldply(detmidpecent, function(c) sum(c == "Protective"))
freqprtmidpecent = prtmidpecent[-c(1,2),]
freqmidpecent$Protective = freqprtmidpecent
desmidpecent = ldply(detmidpecent, function(c) sum(c == "Destructive"))      
freqdesmidpecent = desmidpecent[-c(1,2),]
freqmidpecent$Destructive = freqdesmidpecent

#Years of Potential Life Lost Rate
detyearspotentiallifelostrate = subset(prtdescombined, y == "Years of Potential Life Lost Rate")
count_yearspotentiallifelostrate<- ldply(detyearspotentiallifelostrate,function(c) sum(c=="Years of Potential Life Lost Rate"))
freqyearspotentiallifelostrate = count_yearspotentiallifelostrate[-c(2, 3),]
freqyearspotentiallifelostrate$Determinants= "Years of Potential Life Lost Rate"
prtyearspotentiallifelostrate = ldply(detyearspotentiallifelostrate, function(c) sum(c == "Protective"))
freqprtyearspotentiallifelostrate = prtyearspotentiallifelostrate[-c(1,2),]
freqyearspotentiallifelostrate$Protective = freqprtyearspotentiallifelostrate
desyearspotentiallifelostrate = ldply(detyearspotentiallifelostrate, function(c) sum(c == "Destructive"))      
freqdesyearspotentiallifelostrate = desyearspotentiallifelostrate[-c(1,2),]
freqyearspotentiallifelostrate$Destructive = freqdesyearspotentiallifelostrate

detlowbirthweight = subset(prtdescombined, y == "% Low Birthweight")
count_lowbirthweight<- ldply(detlowbirthweight,function(c) sum(c=="% Low Birthweight"))
freqlowbirthweight = count_lowbirthweight[-c(2, 3),]
freqlowbirthweight$Determinants= "% Low Birthweight"
prtlowbirthweight = ldply(detlowbirthweight, function(c) sum(c == "Protective"))
freqprtlowbirthweight = prtlowbirthweight[-c(1,2),]
freqlowbirthweight$Protective = freqprtlowbirthweight
deslowbirthweight = ldply(detlowbirthweight, function(c) sum(c == "Destructive"))      
freqdeslowbirthweight = deslowbirthweight[-c(1,2),]
freqlowbirthweight$Destructive = freqdeslowbirthweight

detsmokers = subset(prtdescombined, y == "% Smokers")
count_smokers<- ldply(detsmokers,function(c) sum(c=="% Smokers"))
freqsmokers = count_smokers[-c(2, 3),]
freqsmokers$Determinants= "% Smokers"
prtsmokers = ldply(detsmokers, function(c) sum(c == "Protective"))
freqprtsmokers = prtsmokers[-c(1,2),]
freqsmokers$Protective = freqprtsmokers
dessmokers = ldply(detsmokers, function(c) sum(c == "Destructive"))      
freqdessmokers = dessmokers[-c(1,2),]
freqsmokers$Destructive = freqdessmokers

detpct_obesity = subset(prtdescombined, y == "pct_obesity")
count_pct_obesity<- ldply(detpct_obesity,function(c) sum(c=="pct_obesity"))
freqpct_obesity = count_pct_obesity[-c(2, 3),]
freqpct_obesity$Determinants= "pct_obesity"
prtpct_obesity = ldply(detpct_obesity, function(c) sum(c == "Protective"))
freqprtpct_obesity = prtpct_obesity[-c(1,2),]
freqpct_obesity$Protective = freqprtpct_obesity
despct_obesity = ldply(detpct_obesity, function(c) sum(c == "Destructive"))      
freqdespct_obesity = despct_obesity[-c(1,2),]
freqpct_obesity$Destructive = freqdespct_obesity

detphysicallyinactive = subset(prtdescombined, y == "% Physically Inactive")
count_physicallyinactive<- ldply(detphysicallyinactive,function(c) sum(c=="% Physically Inactive"))
freqphysicallyinactive = count_physicallyinactive[-c(2, 3),]
freqphysicallyinactive$Determinants= "% Physically Inactive"
prtphysicallyinactive = ldply(detphysicallyinactive, function(c) sum(c == "Protective"))
freqprtphysicallyinactive = prtphysicallyinactive[-c(1,2),]
freqphysicallyinactive$Protective = freqprtphysicallyinactive
desphysicallyinactive = ldply(detphysicallyinactive, function(c) sum(c == "Destructive"))      
freqdesphysicallyinactive = desphysicallyinactive[-c(1,2),]
freqphysicallyinactive$Destructive = freqdesphysicallyinactive

detexcessivedrinking = subset(prtdescombined, y == "% Excessive Drinking")
count_excessivedrinking<- ldply(detexcessivedrinking,function(c) sum(c=="% Excessive Drinking"))
freqexcessivedrinking = count_excessivedrinking[-c(2, 3),]
freqexcessivedrinking$Determinants= "% Excessive Drinking"
prtexcessivedrinking = ldply(detexcessivedrinking, function(c) sum(c == "Protective"))
freqprtexcessivedrinking = prtexcessivedrinking[-c(1,2),]
freqexcessivedrinking$Protective = freqprtexcessivedrinking
desexcessivedrinking = ldply(detexcessivedrinking, function(c) sum(c == "Destructive"))      
freqdesexcessivedrinking = desexcessivedrinking[-c(1,2),]
freqexcessivedrinking$Destructive = freqdesexcessivedrinking

detdrivingalcohol = subset(prtdescombined, y == "% Driving Deaths with Alcohol Involvement")
count_drivingalcohol<- ldply(detdrivingalcohol,function(c) sum(c=="% Driving Deaths with Alcohol Involvement"))
freqdrivingalcohol = count_drivingalcohol[-c(2, 3),]
freqdrivingalcohol$Determinants= "% Driving Deaths with Alcohol Involvement"
prtdrivingalcohol = ldply(detdrivingalcohol, function(c) sum(c == "Protective"))
freqprtdrivingalcohol = prtdrivingalcohol[-c(1,2),]
freqdrivingalcohol$Protective = freqprtdrivingalcohol
desdrivingalcohol = ldply(detdrivingalcohol, function(c) sum(c == "Destructive"))      
freqdesdrivingalcohol = desdrivingalcohol[-c(1,2),]
freqdrivingalcohol$Destructive = freqdesdrivingalcohol

detteenbirthhispanic = subset(prtdescombined, y == "Teen Birth Rate (Hispanic)")
count_teenbirthhispanic<- ldply(detteenbirthhispanic,function(c) sum(c=="Teen Birth Rate (Hispanic)"))
freqteenbirthhispanic = count_teenbirthhispanic[-c(2, 3),]
freqteenbirthhispanic$Determinants= "Teen Birth Rate (Hispanic)"
prtteenbirthhispanic = ldply(detteenbirthhispanic, function(c) sum(c == "Protective"))
freqprtteenbirthhispanic = prtteenbirthhispanic[-c(1,2),]
freqteenbirthhispanic$Protective = freqprtteenbirthhispanic
desteenbirthhispanic = ldply(detteenbirthhispanic, function(c) sum(c == "Destructive"))      
freqdesteenbirthhispanic = desteenbirthhispanic[-c(1,2),]
freqteenbirthhispanic$Destructive = freqdesteenbirthhispanic

detteenbirthwhite = subset(prtdescombined, y == "Teen Birth Rate (White)")
count_teenbirthwhite<- ldply(detteenbirthwhite,function(c) sum(c=="Teen Birth Rate (White)"))
freqteenbirthwhite = count_teenbirthwhite[-c(2, 3),]
freqteenbirthwhite$Determinants= "Teen Birth Rate (White)"
prtteenbirthwhite = ldply(detteenbirthwhite, function(c) sum(c == "Protective"))
freqprtteenbirthwhite = prtteenbirthwhite[-c(1,2),]
freqteenbirthwhite$Protective = freqprtteenbirthwhite
desteenbirthwhite = ldply(detteenbirthwhite, function(c) sum(c == "Destructive"))      
freqdesteenbirthwhite = desteenbirthwhite[-c(1,2),]
freqteenbirthwhite$Destructive = freqdesteenbirthwhite

detincidencerate = subset(prtdescombined, y == "Incidence_Rate")
count_incidencerate<- ldply(detincidencerate,function(c) sum(c=="Incidence_Rate"))
freqincidencerate = count_incidencerate[-c(2, 3),]
freqincidencerate$Determinants= "Incidence Rate"
prtincidencerate = ldply(detincidencerate, function(c) sum(c == "Protective"))
freqprtincidencerate = prtincidencerate[-c(1,2),]
freqincidencerate$Protective = freqprtincidencerate
desincidencerate = ldply(detincidencerate, function(c) sum(c == "Destructive"))      
freqdesincidencerate = desincidencerate[-c(1,2),]
freqincidencerate$Destructive = freqdesincidencerate

detpreventablehospital = subset(prtdescombined, y == "Preventable Hospitalization Rate")
count_preventablehospital<- ldply(prtdescombined,function(c) sum(c=="Preventable Hospitalization Rate"))
freqpreventablehospital = count_preventablehospital[-c(2, 3),]
freqpreventablehospital$Determinants= "Preventable Hospitalization Rate"
prtpreventablehospital = ldply(detpreventablehospital, function(c) sum(c == "Protective"))
freqprtpreventablehospital = prtpreventablehospital[-c(1,2),]
freqpreventablehospital$Protective = freqprtpreventablehospital
despreventablehospital = ldply(detpreventablehospital, function(c) sum(c == "Destructive"))      
freqdespreventablehospital = despreventablehospital[-c(1,2),]
freqpreventablehospital$Destructive = freqdespreventablehospital

detpreventablehospitalhispanic = subset(prtdescombined, y == "Preventable Hosp. Rate (Hispanic)")
count_preventablehospitalhispanic<- ldply(prtdescombined,function(c) sum(c=="Preventable Hosp. Rate (Hispanic)"))
freqpreventablehospitalhispanic = count_preventablehospitalhispanic[-c(2, 3),]
freqpreventablehospitalhispanic$Determinants= "Preventable Hosp. Rate (Hispanic)"
prtpreventablehospitalhispanic = ldply(detpreventablehospitalhispanic, function(c) sum(c == "Protective"))
freqprtpreventablehospitalhispanic = prtpreventablehospitalhispanic[-c(1,2),]
freqpreventablehospitalhispanic$Protective = freqprtpreventablehospitalhispanic
despreventablehospitalhispanic = ldply(detpreventablehospitalhispanic, function(c) sum(c == "Destructive"))      
freqdespreventablehospitalhispanic = despreventablehospitalhispanic[-c(1,2),]
freqpreventablehospitalhispanic$Destructive = freqdespreventablehospitalhispanic

detpreventablehospitalwhite = subset(prtdescombined, y == "Preventable Hosp. Rate (White)")
count_preventablehospitalwhite<- ldply(prtdescombined,function(c) sum(c=="Preventable Hosp. Rate (White)"))
freqpreventablehospitalwhite = count_preventablehospitalwhite[-c(2, 3),]
freqpreventablehospitalwhite$Determinants= "Preventable Hosp. Rate (White)"
prtpreventablehospitalwhite = ldply(detpreventablehospitalwhite, function(c) sum(c == "Protective"))
freqprtpreventablehospitalwhite = prtpreventablehospitalwhite[-c(1,2),]
freqpreventablehospitalwhite$Protective = freqprtpreventablehospitalwhite
despreventablehospitalwhite = ldply(detpreventablehospitalwhite, function(c) sum(c == "Destructive"))      
freqdespreventablehospitalwhite = despreventablehospitalwhite[-c(1,2),]
freqpreventablehospitalwhite$Destructive = freqdespreventablehospitalwhite

detscreenedhispanic = subset(prtdescombined, y == "% Screened (Hispanic)")
count_screenedhispanic<- ldply(prtdescombined,function(c) sum(c=="% Screened (Hispanic)"))
freqscreenedhispanic = count_screenedhispanic[-c(2, 3),]
freqscreenedhispanic$Determinants= "% Screened (Hispanic)"
prtscreenedhispanic = ldply(detscreenedhispanic, function(c) sum(c == "Protective"))
freqprtscreenedhispanic = prtscreenedhispanic[-c(1,2),]
freqscreenedhispanic$Protective = freqprtscreenedhispanic
desscreenedhispanic = ldply(detscreenedhispanic, function(c) sum(c == "Destructive"))      
freqdesscreenedhispanic = desscreenedhispanic[-c(1,2),]
freqscreenedhispanic$Destructive = freqdesscreenedhispanic

detchildrenpoverty = subset(prtdescombined, y == "% Children in Poverty (White)")
count_childrenpoverty<- ldply(prtdescombined,function(c) sum(c=="% Children in Poverty (White)"))
freqchildrenpoverty = count_childrenpoverty[-c(2, 3),]
freqchildrenpoverty$Determinants= "% Children in Poverty (White)"
prtchildrenpoverty = ldply(detchildrenpoverty, function(c) sum(c == "Protective"))
freqprtchildrenpoverty = prtchildrenpoverty[-c(1,2),]
freqchildrenpoverty$Protective = freqprtchildrenpoverty
deschildrenpoverty = ldply(detchildrenpoverty, function(c) sum(c == "Destructive"))      
freqdeschildrenpoverty = deschildrenpoverty[-c(1,2),]
freqchildrenpoverty$Destructive = freqdeschildrenpoverty

detincomeratio = subset(prtdescombined, y == "Income Ratio")
count_incomeratio<- ldply(prtdescombined,function(c) sum(c=="Income Ratio"))
freqincomeratio = count_incomeratio[-c(2, 3),]
freqincomeratio$Determinants= "Income Ratio"
prtincomeratio = ldply(detincomeratio, function(c) sum(c == "Protective"))
freqprtincomeratio = prtincomeratio[-c(1,2),]
freqincomeratio$Protective = freqprtincomeratio
desincomeratio = ldply(detincomeratio, function(c) sum(c == "Destructive"))      
freqdesincomeratio = desincomeratio[-c(1,2),]
freqincomeratio$Destructive = freqdesincomeratio

detsingleparent = subset(prtdescombined, y == "% Single-Parent Households")
count_singleparent<- ldply(prtdescombined,function(c) sum(c=="% Single-Parent Households"))
freqsingleparent = count_singleparent[-c(2, 3),]
freqsingleparent$Determinants= "% Single-Parent Households"
prtsingleparent = ldply(detsingleparent, function(c) sum(c == "Protective"))
freqprtsingleparent = prtsingleparent[-c(1,2),]
freqsingleparent$Protective = freqprtsingleparent
dessingleparent = ldply(detsingleparent, function(c) sum(c == "Destructive"))      
freqdessingleparent = dessingleparent[-c(1,2),]
freqsingleparent$Destructive = freqdessingleparent

detinjurydeathrate = subset(prtdescombined, y == "Injury Death Rate")
count_injurydeathrate<- ldply(prtdescombined,function(c) sum(c=="Injury Death Rate"))
freqinjurydeathrate = count_injurydeathrate[-c(2, 3),]
freqinjurydeathrate$Determinants= "Injury Death Rate"
prtinjurydeathrate = ldply(detinjurydeathrate, function(c) sum(c == "Protective"))
freqprtinjurydeathrate = prtinjurydeathrate[-c(1,2),]
freqinjurydeathrate$Protective = freqprtinjurydeathrate
desinjurydeathrate = ldply(detinjurydeathrate, function(c) sum(c == "Destructive"))      
freqdesinjurydeathrate = desinjurydeathrate[-c(1,2),]
freqinjurydeathrate$Destructive = freqdesinjurydeathrate

detinjurydeathratehispanic = subset(prtdescombined, y == "Injury Death Rate (Hispanic)")
count_injurydeathratehispanic<- ldply(prtdescombined,function(c) sum(c=="Injury Death Rate (Hispanic)"))
freqinjurydeathratehispanic = count_injurydeathratehispanic[-c(2, 3),]
freqinjurydeathratehispanic$Determinants= "Injury Death Rate (Hispanic)"
prtinjurydeathratehispanic = ldply(detinjurydeathratehispanic, function(c) sum(c == "Protective"))
freqprtinjurydeathratehispanic = prtinjurydeathratehispanic[-c(1,2),]
freqinjurydeathratehispanic$Protective = freqprtinjurydeathratehispanic
desinjurydeathratehispanic = ldply(detinjurydeathratehispanic, function(c) sum(c == "Destructive"))      
freqdesinjurydeathratehispanic = desinjurydeathratehispanic[-c(1,2),]
freqinjurydeathratehispanic$Destructive = freqdesinjurydeathratehispanic

detinjurydeathratewhite = subset(prtdescombined, y == "Injury Death Rate (White)")
count_injurydeathratewhite<- ldply(prtdescombined,function(c) sum(c=="Injury Death Rate (White)"))
freqinjurydeathratewhite = count_injurydeathratewhite[-c(2, 3),]
freqinjurydeathratewhite$Determinants= "Injury Death Rate (White)"
prtinjurydeathratewhite = ldply(detinjurydeathratewhite, function(c) sum(c == "Protective"))
freqprtinjurydeathratewhite = prtinjurydeathratewhite[-c(1,2),]
freqinjurydeathratewhite$Protective = freqprtinjurydeathratewhite
desinjurydeathratewhite = ldply(detinjurydeathratewhite, function(c) sum(c == "Destructive"))   
freqdesinjurydeathratewhite = desinjurydeathratewhite[-c(1,2),]
freqinjurydeathratewhite$Destructive = freqdesinjurydeathratewhite

detinadequatefacilities = subset(prtdescombined, y == "Inadequate Facilities")
count_inadequatefacilities<- ldply(prtdescombined,function(c) sum(c=="Inadequate Facilities"))
freqinadequatefacilities = count_inadequatefacilities[-c(2, 3),]
freqinadequatefacilities$Determinants= "Inadequate Facilities"
prtinadequatefacilities = ldply(detinadequatefacilities, function(c) sum(c == "Protective"))
freqprtinadequatefacilities = prtinadequatefacilities[-c(1,2),]
freqinadequatefacilities$Protective = freqprtinadequatefacilities
desinadequatefacilities = ldply(detinadequatefacilities, function(c) sum(c == "Destructive"))      
freqdesinadequatefacilities = desinadequatefacilities[-c(1,2),]
freqinadequatefacilities$Destructive = freqdesinadequatefacilities

detdrivealonehispanic = subset(prtdescombined, y == "% Drive Alone (Hispanic)")
count_drivealonehispanic<- ldply(prtdescombined,function(c) sum(c=="% Drive Alone (Hispanic)"))
freqdrivealonehispanic = count_drivealonehispanic[-c(2, 3),]
freqdrivealonehispanic$Determinants= "% Drive Alone (Hispanic)"
prtdrivealonehispanic = ldply(detdrivealonehispanic, function(c) sum(c == "Protective"))
freqprtdrivealonehispanic = prtdrivealonehispanic[-c(1,2),]
freqdrivealonehispanic$Protective = freqprtdrivealonehispanic
desdrivealonehispanic = ldply(detdrivealonehispanic, function(c) sum(c == "Destructive"))      
freqdesdrivealonehispanic = desdrivealonehispanic[-c(1,2),]
freqdrivealonehispanic$Destructive = freqdesdrivealonehispanic

detdrivealonewhite = subset(prtdescombined, y == "% Drive Alone (White)")
count_drivealonewhite<- ldply(prtdescombined,function(c) sum(c=="% Drive Alone (White)"))
freqdrivealonewhite = count_drivealonewhite[-c(2, 3),]
freqdrivealonewhite$Determinants= "% Drive Alone (White)"
prtdrivealonewhite = ldply(detdrivealonewhite, function(c) sum(c == "Protective"))
freqprtdrivealonewhite = prtdrivealonewhite[-c(1,2),]
freqdrivealonewhite$Protective = freqprtdrivealonewhite
desdrivealonewhite = ldply(detdrivealonewhite, function(c) sum(c == "Destructive"))      
freqdesdrivealonewhite = desdrivealonewhite[-c(1,2),]
freqdrivealonewhite$Destructive = freqdesdrivealonewhite

detprecoviddeathrate = subset(prtdescombined, y == "pre_covid_death_rate")
count_precoviddeathrate<- ldply(prtdescombined,function(c) sum(c=="pre_covid_death_rate"))
freqprecoviddeathrate = count_precoviddeathrate[-c(2, 3),]
freqprecoviddeathrate$Determinants= "PreCovid Death Rate"
prtprecoviddeathrate = ldply(detprecoviddeathrate, function(c) sum(c == "Protective"))
freqprtprecoviddeathrate = prtprecoviddeathrate[-c(1,2),]
freqprecoviddeathrate$Protective = freqprtprecoviddeathrate
desprecoviddeathrate = ldply(detprecoviddeathrate, function(c) sum(c == "Destructive"))      
freqdesprecoviddeathrate = desprecoviddeathrate[-c(1,2),]
freqprecoviddeathrate$Destructive = freqdesprecoviddeathrate

detageadjustedhispanic = subset(prtdescombined, y == "Age-Adjusted Mortality (Hispanic)")
count_ageadjustedhispanic<- ldply(prtdescombined,function(c) sum(c=="Age-Adjusted Mortality (Hispanic)"))
freqageadjustedhispanic = count_ageadjustedhispanic[-c(2, 3),]
freqageadjustedhispanic$Determinants= "Age-Adjusted Mortality (Hispanic)"
prtageadjustedhispanic = ldply(detageadjustedhispanic, function(c) sum(c == "Protective"))
freqprtageadjustedhispanic = prtageadjustedhispanic[-c(1,2),]
freqageadjustedhispanic$Protective = freqprtageadjustedhispanic
desageadjustedhispanic = ldply(detageadjustedhispanic, function(c) sum(c == "Destructive"))      
freqdesageadjustedhispanic = desageadjustedhispanic[-c(1,2),]
freqageadjustedhispanic$Destructive = freqdesageadjustedhispanic

detageadjustedwhite = subset(prtdescombined, y == "Age-Adjusted Mortality (White)")
count_ageadjustedwhite<- ldply(prtdescombined,function(c) sum(c=="Age-Adjusted Mortality (White)"))
freqageadjustedwhite = count_ageadjustedwhite[-c(2, 3),]
freqageadjustedwhite$Determinants= "Age-Adjusted Mortality (White)"
prtageadjustedwhite = ldply(detageadjustedwhite, function(c) sum(c == "Protective"))
freqprtageadjustedwhite = prtageadjustedwhite[-c(1,2),]
freqageadjustedwhite$Protective = freqprtageadjustedwhite
desageadjustedwhite = ldply(detageadjustedwhite, function(c) sum(c == "Destructive"))      
freqdesageadjustedwhite = desageadjustedwhite[-c(1,2),]
freqageadjustedwhite$Destructive = freqdesageadjustedwhite

detpct_diabetes = subset(prtdescombined, y == "pct_diabetes")
count_pct_diabetes<- ldply(prtdescombined,function(c) sum(c=="pct_diabetes"))
freqpct_diabetes = count_pct_diabetes[-c(2, 3),]
freqpct_diabetes$Determinants= "pct_diabetes"
prtpct_diabetes = ldply(detpct_diabetes, function(c) sum(c == "Protective"))
freqprtpct_diabetes = prtpct_diabetes[-c(1,2),]
freqpct_diabetes$Protective = freqprtpct_diabetes
despct_diabetes = ldply(detpct_diabetes, function(c) sum(c == "Destructive"))      
freqdespct_diabetes = despct_diabetes[-c(1,2),]
freqpct_diabetes$Destructive = freqdespct_diabetes

detfoodinsecure = subset(prtdescombined, y == "% Food Insecure")
count_foodinsecure<- ldply(prtdescombined,function(c) sum(c=="% Food Insecure"))
freqfoodinsecure = count_foodinsecure[-c(2, 3),]
freqfoodinsecure$Determinants= "% Food Insecure"
prtfoodinsecure = ldply(detfoodinsecure, function(c) sum(c == "Protective"))
freqprtfoodinsecure = prtfoodinsecure[-c(1,2),]
freqfoodinsecure$Protective = freqprtfoodinsecure
desfoodinsecure = ldply(detfoodinsecure, function(c) sum(c == "Destructive"))      
freqdesfoodinsecure = desfoodinsecure[-c(1,2),]
freqfoodinsecure$Destructive = freqdesfoodinsecure

detlimitedhealthyfood = subset(prtdescombined, y == "% Limited Access to Healthy Foods")
count_limitedhealthyfood<- ldply(prtdescombined,function(c) sum(c=="% Limited Access to Healthy Foods"))
freqlimitedhealthyfood = count_limitedhealthyfood[-c(2, 3),]
freqlimitedhealthyfood$Determinants= "% Limited Access to Healthy Foods"
prtlimitedhealthyfood = ldply(detlimitedhealthyfood, function(c) sum(c == "Protective"))
freqprtlimitedhealthyfood = prtlimitedhealthyfood[-c(1,2),]
freqlimitedhealthyfood$Protective = freqprtlimitedhealthyfood
deslimitedhealthyfood = ldply(detlimitedhealthyfood, function(c) sum(c == "Destructive"))      
freqdeslimitedhealthyfood = deslimitedhealthyfood[-c(1,2),]
freqlimitedhealthyfood$Destructive = freqdeslimitedhealthyfood

detmotormortality = subset(prtdescombined, y == "Motor Vehicle Mortality Rate")
count_motormortality<- ldply(prtdescombined,function(c) sum(c=="Motor Vehicle Mortality Rate"))
freqmotormortality = count_motormortality[-c(2, 3),]
freqmotormortality$Determinants= "Motor Vehicle Mortality Rate"
prtmotormortality = ldply(detmotormortality, function(c) sum(c == "Protective"))
freqprtmotormortality = prtmotormortality[-c(1,2),]
freqmotormortality$Protective = freqprtmotormortality
desmotormortality = ldply(detmotormortality, function(c) sum(c == "Destructive"))      
freqdesmotormortality = desmotormortality[-c(1,2),]
freqmotormortality$Destructive = freqdesmotormortality

detinsufficientsleep = subset(prtdescombined, y == "% Insufficient Sleep")
count_insufficientsleep<- ldply(prtdescombined,function(c) sum(c=="% Insufficient Sleep"))
freqinsufficientsleep = count_insufficientsleep[-c(2, 3),]
freqinsufficientsleep$Determinants= "% Insufficient Sleep"
prtinsufficientsleep = ldply(detinsufficientsleep, function(c) sum(c == "Protective"))
freqprtinsufficientsleep = prtinsufficientsleep[-c(1,2),]
freqinsufficientsleep$Protective = freqprtinsufficientsleep
desinsufficientsleep = ldply(detinsufficientsleep, function(c) sum(c == "Destructive"))      
freqdesinsufficientsleep = desinsufficientsleep[-c(1,2),]
freqinsufficientsleep$Destructive = freqdesinsufficientsleep

detsegregationindex = subset(prtdescombined, y == "Segregation Index")
count_segregationindex<- ldply(prtdescombined,function(c) sum(c=="Segregation Index"))
freqsegregationindex = count_segregationindex[-c(2, 3),]
freqsegregationindex$Determinants= "Segregation Index"
prtsegregationindex = ldply(detsegregationindex, function(c) sum(c == "Protective"))
freqprtsegregationindex = prtsegregationindex[-c(1,2),]
freqsegregationindex$Protective = freqprtsegregationindex
dessegregationindex = ldply(detsegregationindex, function(c) sum(c == "Destructive"))      
freqdessegregationindex = dessegregationindex[-c(1,2),]
freqsegregationindex$Destructive = freqdessegregationindex

dethomeowners = subset(prtdescombined, y == "% Homeowners")
count_homeowners<- ldply(prtdescombined,function(c) sum(c=="% Homeowners"))
freqhomeowners = count_homeowners[-c(2, 3),]
freqhomeowners$Determinants= "% Homeowners"
prthomeowners = ldply(dethomeowners, function(c) sum(c == "Protective"))
freqprthomeowners = prthomeowners[-c(1,2),]
freqhomeowners$Protective = freqprthomeowners
deshomeowners = ldply(dethomeowners, function(c) sum(c == "Destructive"))      
freqdeshomeowners = deshomeowners[-c(1,2),]
freqhomeowners$Destructive = freqdeshomeowners

detpct_age65 = subset(prtdescombined, y == "pct_age65")
count_pct_age65<- ldply(prtdescombined,function(c) sum(c=="pct_age65"))
freqpct_age65 = count_pct_age65[-c(2, 3),]
freqpct_age65$Determinants= "pct_age65"
prtpct_age65 = ldply(detpct_age65, function(c) sum(c == "Protective"))
freqprtpct_age65 = prtpct_age65[-c(1,2),]
freqpct_age65$Protective = freqprtpct_age65
despct_age65 = ldply(detpct_age65, function(c) sum(c == "Destructive"))      
freqdespct_age65 = despct_age65[-c(1,2),]
freqpct_age65$Destructive = freqdespct_age65

detblack = subset(prtdescombined, y == "% Black")
count_black<- ldply(prtdescombined,function(c) sum(c=="% Black"))
freqblack = count_black[-c(2, 3),]
freqblack$Determinants= "% Black"
prtblack = ldply(detblack, function(c) sum(c == "Protective"))
freqprtblack = prtblack[-c(1,2),]
freqblack$Protective = freqprtblack
desblack = ldply(detblack, function(c) sum(c == "Destructive"))      
freqdesblack = desblack[-c(1,2),]
freqblack$Destructive = freqdesblack

detindianalaska = subset(prtdescombined, y == "% American Indian & Alaska Native")
count_indianalaska<- ldply(prtdescombined,function(c) sum(c=="% American Indian & Alaska Native"))
freqindianalaska = count_indianalaska[-c(2, 3),]
freqindianalaska$Determinants= "% American Indian & Alaska Native"
prtindianalaska = ldply(detindianalaska, function(c) sum(c == "Protective"))
freqprtindianalaska = prtindianalaska[-c(1,2),]
freqindianalaska$Protective = freqprtindianalaska
desindianalaska = ldply(detindianalaska, function(c) sum(c == "Destructive"))      
freqdesindianalaska = desindianalaska[-c(1,2),]
freqindianalaska$Destructive = freqdesindianalaska

dethawaiian = subset(prtdescombined, y == "% Native Hawaiian/Other Pacific Islander")
count_hawaiian<- ldply(prtdescombined,function(c) sum(c=="% Native Hawaiian/Other Pacific Islander"))
freqhawaiian = count_hawaiian[-c(2, 3),]
freqhawaiian$Determinants= "% Native Hawaiian/Other Pacific Islander"
prthawaiian = ldply(dethawaiian, function(c) sum(c == "Protective"))
freqprthawaiian = prthawaiian[-c(1,2),]
freqhawaiian$Protective = freqprthawaiian
deshawaiian = ldply(dethawaiian, function(c) sum(c == "Destructive"))      
freqdeshawaiian = deshawaiian[-c(1,2),]
freqhawaiian$Destructive = freqdeshawaiian

detnonhispanicwhite = subset(prtdescombined, y == "% Non-Hispanic White")
count_nonhispanicwhite<- ldply(prtdescombined,function(c) sum(c=="% Non-Hispanic White"))
freqnonhispanicwhite = count_nonhispanicwhite[-c(2, 3),]
freqnonhispanicwhite$Determinants= "% Non-Hispanic White"
prtnonhispanicwhite = ldply(detnonhispanicwhite, function(c) sum(c == "Protective"))
freqprtnonhispanicwhite = prtnonhispanicwhite[-c(1,2),]
freqnonhispanicwhite$Protective = freqprtnonhispanicwhite
desnonhispanicwhite = ldply(detnonhispanicwhite, function(c) sum(c == "Destructive"))      
freqdesnonhispanicwhite = desnonhispanicwhite[-c(1,2),]
freqnonhispanicwhite$Destructive = freqdesnonhispanicwhite

detadultasthma = subset(prtdescombined, y == "AdultAsthma")
count_adultasthma<- ldply(prtdescombined,function(c) sum(c=="AdultAsthma"))
freqadultasthma = count_adultasthma[-c(2, 3),]
freqadultasthma$Determinants= "Adult Asthma"
prtadultasthma = ldply(detadultasthma, function(c) sum(c == "Protective"))
freqprtadultasthma = prtadultasthma[-c(1,2),]
freqadultasthma$Protective = freqprtadultasthma
desadultasthma = ldply(detadultasthma, function(c) sum(c == "Destructive"))      
freqdesadultasthma = desadultasthma[-c(1,2),]
freqadultasthma$Destructive = freqdesadultasthma

dethouseholdincomeblack = subset(prtdescombined, y == "Household Income (Black)")
count_householdincomeblack<- ldply(prtdescombined,function(c) sum(c=="Household Income (Black)"))
freqhouseholdincomeblack = count_householdincomeblack[-c(2, 3),]
freqhouseholdincomeblack$Determinants= "Household Income (Black)"
prthouseholdincomeblack = ldply(dethouseholdincomeblack, function(c) sum(c == "Protective"))
freqprthouseholdincomeblack = prthouseholdincomeblack[-c(1,2),]
freqhouseholdincomeblack$Protective = freqprthouseholdincomeblack
deshouseholdincomeblack = ldply(dethouseholdincomeblack, function(c) sum(c == "Destructive")) 
freqdeshouseholdincomeblack = deshouseholdincomeblack[-c(1,2),]
freqhouseholdincomeblack$Destructive = freqdeshouseholdincomeblack

detmean_summer_rm = subset(prtdescombined, y == "mean_summer_rm")
count_mean_summer_rm<- ldply(prtdescombined,function(c) sum(c=="mean_summer_rm"))
freqmean_summer_rm = count_mean_summer_rm[-c(2, 3),]
freqmean_summer_rm$Determinants= "mean_summer_rm"
prtmean_summer_rm = ldply(detmean_summer_rm, function(c) sum(c == "Protective"))
freqprtmean_summer_rm = prtmean_summer_rm[-c(1,2),]
freqmean_summer_rm$Protective = freqprtmean_summer_rm
desmean_summer_rm = ldply(detmean_summer_rm, function(c) sum(c == "Destructive"))      
freqdesmean_summer_rm = desmean_summer_rm[-c(1,2),]
freqmean_summer_rm$Destructive = freqdesmean_summer_rm

detpct_owner_occ = subset(prtdescombined, y == "pct_owner_occ")
count_pct_owner_occ<- ldply(prtdescombined,function(c) sum(c=="pct_owner_occ"))
freqpct_owner_occ = count_pct_owner_occ[-c(2, 3),]
freqpct_owner_occ$Determinants= "pct_owner_occ"
prtpct_owner_occ = ldply(detpct_owner_occ, function(c) sum(c == "Protective"))
freqprtpct_owner_occ = prtpct_owner_occ[-c(1,2),]
freqpct_owner_occ$Protective = freqprtpct_owner_occ
despct_owner_occ = ldply(detpct_owner_occ, function(c) sum(c == "Destructive"))      
freqdespct_owner_occ = despct_owner_occ[-c(1,2),]
freqpct_owner_occ$Destructive = freqdespct_owner_occ

detpoverty = subset(prtdescombined, y == "poverty")
count_poverty<- ldply(prtdescombined,function(c) sum(c=="poverty"))
freqpoverty = count_poverty[-c(2, 3),]
freqpoverty$Determinants= "poverty"
prtpoverty = ldply(detpoverty, function(c) sum(c == "Protective"))
freqprtpoverty = prtpoverty[-c(1,2),]
freqpoverty$Protective = freqprtpoverty
despoverty = ldply(detpoverty, function(c) sum(c == "Destructive"))      
freqdespoverty = despoverty[-c(1,2),]
freqpoverty$Destructive = freqdespoverty

detmentalproviderrate = subset(prtdescombined, y == "Mental Health Provider Rate")
count_mentalproviderrate<- ldply(prtdescombined,function(c) sum(c=="Mental Health Provider Rate"))
freqmentalproviderrate = count_mentalproviderrate[-c(2, 3),]
freqmentalproviderrate$Determinants= "Mental Health Provider Rate"
prtmentalproviderrate = ldply(detmentalproviderrate, function(c) sum(c == "Protective"))
freqprtmentalproviderrate = prtmentalproviderrate[-c(1,2),]
freqmentalproviderrate$Protective = freqprtmentalproviderrate
desmentalproviderrate = ldply(detmentalproviderrate, function(c) sum(c == "Destructive"))      
freqdesmentalproviderrate = desmentalproviderrate[-c(1,2),]
freqmentalproviderrate$Destructive = freqdesmentalproviderrate

detunhealthydays = subset(prtdescombined, y == "Average Number of Physically Unhealthy Days")
count_unhealthydays<- ldply(prtdescombined,function(c) sum(c=="Average Number of Physically Unhealthy Days"))
frequnhealthydays = count_unhealthydays[-c(2, 3),]
frequnhealthydays$Determinants= "Average Number of Physically Unhealthy Days"
prtunhealthydays = ldply(detunhealthydays, function(c) sum(c == "Protective"))
freqprtunhealthydays = prtunhealthydays[-c(1,2),]
frequnhealthydays$Protective = freqprtunhealthydays
desunhealthydays = ldply(detunhealthydays, function(c) sum(c == "Destructive"))      
freqdesunhealthydays = desunhealthydays[-c(1,2),]
frequnhealthydays$Destructive = freqdesunhealthydays

detdrivealonework = subset(prtdescombined, y == "% Drive Alone to Work")
count_drivealonework<- ldply(prtdescombined,function(c) sum(c=="% Drive Alone to Work"))
freqdrivealonework = count_drivealonework[-c(2, 3),]
freqdrivealonework$Determinants= "% Drive Alone to Work"
prtdrivealonework = ldply(detdrivealonework, function(c) sum(c == "Protective"))
freqprtdrivealonework = prtdrivealonework[-c(1,2),]
freqdrivealonework$Protective = freqprtdrivealonework
desdrivealonework = ldply(detdrivealonework, function(c) sum(c == "Destructive"))      
freqdesdrivealonework = desdrivealonework[-c(1,2),]
freqdrivealonework$Destructive = freqdesdrivealonework

det20percentileincome = subset(prtdescombined, y == "20th Percentile Income")
count_20percentileincome<- ldply(prtdescombined,function(c) sum(c=="20th Percentile Income"))
freq20percentileincome = count_20percentileincome[-c(2, 3),]
freq20percentileincome$Determinants= "20th Percentile Income"
prt20percentileincome = ldply(det20percentileincome, function(c) sum(c == "Protective"))
freqprt20percentileincome = prt20percentileincome[-c(1,2),]
freq20percentileincome$Protective = freqprt20percentileincome
des20percentileincome = ldply(det20percentileincome, function(c) sum(c == "Destructive"))      
freqdes20percentileincome = des20percentileincome[-c(1,2),]
freq20percentileincome$Destructive = freqdes20percentileincome

detlongcommutedrivealone = subset(prtdescombined, y == "% Long Commute - Drives Alone")
count_longcommutedrivealone<- ldply(prtdescombined,function(c) sum(c=="% Long Commute - Drives Alone"))
freqlongcommutedrivealone = count_longcommutedrivealone[-c(2, 3),]
freqlongcommutedrivealone$Determinants= "% Long Commute - Drives Alone"
prtlongcommutedrivealone = ldply(detlongcommutedrivealone, function(c) sum(c == "Protective"))
freqprtlongcommutedrivealone = prtlongcommutedrivealone[-c(1,2),]
freqlongcommutedrivealone$Protective = freqprtlongcommutedrivealone
deslongcommutedrivealone = ldply(detlongcommutedrivealone, function(c) sum(c == "Destructive")) 
freqdeslongcommutedrivealone = deslongcommutedrivealone[-c(1,2),]
freqlongcommutedrivealone$Destructive = freqdeslongcommutedrivealone

detsocialassociationrate = subset(prtdescombined, y == "Social Association Rate")
count_socialassociationrate<- ldply(prtdescombined,function(c) sum(c=="Social Association Rate"))
freqsocialassociationrate = count_socialassociationrate[-c(2, 3),]
freqsocialassociationrate$Determinants= "Social Association Rate"
prtsocialassociationrate = ldply(detsocialassociationrate, function(c) sum(c == "Protective"))
freqprtsocialassociationrate = prtsocialassociationrate[-c(1,2),]
freqsocialassociationrate$Protective = freqprtsocialassociationrate
dessocialassociationrate = ldply(detsocialassociationrate, function(c) sum(c == "Destructive")) 
freqdessocialassociationrate = dessocialassociationrate[-c(1,2),]
freqsocialassociationrate$Destructive = freqdessocialassociationrate

dettrafficvolumepermeter = subset(prtdescombined, y == "Average Traffic Volume per Meter of Major Roadways")
count_trafficvolumepermeter<- ldply(prtdescombined,function(c) sum(c=="Average Traffic Volume per Meter of Major Roadways"))
freqtrafficvolumepermeter = count_trafficvolumepermeter[-c(2, 3),]
freqtrafficvolumepermeter$Determinants= "Average Traffic Volume per Meter of Major Roadways"
prttrafficvolumepermeter = ldply(dettrafficvolumepermeter, function(c) sum(c == "Protective"))
freqprttrafficvolumepermeter = prttrafficvolumepermeter[-c(1,2),]
freqtrafficvolumepermeter$Protective = freqprttrafficvolumepermeter
destrafficvolumepermeter = ldply(dettrafficvolumepermeter, function(c) sum(c == "Destructive")) 
freqdestrafficvolumepermeter = destrafficvolumepermeter[-c(1,2),]
freqtrafficvolumepermeter$Destructive = freqdestrafficvolumepermeter

detmentalunhealthydays = subset(prtdescombined, y == "Average Number of Mentally Unhealthy Days")
count_mentalunhealthydays<- ldply(prtdescombined,function(c) sum(c=="Average Number of Mentally Unhealthy Days"))
freqmentalunhealthydays = count_mentalunhealthydays[-c(2, 3),]
freqmentalunhealthydays$Determinants= "Average Number of Mentally Unhealthy Days"
prtmentalunhealthydays = ldply(detmentalunhealthydays, function(c) sum(c == "Protective"))
freqprtmentalunhealthydays = prtmentalunhealthydays[-c(1,2),]
freqmentalunhealthydays$Protective = freqprtmentalunhealthydays
desmentalunhealthydays = ldply(detmentalunhealthydays, function(c) sum(c == "Destructive"))      
freqdesmentalunhealthydays = desmentalunhealthydays[-c(1,2),]
freqmentalunhealthydays$Destructive = freqdesmentalunhealthydays

detmentaldistressfrequent = subset(prtdescombined, y == "% Frequent Mental Distress")
count_mentaldistressfrequent<- ldply(prtdescombined,function(c) sum(c=="% Frequent Mental Distress"))
freqmentaldistressfrequent = count_mentaldistressfrequent[-c(2, 3),]
freqmentaldistressfrequent$Determinants= "% Frequent Mental Distress"
prtmentaldistressfrequent = ldply(detmentaldistressfrequent, function(c) sum(c == "Protective"))
freqprtmentaldistressfrequent = prtmentaldistressfrequent[-c(1,2),]
freqmentaldistressfrequent$Protective = freqprtmentaldistressfrequent
desmentaldistressfrequent = ldply(detmentaldistressfrequent, function(c) sum(c == "Destructive"))
freqdesmentaldistressfrequent = desmentaldistressfrequent[-c(1,2),]
freqmentaldistressfrequent$Destructive = freqdesmentaldistressfrequent

detwhitechildpoverty = subset(prtdescombined, y == "% Children in Poverty")
count_whitechildpoverty<- ldply(prtdescombined,function(c) sum(c=="% Children in Poverty"))
freqwhitechildpoverty = count_whitechildpoverty[-c(2, 3),]
freqwhitechildpoverty$Determinants= "% Children in Poverty"
prtwhitechildpoverty = ldply(detwhitechildpoverty, function(c) sum(c == "Protective"))
freqprtwhitechildpoverty = prtwhitechildpoverty[-c(1,2),]
freqwhitechildpoverty$Protective = freqprtwhitechildpoverty
deswhitechildpoverty = ldply(detwhitechildpoverty, function(c) sum(c == "Destructive"))      
freqdeswhitechildpoverty = deswhitechildpoverty[-c(1,2),]
freqwhitechildpoverty$Destructive = freqdeswhitechildpoverty

detmean_pm25 = subset(prtdescombined, y == "mean_pm25")
count_mean_pm25<- ldply(prtdescombined,function(c) sum(c=="mean_pm25"))
freqmean_pm25 = count_mean_pm25[-c(2, 3),]
freqmean_pm25$Determinants= "mean_pm25"
prtmean_pm25 = ldply(detmean_pm25, function(c) sum(c == "Protective"))
freqprtmean_pm25 = prtmean_pm25[-c(1,2),]
freqmean_pm25$Protective = freqprtmean_pm25
desmean_pm25 = ldply(detmean_pm25, function(c) sum(c == "Destructive"))      
freqdesmean_pm25 = desmean_pm25[-c(1,2),]
freqmean_pm25$Destructive = freqdesmean_pm25

detLungCancer = subset(prtdescombined, y == "LungCancer")
count_LungCancer<- ldply(prtdescombined,function(c) sum(c=="LungCancer"))
freqLungCancer = count_LungCancer[-c(2, 3),]
freqLungCancer$Determinants= "LungCancer"
prtLungCancer = ldply(detLungCancer, function(c) sum(c == "Protective"))
freqprtLungCancer = prtLungCancer[-c(1,2),]
freqLungCancer$Protective = freqprtLungCancer
desLungCancer = ldply(detLungCancer, function(c) sum(c == "Destructive"))      
freqdesLungCancer = desLungCancer[-c(1,2),]
freqLungCancer$Destructive = freqdesLungCancer

detfemale = subset(prtdescombined, y == "% Female")
count_female<- ldply(prtdescombined,function(c) sum(c=="% Female"))
freqfemale = count_female[-c(2, 3),]
freqfemale$Determinants= "% Female"
prtfemale = ldply(detfemale, function(c) sum(c == "Protective"))
freqprtfemale = prtfemale[-c(1,2),]
freqfemale$Protective = freqprtfemale
desfemale = ldply(detfemale, function(c) sum(c == "Destructive"))      
freqdesfemale = desfemale[-c(1,2),]
freqfemale$Destructive = freqdesfemale

dethispanic = subset(prtdescombined, y == "% Hispanic")
count_hispanic<- ldply(prtdescombined,function(c) sum(c=="% Hispanic"))
freqhispanic = count_hispanic[-c(2, 3),]
freqhispanic$Determinants= "% Hispanic"
prthispanic = ldply(dethispanic, function(c) sum(c == "Protective"))
freqprthispanic = prthispanic[-c(1,2),]
freqhispanic$Protective = freqprthispanic
deshispanic = ldply(dethispanic, function(c) sum(c == "Destructive"))      
freqdeshispanic = deshispanic[-c(1,2),]
freqhispanic$Destructive = freqdeshispanic

detnolessthan18 = subset(prtdescombined, y == "# less than 18 years of age")
count_nolessthan18<- ldply(prtdescombined,function(c) sum(c=="# less than 18 years of age"))
freqnolessthan18 = count_nolessthan18[-c(2, 3),]
freqnolessthan18$Determinants= "# less than 18 years of age"
prtnolessthan18 = ldply(detnolessthan18, function(c) sum(c == "Protective"))
freqprtnolessthan18 = prtnolessthan18[-c(1,2),]
freqnolessthan18$Protective = freqprtnolessthan18
desnolessthan18 = ldply(detnolessthan18, function(c) sum(c == "Destructive"))      
freqdesnolessthan18 = desnolessthan18[-c(1,2),]
freqnolessthan18$Destructive = freqdesnolessthan18

detnoblack = subset(prtdescombined, y == "# Black")
count_noblack<- ldply(prtdescombined,function(c) sum(c=="# Black"))
freqnoblack = count_noblack[-c(2, 3),]
freqnoblack$Determinants= "# Black"
prtnoblack = ldply(detnoblack, function(c) sum(c == "Protective"))
freqprtnoblack = prtnoblack[-c(1,2),]
freqnoblack$Protective = freqprtnoblack
desnoblack = ldply(detnoblack, function(c) sum(c == "Destructive"))      
freqdesnoblack = desnoblack[-c(1,2),]
freqnoblack$Destructive = freqdesnoblack

detnoindianalaska = subset(prtdescombined, y == "# American Indian & Alaska Native")
count_noindianalaska<- ldply(prtdescombined,function(c) sum(c=="# American Indian & Alaska Native"))
freqnoindianalaska = count_noindianalaska[-c(2, 3),]
freqnoindianalaska$Determinants= "# American Indian & Alaska Native"
prtnoindianalaska = ldply(detnoindianalaska, function(c) sum(c == "Protective"))
freqprtnoindianalaska = prtnoindianalaska[-c(1,2),]
freqnoindianalaska$Protective = freqprtnoindianalaska
desnoindianalaska = ldply(detnoindianalaska, function(c) sum(c == "Destructive"))      
freqdesnoindianalaska = desnoindianalaska[-c(1,2),]
freqnoindianalaska$Destructive = freqdesnoindianalaska

detnoasian = subset(prtdescombined, y == "# Asian")
count_noasian<- ldply(prtdescombined,function(c) sum(c=="# Asian"))
freqnoasian = count_noasian[-c(2, 3),]
freqnoasian$Determinants= "# Asian"
prtnoasian = ldply(detnoasian, function(c) sum(c == "Protective"))
freqprtnoasian = prtnoasian[-c(1,2),]
freqnoasian$Protective = freqprtnoasian
desnoasian = ldply(detnoasian, function(c) sum(c == "Destructive"))      
freqdesnoasian = desnoasian[-c(1,2),]
freqnoasian$Destructive = freqdesnoasian

detnohawaiian = subset(prtdescombined, y == "# Native Hawaiian/Other Pacific Islander")
count_nohawaiian<- ldply(prtdescombined,function(c) sum(c=="# Native Hawaiian/Other Pacific Islander"))
freqnohawaiian = count_nohawaiian[-c(2, 3),]
freqnohawaiian$Determinants= "# Native Hawaiian/Other Pacific Islander"
prtnohawaiian = ldply(detnohawaiian, function(c) sum(c == "Protective"))
freqprtnohawaiian = prtnohawaiian[-c(1,2),]
freqnohawaiian$Protective = freqprtnohawaiian
desnohawaiian = ldply(detnohawaiian, function(c) sum(c == "Destructive"))      
freqdesnohawaiian = desnohawaiian[-c(1,2),]
freqnohawaiian$Destructive = freqdesnohawaiian

detnohomeowners = subset(prtdescombined, y == "# Homeowners")
count_nohomeowners<- ldply(prtdescombined,function(c) sum(c=="# Homeowners"))
freqnohomeowners = count_nohomeowners[-c(2, 3),]
freqnohomeowners$Determinants= "# Homeowners"
prtnohomeowners = ldply(detnohomeowners, function(c) sum(c == "Protective"))
freqprtnohomeowners = prtnohomeowners[-c(1,2),]
freqnohomeowners$Protective = freqprtnohomeowners
desnohomeowners = ldply(detnohomeowners, function(c) sum(c == "Destructive"))      
freqdesnohomeowners = desnohomeowners[-c(1,2),]
freqnohomeowners$Destructive = freqdesnohomeowners

detnohouseholdwithseverecostburden = subset(prtdescombined, y == "# Households with Severe Cost Burden")
count_nohouseholdwithseverecostburden<- ldply(prtdescombined,function(c) sum(c=="# Households with Severe Cost Burden"))
freqnohouseholdwithseverecostburden = count_nohouseholdwithseverecostburden[-c(2, 3),]
freqnohouseholdwithseverecostburden$Determinants= "# Households with Severe Cost Burden"
prtnohouseholdwithseverecostburden = ldply(detnohouseholdwithseverecostburden, function(c) sum(c == "Protective"))
freqprtnohouseholdwithseverecostburden = prtnohouseholdwithseverecostburden[-c(1,2),]
freqnohouseholdwithseverecostburden$Protective = freqprtnohouseholdwithseverecostburden
desnohouseholdwithseverecostburden = ldply(detnohouseholdwithseverecostburden, function(c) sum(c == "Destructive"))      
freqdesnohouseholdwithseverecostburden = desnohouseholdwithseverecostburden[-c(1,2),]
freqnohouseholdwithseverecostburden$Destructive = freqdesnohouseholdwithseverecostburden

detseverehousingcostburden = subset(prtdescombined, y == "% Severe Housing Cost Burden")
count_severehousingcostburden<- ldply(prtdescombined,function(c) sum(c=="% Severe Housing Cost Burden"))
freqseverehousingcostburden = count_severehousingcostburden[-c(2, 3),]
freqseverehousingcostburden$Determinants= "% Severe Housing Cost Burden"
prtseverehousingcostburden = ldply(detseverehousingcostburden, function(c) sum(c == "Protective"))
freqprtseverehousingcostburden = prtseverehousingcostburden[-c(1,2),]
freqseverehousingcostburden$Protective = freqprtseverehousingcostburden
desseverehousingcostburden = ldply(detseverehousingcostburden, function(c) sum(c == "Destructive"))      
freqdesseverehousingcostburden = desseverehousingcostburden[-c(1,2),]
freqseverehousingcostburden$Destructive = freqdesseverehousingcostburden

detDenominator = subset(prtdescombined, y == "Denominator")
count_Denominator<- ldply(prtdescombined,function(c) sum(c=="Denominator"))
freqDenominator = count_Denominator[-c(2, 3),]
freqDenominator$Determinants= "Denominator"
prtDenominator = ldply(detDenominator, function(c) sum(c == "Protective"))
freqprtDenominator = prtDenominator[-c(1,2),]
freqDenominator$Protective = freqprtDenominator
desDenominator = ldply(detDenominator, function(c) sum(c == "Destructive"))      
freqdesDenominator = desDenominator[-c(1,2),]
freqDenominator$Destructive = freqdesDenominator

detSegregation_index = subset(prtdescombined, y == "Segregation index")
count_Segregation_index<- ldply(prtdescombined,function(c) sum(c=="Segregation index"))
freqSegregation_index = count_Segregation_index[-c(2, 3),]
freqSegregation_index$Determinants= "Segregation index"
prtSegregation_index = ldply(detSegregation_index, function(c) sum(c == "Protective"))
freqprtSegregation_index = prtSegregation_index[-c(1,2),]
freqSegregation_index$Protective = freqprtSegregation_index
desSegregation_index = ldply(detSegregation_index, function(c) sum(c == "Destructive"))      
freqdesSegregation_index = desSegregation_index[-c(1,2),]
freqSegregation_index$Destructive = freqdesSegregation_index

detenrolledfreelunch = subset(prtdescombined, y == "% Enrolled in Free or Reduced Lunch")
count_enrolledfreelunch<- ldply(prtdescombined,function(c) sum(c=="% Enrolled in Free or Reduced Lunch"))
freqenrolledfreelunch = count_enrolledfreelunch[-c(2, 3),]
freqenrolledfreelunch$Determinants= "% Enrolled in Free or Reduced Lunch"
prtenrolledfreelunch = ldply(detenrolledfreelunch, function(c) sum(c == "Protective"))
freqprtenrolledfreelunch = prtenrolledfreelunch[-c(1,2),]
freqenrolledfreelunch$Protective = freqprtenrolledfreelunch
desenrolledfreelunch = ldply(detenrolledfreelunch, function(c) sum(c == "Destructive"))      
freqdesenrolledfreelunch = desenrolledfreelunch[-c(1,2),]
freqenrolledfreelunch$Destructive = freqdesenrolledfreelunch

dethouseholdincomewhite = subset(prtdescombined, y == "Household Income (White)")
count_householdincomewhite<- ldply(prtdescombined,function(c) sum(c=="Household Income (White)"))
freqhouseholdincomewhite = count_householdincomewhite[-c(2, 3),]
freqhouseholdincomewhite$Determinants= "Household Income (White)"
prthouseholdincomewhite = ldply(dethouseholdincomewhite, function(c) sum(c == "Protective"))
freqprthouseholdincomewhite = prthouseholdincomewhite[-c(1,2),]
freqhouseholdincomewhite$Protective = freqprthouseholdincomewhite
deshouseholdincomewhite = ldply(dethouseholdincomewhite, function(c) sum(c == "Destructive"))   
freqdeshouseholdincomewhite = deshouseholdincomewhite[-c(1,2),]
freqhouseholdincomewhite$Destructive = freqdeshouseholdincomewhite

detnouninsured2 = subset(prtdescombined, y == "# Uninsured_2")
count_nouninsured2<- ldply(prtdescombined,function(c) sum(c=="# Uninsured_2"))
freqnouninsured2 = count_nouninsured2[-c(2, 3),]
freqnouninsured2$Determinants= "# Uninsured_2"
prtnouninsured2 = ldply(detnouninsured2, function(c) sum(c == "Protective"))
freqprtnouninsured2 = prtnouninsured2[-c(1,2),]
freqnouninsured2$Protective = freqprtnouninsured2
desnouninsured2 = ldply(detnouninsured2, function(c) sum(c == "Destructive"))      
freqdesnouninsured2 = desnouninsured2[-c(1,2),]
freqnouninsured2$Destructive = freqdesnouninsured2

detnouninsured1 = subset(prtdescombined, y == "# Uninsured_1")
count_nouninsured1<- ldply(prtdescombined,function(c) sum(c=="# Uninsured_1"))
freqnouninsured1 = count_nouninsured1[-c(2, 3),]
freqnouninsured1$Determinants= "# Uninsured_1"
prtnouninsured1 = ldply(detnouninsured1, function(c) sum(c == "Protective"))
freqprtnouninsured1 = prtnouninsured1[-c(1,2),]
freqnouninsured1$Protective = freqprtnouninsured1
desnouninsured1 = ldply(detnouninsured1, function(c) sum(c == "Destructive"))      
freqdesnouninsured1 = desnouninsured1[-c(1,2),]
freqnouninsured1$Destructive = freqdesnouninsured1

detmotorvehicledeaths = subset(prtdescombined, y == "# Motor Vehicle Deaths")
count_motorvehicledeaths<- ldply(prtdescombined,function(c) sum(c=="# Motor Vehicle Deaths"))
freqmotorvehicledeaths = count_motorvehicledeaths[-c(2, 3),]
freqmotorvehicledeaths$Determinants= "# Motor Vehicle Deaths"
prtmotorvehicledeaths = ldply(detmotorvehicledeaths, function(c) sum(c == "Protective"))
freqprtmotorvehicledeaths = prtmotorvehicledeaths[-c(1,2),]
freqmotorvehicledeaths$Protective = freqprtmotorvehicledeaths
desmotorvehicledeaths = ldply(detmotorvehicledeaths, function(c) sum(c == "Destructive"))      
freqdesmotorvehicledeaths = desmotorvehicledeaths[-c(1,2),]
freqmotorvehicledeaths$Destructive = freqdesmotorvehicledeaths

detnolimitedaccess = subset(prtdescombined, y == "# Limited Access")
count_nolimitedaccess<- ldply(prtdescombined,function(c) sum(c=="# Limited Access"))
freqnolimitedaccess = count_nolimitedaccess[-c(2, 3),]
freqnolimitedaccess$Determinants= "# Limited Access"
prtnolimitedaccess = ldply(detnolimitedaccess, function(c) sum(c == "Protective"))
freqprtnolimitedaccess = prtnolimitedaccess[-c(1,2),]
freqnolimitedaccess$Protective = freqprtnolimitedaccess
desnolimitedaccess = ldply(detnolimitedaccess, function(c) sum(c == "Destructive"))      
freqdesnolimitedaccess = desnolimitedaccess[-c(1,2),]
freqnolimitedaccess$Destructive = freqdesnolimitedaccess

detnofoodinsecure = subset(prtdescombined, y == "# Food Insecure")
count_nofoodinsecure<- ldply(prtdescombined,function(c) sum(c=="# Food Insecure"))
freqnofoodinsecure = count_nofoodinsecure[-c(2, 3),]
freqnofoodinsecure$Determinants= "# Food Insecure"
prtnofoodinsecure = ldply(detnofoodinsecure, function(c) sum(c == "Protective"))
freqprtnofoodinsecure = prtnofoodinsecure[-c(1,2),]
freqnofoodinsecure$Protective = freqprtnofoodinsecure
desnofoodinsecure = ldply(detnofoodinsecure, function(c) sum(c == "Destructive"))      
freqdesnofoodinsecure = desnofoodinsecure[-c(1,2),]
freqnofoodinsecure$Destructive = freqdesnofoodinsecure

detnohivecases = subset(prtdescombined, y == "# HIV Cases")
count_nohivecases<- ldply(prtdescombined,function(c) sum(c=="# HIV Cases"))
freqnohivecases = count_nohivecases[-c(2, 3),]
freqnohivecases$Determinants= "# HIV Cases"
prtnohivecases = ldply(detnohivecases, function(c) sum(c == "Protective"))
freqprtnohivecases = prtnohivecases[-c(1,2),]
freqnohivecases$Protective = freqprtnohivecases
desnohivecases = ldply(detnohivecases, function(c) sum(c == "Destructive"))      
freqdesnohivecases = desnohivecases[-c(1,2),]
freqnohivecases$Destructive = freqdesnohivecases

detphysicaldistressfrequent = subset(prtdescombined, y == "% Frequent Physical Distress")
count_physicaldistressfrequent<- ldply(prtdescombined,function(c) sum(c=="% Frequent Physical Distress"))
freqphysicaldistressfrequent = count_physicaldistressfrequent[-c(2, 3),]
freqphysicaldistressfrequent$Determinants= "% Frequent Physical Distress"
prtphysicaldistressfrequent = ldply(detphysicaldistressfrequent, function(c) sum(c == "Protective"))
freqprtphysicaldistressfrequent = prtphysicaldistressfrequent[-c(1,2),]
freqphysicaldistressfrequent$Protective = freqprtphysicaldistressfrequent
desphysicaldistressfrequent = ldply(detphysicaldistressfrequent, function(c) sum(c == "Destructive"))      
freqdesphysicaldistressfrequent = desphysicaldistressfrequent[-c(1,2),]
freqphysicaldistressfrequent$Destructive = freqdesphysicaldistressfrequent

detpre_covid_deaths = subset(prtdescombined, y == "pre_covid_deaths")
count_pre_covid_deaths<- ldply(prtdescombined,function(c) sum(c=="pre_covid_deaths"))
freqpre_covid_deaths = count_pre_covid_deaths[-c(2, 3),]
freqpre_covid_deaths$Determinants= "pre_covid_deaths"
prtpre_covid_deaths = ldply(detpre_covid_deaths, function(c) sum(c == "Protective"))
freqprtpre_covid_deaths = prtpre_covid_deaths[-c(1,2),]
freqpre_covid_deaths$Protective = freqprtpre_covid_deaths
despre_covid_deaths = ldply(detpre_covid_deaths, function(c) sum(c == "Destructive"))      
freqdespre_covid_deaths = despre_covid_deaths[-c(1,2),]
freqpre_covid_deaths$Destructive = freqdespre_covid_deaths

detlifeexpwhite = subset(prtdescombined, y == "Life Expectancy (White)")
count_lifeexpwhite<- ldply(prtdescombined,function(c) sum(c=="Life Expectancy (White)"))
freqlifeexpwhite = count_lifeexpwhite[-c(2, 3),]
freqlifeexpwhite$Determinants= "Life Expectancy (White)"
prtlifeexpwhite = ldply(detlifeexpwhite, function(c) sum(c == "Protective"))
freqprtlifeexpwhite = prtlifeexpwhite[-c(1,2),]
freqlifeexpwhite$Protective = freqprtlifeexpwhite
deslifeexpwhite = ldply(detlifeexpwhite, function(c) sum(c == "Destructive"))      
freqdeslifeexpwhite = deslifeexpwhite[-c(1,2),]
freqlifeexpwhite$Destructive = freqdeslifeexpwhite

detlifeexphispanic = subset(prtdescombined, y == "Life Expectancy (Hispanic)")
count_lifeexphispanic<- ldply(prtdescombined,function(c) sum(c=="Life Expectancy (Hispanic)"))
freqlifeexphispanic = count_lifeexphispanic[-c(2, 3),]
freqlifeexphispanic$Determinants= "Life Expectancy (Hispanic)"
prtlifeexphispanic = ldply(detlifeexphispanic, function(c) sum(c == "Protective"))
freqprtlifeexphispanic = prtlifeexphispanic[-c(1,2),]
freqlifeexphispanic$Protective = freqprtlifeexphispanic
deslifeexphispanic = ldply(detlifeexphispanic, function(c) sum(c == "Destructive"))      
freqdeslifeexphispanic = deslifeexphispanic[-c(1,2),]
freqlifeexphispanic$Destructive = freqdeslifeexphispanic

detlifeexp = subset(prtdescombined, y == "Life Expectancy")
count_lifeexp<- ldply(prtdescombined,function(c) sum(c=="Life Expectancy"))
freqlifeexp = count_lifeexp[-c(2, 3),]
freqlifeexp$Determinants= "Life Expectancy"
prtlifeexp = ldply(detlifeexp, function(c) sum(c == "Protective"))
freqprtlifeexp = prtlifeexp[-c(1,2),]
freqlifeexp$Protective = freqprtlifeexp
deslifeexp = ldply(detlifeexp, function(c) sum(c == "Destructive"))      
freqdeslifeexp = deslifeexp[-c(1,2),]
freqlifeexp$Destructive = freqdeslifeexp

detRural = subset(prtdescombined, y == "% Rural")
count_Rural<- ldply(prtdescombined,function(c) sum(c=="% Rural"))
freqRural = count_Rural[-c(2, 3),]
freqRural$Determinants= "% Rural"
prtRural = ldply(detRural, function(c) sum(c == "Protective"))
freqprtRural = prtRural[-c(1,2),]
freqRural$Protective = freqprtRural
desRural = ldply(detRural, function(c) sum(c == "Destructive"))      
freqdesRural = desRural[-c(1,2),]
freqRural$Destructive = freqdesRural

detAll.Cause.death_rate = subset(prtdescombined, y == "All.Cause.death_rate")
count_All.Cause.death_rate<- ldply(prtdescombined,function(c) sum(c=="All.Cause.death_rate"))
freqAll.Cause.death_rate = count_All.Cause.death_rate[-c(2, 3),]
freqAll.Cause.death_rate$Determinants= "All.Cause.death_rate"
prtAll.Cause.death_rate = ldply(detAll.Cause.death_rate, function(c) sum(c == "Protective"))
freqprtAll.Cause.death_rate = prtAll.Cause.death_rate[-c(1,2),]
freqAll.Cause.death_rate$Protective = freqprtAll.Cause.death_rate
desAll.Cause.death_rate = ldply(detAll.Cause.death_rate, function(c) sum(c == "Destructive"))   
freqdesAll.Cause.death_rate = desAll.Cause.death_rate[-c(1,2),]
freqAll.Cause.death_rate$Destructive = freqdesAll.Cause.death_rate

detAssault.death_rate = subset(prtdescombined, y == "Assault.death_rate")
count_Assault.death_rate<- ldply(prtdescombined,function(c) sum(c=="Assault.death_rate"))
freqAssault.death_rate = count_Assault.death_rate[-c(2, 3),]
freqAssault.death_rate$Determinants= "Assault.death_rate"
prtAssault.death_rate = ldply(detAssault.death_rate, function(c) sum(c == "Protective"))
freqprtAssault.death_rate = prtAssault.death_rate[-c(1,2),]
freqAssault.death_rate$Protective = freqprtAssault.death_rate
desAssault.death_rate = ldply(detAssault.death_rate, function(c) sum(c == "Destructive"))      
freqdesAssault.death_rate = desAssault.death_rate[-c(1,2),]
freqAssault.death_rate$Destructive = freqdesAssault.death_rate

detCancer.death_rate = subset(prtdescombined, y == "Cancer.death_rate")
count_Cancer.death_rate<- ldply(prtdescombined,function(c) sum(c=="Cancer.death_rate"))
freqCancer.death_rate = count_Cancer.death_rate[-c(2, 3),]
freqCancer.death_rate$Determinants= "Cancer.death_rate"
prtCancer.death_rate = ldply(detCancer.death_rate, function(c) sum(c == "Protective"))
freqprtCancer.death_rate = prtCancer.death_rate[-c(1,2),]
freqCancer.death_rate$Protective = freqprtCancer.death_rate
desCancer.death_rate = ldply(detCancer.death_rate, function(c) sum(c == "Destructive"))      
freqdesCancer.death_rate = desCancer.death_rate[-c(1,2),]
freqCancer.death_rate$Destructive = freqdesCancer.death_rate

detCardiovascular.death_rate = subset(prtdescombined, y == "Cardiovascular.death_rate")
count_Cardiovascular.death_rate<- ldply(prtdescombined,function(c) sum(c=="Cardiovascular.death_rate"))
freqCardiovascular.death_rate = count_Cardiovascular.death_rate[-c(2, 3),]
freqCardiovascular.death_rate$Determinants= "Cardiovascular.death_rate"
prtCardiovascular.death_rate = ldply(detCardiovascular.death_rate, function(c) sum(c == "Protective"))
freqprtCardiovascular.death_rate = prtCardiovascular.death_rate[-c(1,2),]
freqCardiovascular.death_rate$Protective = freqprtCardiovascular.death_rate
desCardiovascular.death_rate = ldply(detCardiovascular.death_rate, function(c) sum(c == "Destructive"))      
freqdesCardiovascular.death_rate = desCardiovascular.death_rate[-c(1,2),]
freqCardiovascular.death_rate$Destructive = freqdesCardiovascular.death_rate

detDespair.death_rate = subset(prtdescombined, y == "Despair.death_rate")
count_Despair.death_rate<- ldply(prtdescombined,function(c) sum(c=="NDespair.death_rate"))
freqDespair.death_rate = count_Despair.death_rate[-c(2, 3),]
freqDespair.death_rate$Determinants= "Despair.death_rate"
prtDespair.death_rate = ldply(detDespair.death_rate, function(c) sum(c == "Protective"))
freqprtDespair.death_rate = prtDespair.death_rate[-c(1,2),]
freqDespair.death_rate$Protective = freqprtDespair.death_rate
desDespair.death_rate = ldply(detDespair.death_rate, function(c) sum(c == "Destructive"))      
freqdesDespair.death_rate = desDespair.death_rate[-c(1,2),]
freqDespair.death_rate$Destructive = freqdesDespair.death_rate

detCOPD = subset(prtdescombined, y == "COPD")
count_COPD<- ldply(prtdescombined,function(c) sum(c=="COPD"))
freqCOPD = count_COPD[-c(2, 3),]
freqCOPD$Determinants= "COPD"
prtCOPD = ldply(detCOPD, function(c) sum(c == "Protective"))
freqprtCOPD = prtCOPD[-c(1,2),]
freqCOPD$Protective = freqprtCOPD
desCOPD = ldply(detCOPD, function(c) sum(c == "Destructive"))      
freqdesCOPD = desCOPD[-c(1,2),]
freqCOPD$Destructive = freqdesCOPD

detAdultChronicLungDisease = subset(prtdescombined, y == "AdultChronicLungDisease")
count_AdultChronicLungDisease<- ldply(prtdescombined,function(c) sum(c=="AdultChronicLungDisease"))
freqAdultChronicLungDisease = count_AdultChronicLungDisease[-c(2, 3),]
freqAdultChronicLungDisease$Determinants= "AdultChronicLungDisease"
prtAdultChronicLungDisease = ldply(detAdultChronicLungDisease, function(c) sum(c == "Protective"))
freqprtAdultChronicLungDisease = prtAdultChronicLungDisease[-c(1,2),]
freqAdultChronicLungDisease$Protective = freqprtAdultChronicLungDisease
desAdultChronicLungDisease = ldply(detAdultChronicLungDisease, function(c) sum(c == "Destructive"))      
freqdesAdultChronicLungDisease = desAdultChronicLungDisease[-c(1,2),]
freqAdultChronicLungDisease$Destructive = freqdesAdultChronicLungDisease

detnoworkersdrivealone = subset(prtdescombined, y == "# Workers who Drive Alone")
count_noworkersdrivealone<- ldply(prtdescombined,function(c) sum(c=="# Workers who Drive Alone"))
freqnoworkersdrivealone = count_noworkersdrivealone[-c(2, 3),]
freqnoworkersdrivealone$Determinants= "# Workers who Drive Alone"
prtnoworkersdrivealone = ldply(detnoworkersdrivealone, function(c) sum(c == "Protective"))
freqprtnoworkersdrivealone = prtnoworkersdrivealone[-c(1,2),]
freqnoworkersdrivealone$Protective = freqprtnoworkersdrivealone
desnoworkersdrivealone = ldply(detnoworkersdrivealone, function(c) sum(c == "Destructive"))   
freqdesnoworkersdrivealone = desnoworkersdrivealone[-c(1,2),]
freqnoworkersdrivealone$Destructive = freqdesnoworkersdrivealone

detjustseverehousingcostburden = subset(prtdescombined, y == "Severe Housing Cost Burden")
count_justseverehousingcostburden<- ldply(prtdescombined,function(c) sum(c=="Severe Housing Cost Burden"))
freqjustseverehousingcostburden = count_justseverehousingcostburden[-c(2, 3),]
freqjustseverehousingcostburden$Determinants= "Severe Housing Cost Burden"
prtjustseverehousingcostburden = ldply(detjustseverehousingcostburden, function(c) sum(c == "Protective"))
freqprtjustseverehousingcostburden = prtjustseverehousingcostburden[-c(1,2),]
freqjustseverehousingcostburden$Protective = freqprtjustseverehousingcostburden
desjustseverehousingcostburden = ldply(detjustseverehousingcostburden, function(c) sum(c == "Destructive"))      
freqdesjustseverehousingcostburden = desjustseverehousingcostburden[-c(1,2),]
freqjustseverehousingcostburden$Destructive = freqdesjustseverehousingcostburden

deteverehousingproblems = subset(prtdescombined, y == "% Severe Housing Problems")
count_everehousingproblems<- ldply(prtdescombined,function(c) sum(c=="% Severe Housing Problems"))
freqeverehousingproblems = count_everehousingproblems[-c(2, 3),]
freqeverehousingproblems$Determinants= "% Severe Housing Problems"
prteverehousingproblems = ldply(deteverehousingproblems, function(c) sum(c == "Protective"))
freqprteverehousingproblems = prteverehousingproblems[-c(1,2),]
freqeverehousingproblems$Protective = freqprteverehousingproblems
deseverehousingproblems = ldply(deteverehousingproblems, function(c) sum(c == "Destructive")) 
freqdeseverehousingproblems = deseverehousingproblems[-c(1,2),]
freqeverehousingproblems$Destructive = freqdeseverehousingproblems

detaveragedailypm2.5 = subset(prtdescombined, y == "Average Daily PM2.5")
count_averagedailypm2.5<- ldply(prtdescombined,function(c) sum(c=="Average Daily PM2.5"))
freqaveragedailypm2.5 = count_averagedailypm2.5[-c(2, 3),]
freqaveragedailypm2.5$Determinants= "Average Daily PM2.5"
prtaveragedailypm2.5 = ldply(detaveragedailypm2.5, function(c) sum(c == "Protective"))
freqprtaveragedailypm2.5 = prtaveragedailypm2.5[-c(1,2),]
freqaveragedailypm2.5$Protective = freqprtaveragedailypm2.5
desaveragedailypm2.5 = ldply(detaveragedailypm2.5, function(c) sum(c == "Destructive"))      
freqdesaveragedailypm2.5 = desaveragedailypm2.5[-c(1,2),]
freqaveragedailypm2.5$Destructive = freqdesaveragedailypm2.5

detnoinjurydeaths = subset(prtdescombined, y == "# Injury Deaths")
count_noinjurydeaths<- ldply(prtdescombined,function(c) sum(c=="# Injury Deaths"))
freqnoinjurydeaths = count_noinjurydeaths[-c(2, 3),]
freqnoinjurydeaths$Determinants= "# Injury Deaths"
prtnoinjurydeaths = ldply(detnoinjurydeaths, function(c) sum(c == "Protective"))
freqprtnoinjurydeaths = prtnoinjurydeaths[-c(1,2),]
freqnoinjurydeaths$Protective = freqprtnoinjurydeaths
desnoinjurydeaths = ldply(detnoinjurydeaths, function(c) sum(c == "Destructive"))      
freqdesnoinjurydeaths = desnoinjurydeaths[-c(1,2),]
freqnoinjurydeaths$Destructive = freqdesnoinjurydeaths

detaverageviolentcrimes = subset(prtdescombined, y == "Annual Average Violent Crimes")
count_averageviolentcrimes<- ldply(prtdescombined,function(c) sum(c=="Annual Average Violent Crimes"))
freqaverageviolentcrimes = count_averageviolentcrimes[-c(2, 3),]
freqaverageviolentcrimes$Determinants= "Annual Average Violent Crimes"
prtaverageviolentcrimes = ldply(detaverageviolentcrimes, function(c) sum(c == "Protective"))
freqprtaverageviolentcrimes = prtaverageviolentcrimes[-c(1,2),]
freqaverageviolentcrimes$Protective = freqprtaverageviolentcrimes
desaverageviolentcrimes = ldply(detaverageviolentcrimes, function(c) sum(c == "Destructive"))   
freqdesaverageviolentcrimes = desaverageviolentcrimes[-c(1,2),]
freqaverageviolentcrimes$Destructive = freqdesaverageviolentcrimes

detnoassociations = subset(prtdescombined, y == "# Associations")
count_noassociations<- ldply(prtdescombined,function(c) sum(c=="# Associations"))
freqnoassociations = count_noassociations[-c(2, 3),]
freqnoassociations$Determinants= "# Associations"
prtnoassociations = ldply(detnoassociations, function(c) sum(c == "Protective"))
freqprtnoassociations = prtnoassociations[-c(1,2),]
freqnoassociations$Protective = freqprtnoassociations
desnoassociations = ldply(detnoassociations, function(c) sum(c == "Destructive"))      
freqdesnoassociations = desnoassociations[-c(1,2),]
freqnoassociations$Destructive = freqdesnoassociations

detnohouseholds = subset(prtdescombined, y == "# Households")
count_nohouseholds<- ldply(prtdescombined,function(c) sum(c=="# Households"))
freqnohouseholds = count_nohouseholds[-c(2, 3),]
freqnohouseholds$Determinants= "# Households"
prtnohouseholds = ldply(detnohouseholds, function(c) sum(c == "Protective"))
freqprtnohouseholds = prtnohouseholds[-c(1,2),]
freqnohouseholds$Protective = freqprtnohouseholds
desnohouseholds = ldply(detnohouseholds, function(c) sum(c == "Destructive"))      
freqdesnohouseholds = desnohouseholds[-c(1,2),]
freqnohouseholds$Destructive = freqdesnohouseholds

detnosingleparenthouseholds = subset(prtdescombined, y == "# Single-Parent Households")
count_nosingleparenthouseholds<- ldply(prtdescombined,function(c) sum(c=="# Single-Parent Households"))
freqnosingleparenthouseholds = count_nosingleparenthouseholds[-c(2, 3),]
freqnosingleparenthouseholds$Determinants= "# Single-Parent Households"
prtnosingleparenthouseholds = ldply(detnosingleparenthouseholds, function(c) sum(c == "Protective"))
freqprtnosingleparenthouseholds = prtnosingleparenthouseholds[-c(1,2),]
freqnosingleparenthouseholds$Protective = freqprtnosingleparenthouseholds
desnosingleparenthouseholds = ldply(detnosingleparenthouseholds, function(c) sum(c == "Destructive"))      
freqdesnosingleparenthouseholds = desnosingleparenthouseholds[-c(1,2),]
freqnosingleparenthouseholds$Destructive = freqdesnosingleparenthouseholds

det80percentileincome = subset(prtdescombined, y == "80th Percentile Income")
count_80percentileincome<- ldply(prtdescombined,function(c) sum(c=="80th Percentile Income"))
freq80percentileincome = count_80percentileincome[-c(2, 3),]
freq80percentileincome$Determinants= "80th Percentile Income"
prt80percentileincome = ldply(det80percentileincome, function(c) sum(c == "Protective"))
freqprt80percentileincome = prt80percentileincome[-c(1,2),]
freq80percentileincome$Protective = freqprt80percentileincome
des80percentileincome = ldply(det80percentileincome, function(c) sum(c == "Destructive"))      
freqdes80percentileincome = des80percentileincome[-c(1,2),]
freq80percentileincome$Destructive = freqdes80percentileincome

detchildrenpovertyhispanic = subset(prtdescombined, y == "% Children in Poverty (Hispanic)")
count_childrenpovertyhispanic<- ldply(prtdescombined,function(c) sum(c=="% Children in Poverty (Hispanic)"))
freqchildrenpovertyhispanic = count_childrenpovertyhispanic[-c(2, 3),]
freqchildrenpovertyhispanic$Determinants= "% Children in Poverty (Hispanic)"
prtchildrenpovertyhispanic = ldply(detchildrenpovertyhispanic, function(c) sum(c == "Protective"))
freqprtchildrenpovertyhispanic = prtchildrenpovertyhispanic[-c(1,2),]
freqchildrenpovertyhispanic$Protective = freqprtchildrenpovertyhispanic
deschildrenpovertyhispanic = ldply(detchildrenpovertyhispanic, function(c) sum(c == "Destructive"))      
freqdeschildrenpovertyhispanic = deschildrenpovertyhispanic[-c(1,2),]
freqchildrenpovertyhispanic$Destructive = freqdeschildrenpovertyhispanic

detLat = subset(prtdescombined, y == "Lat")
count_Lat<- ldply(prtdescombined,function(c) sum(c=="Lat"))
freqLat = count_Lat[-c(2, 3),]
freqLat$Determinants= "Lat"
prtLat = ldply(detLat, function(c) sum(c == "Protective"))
freqprtLat = prtLat[-c(1,2),]
freqLat$Protective = freqprtLat
desLat = ldply(detLat, function(c) sum(c == "Destructive"))      
freqdesLat = desLat[-c(1,2),]
freqLat$Destructive = freqdesLat

detpopdensity = subset(prtdescombined, y == "popdensity")
count_popdensity<- ldply(prtdescombined,function(c) sum(c=="popdensity"))
freqpopdensity = count_popdensity[-c(2, 3),]
freqpopdensity$Determinants= "popdensity"
prtpopdensity = ldply(detpopdensity, function(c) sum(c == "Protective"))
freqprtpopdensity = prtpopdensity[-c(1,2),]
freqpopdensity$Protective = freqprtpopdensity
despopdensity = ldply(detpopdensity, function(c) sum(c == "Destructive"))      
freqdespopdensity = despopdensity[-c(1,2),]
freqpopdensity$Destructive = freqdespopdensity

detmedianhousevalue = subset(prtdescombined, y == "medianhousevalue")
count_medianhousevalue<- ldply(prtdescombined,function(c) sum(c=="medianhousevalue"))
freqmedianhousevalue = count_medianhousevalue[-c(2, 3),]
freqmedianhousevalue$Determinants= "medianhousevalue"
prtmedianhousevalue = ldply(detmedianhousevalue, function(c) sum(c == "Protective"))
freqprtmedianhousevalue = prtmedianhousevalue[-c(1,2),]
freqmedianhousevalue$Protective = freqprtmedianhousevalue
desmedianhousevalue = ldply(detmedianhousevalue, function(c) sum(c == "Destructive"))      
freqdesmedianhousevalue = desmedianhousevalue[-c(1,2),]
freqmedianhousevalue$Destructive = freqdesmedianhousevalue

detyoung_pecent = subset(prtdescombined, y == "young_pecent")
count_young_pecent<- ldply(prtdescombined,function(c) sum(c=="young_pecent"))
freqyoung_pecent = count_young_pecent[-c(2, 3),]
freqyoung_pecent$Determinants= "young_pecent"
prtyoung_pecent = ldply(detyoung_pecent, function(c) sum(c == "Protective"))
freqprtyoung_pecent = prtyoung_pecent[-c(1,2),]
freqyoung_pecent$Protective = freqprtyoung_pecent
desyoung_pecent = ldply(detyoung_pecent, function(c) sum(c == "Destructive"))      
freqdesyoung_pecent = desyoung_pecent[-c(1,2),]
freqyoung_pecent$Destructive = freqdesyoung_pecent

detprime_pecent = subset(prtdescombined, y == "prime_pecent")
count_prime_pecent<- ldply(prtdescombined,function(c) sum(c=="prime_pecent"))
freqprime_pecent = count_prime_pecent[-c(2, 3),]
freqprime_pecent$Determinants= "prime_pecent"
prtprime_pecent = ldply(detprime_pecent, function(c) sum(c == "Protective"))
freqprtprime_pecent = prtprime_pecent[-c(1,2),]
freqprime_pecent$Protective = freqprtprime_pecent
desprime_pecent = ldply(detprime_pecent, function(c) sum(c == "Destructive"))      
freqdesprime_pecent = desprime_pecent[-c(1,2),]
freqprime_pecent$Destructive = freqdesprime_pecent

#create sigdeterminants data frame that combines all of the data frames formed above
sigdeterminants <- bind_rows(freqconfirmed, freqactive, freqcase.fatality, freqteenbirth, freqovercrowding, freqlessthan18, freqnotproficientinenglish, freqpediatricasthma, frequninsured1, frequninsured2, freqmeanwintertemp, freqmeansummertemp, freqlong, freqolderpecent, freqmidpecent, freqyearspotentiallifelostrate, freqlowbirthweight, freqsmokers, freqpct_obesity, freqphysicallyinactive, freqexcessivedrinking, freqdrivingalcohol, freqteenbirthhispanic, freqteenbirthwhite, freqincidencerate, freqpreventablehospital, freqpreventablehospitalhispanic, freqpreventablehospitalwhite, freqscreenedhispanic, freqchildrenpoverty, freqincomeratio, freqsingleparent, freqinjurydeathrate, freqinjurydeathratehispanic, freqinjurydeathratewhite, freqinadequatefacilities, freqdrivealonehispanic,freqdrivealonewhite, freqprecoviddeathrate,freqageadjustedhispanic,freqageadjustedwhite, freqpct_diabetes, freqfoodinsecure, freqlimitedhealthyfood, freqmotormortality, freqinsufficientsleep, freqsegregationindex, freqhomeowners, freqpct_age65,freqblack,freqindianalaska, freqhawaiian, freqnonhispanicwhite, freqadultasthma, freqhouseholdincomeblack, freqmean_summer_rm, freqpct_owner_occ, freqpoverty,freqmentalproviderrate, frequnhealthydays, freqdrivealonework,freq20percentileincome, freqlongcommutedrivealone,freqsocialassociationrate,freqtrafficvolumepermeter,freqmentalunhealthydays,freqmentaldistressfrequent,freqwhitechildpoverty,freqmean_pm25,freqLungCancer,freqfemale,freqhispanic, freqnolessthan18,freqnoblack,freqnoindianalaska,freqnoasian,freqnohawaiian,freqnohomeowners,freqnohouseholdwithseverecostburden,freqseverehousingcostburden, freqDenominator,freqSegregation_index,freqenrolledfreelunch,freqhouseholdincomewhite,freqnouninsured2, freqnouninsured1,freqmotorvehicledeaths,freqnolimitedaccess,freqnofoodinsecure,freqnohivecases,freqphysicaldistressfrequent,freqpre_covid_deaths,freqlifeexpwhite,freqlifeexphispanic,freqlifeexp,freqRural,freqAll.Cause.death_rate,freqAssault.death_rate,freqCancer.death_rate,freqCardiovascular.death_rate,freqDespair.death_rate,freqCOPD,freqAdultChronicLungDisease,freqnoworkersdrivealone,freqjustseverehousingcostburden,freqeverehousingproblems,freqaveragedailypm2.5,freqnoinjurydeaths,freqaverageviolentcrimes,freqnoassociations,freqnohouseholds,freqnosingleparenthouseholds,freq80percentileincome,freqchildrenpovertyhispanic, freqLat,freqpopdensity,freqmedianhousevalue,freqyoung_pecent,freqprime_pecent)

```

Graph of Significant Determinants' Frequency
```{r}
library(ggplot2)

#bar graph of frequency of significant determinants
#does not show frequency of destructive and protective occurrences
p <- ggplot(sigdeterminants, aes(x=Determinants, y=V1)) + 
  ggtitle("Frequency of Significant Determinants")+
  xlab("Significant Determinants") +
  ylab("Frequency") +
  geom_bar(stat = "identity")
p + coord_flip()
```

Stacked Bar Graph of Frequency of Protective/Destructive Occurrences of each Significant Determinant
```{r}
library(ggplot2)

#stacked bar graph version of graph above
#currently working on it
#issue: two colors are not showing
ggplot(data=prtdescombined, aes(x=y, y='V1', fill='Effect on MRR')) +
  ggtitle("Frequency of Significant DeterminantsS")+
  xlab("Significant Determinants")+
  ylab("Frequency") +
  geom_bar(stat = "identity")+coord_flip()

```

