---
title: "ahns3-Determinants Graphing"
output: html_notebook
---

code is from ProtoNotebook
It was used to load the data for siginificant protective and destructive determinants for every state.
```{r echo = F}

  # use GWAS_ADJ_P and GWAS_MRR to say for which states there are significant protective and destructive variables

  s = ""
  for (state in colnames(GWAS_MRR)) {
    s <- paste(s, state, ": ", sep = "")
    
    prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          #des <- c(des, GWAS_MRR[[state]][itr])
          des <- c(des, itr)
        } else {
          #prt <- c(prt, GWAS_MRR[[state]][itr])
          prt <- c(prt, itr)
        }
      }
    }
  
    if (length(prt) > 1) {
      s <- paste(s, "protective variables include: ", sep = "")
      for ( i  in 2:length(prt) ) {
        if (i != length(prt)) {
          s <- paste(s, colnames(model_input)[prt[i]], ", ", sep = "")
        } else {
          s <- paste(s, colnames(model_input)[prt[i]], " ", sep = "")
        }
      }
    } else {
      s <- paste(s, "no protective variables; ", sep = "")
    }
    
    if (length(des) > 1) {
      s <- paste(s, "destructive variables include: ", sep = "")
      for ( i  in 2:length(des) ) {
        if (i != length(des)) {
          s <- paste(s, colnames(model_input)[des[i]], ", ", sep = "")
        } else {
          s <- paste(s, colnames(model_input)[des[i]], "", sep = "")
        }
      }
    } else {
      s <- paste(s, "no destructive variables;", sep = "")
    }
    
    s <- paste(s, "\n", sep ="")
  }

  cat(s)


```

code is from ProtoNotebook
It was used to load each state's significant determinants into the global environment.
To use:
* replace state with "chosen state" (ex: NY)
* replace data frame name with data"chosenstate" (ex: dataNY)
```{r echo = F}
   # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  #REPLACE STATE NAME
  state = "NY"
  state
   s <- paste("GENERATING FIGURE FOR ", state, sep = "")
   print(s)
  
   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

   #REPLACE DATA FRAME WITH CHOSEN STATE 
    dataNY <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #REPLACE DATA FRAME WITH CHOSEN STATE
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataNY <- dataNY %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataNY$y <- factor(dataNY$y, levels = dataNY$y)

    # Plot
    h <- (length(vals)-1) * 0.4
    f <- paste("Notebooks/state_GWAS_results/", state, "SDWAS.png", sep = "")
    png(filename=f,height=h,width=7,res=200,units="in")
    ggplot(data, aes(x=x, y=y)) +
      geom_point() +
      geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=1.3, alpha=0.9 ) +
      scale_color_manual(values = c("#c35442", "#2b517f")) +
      geom_point() +
      ylab("Interested Variable") +
      xlab("MRR of Interested Variable") +
      ggtitle(title) +
      geom_segment( aes(x=1, xend=1, y=0, yend = length(vals)), size = 1.0)
    dev.off()
}
```

code is my work
After collecting most of 50 states, I counted the frequency of each significant determinant in the state GWAS.
This route was abandoned because it was not time efficient.
```{r echo = F }
library(plyr)

#states with not enough data: UT,VT,DE,ME,MD,MA,NH,NJ
#states that did not work with above code: AK,MI,RI,WY

#combined all of state data into a data frame called "prtdescombined"
prtdescombined = rbind(dataAL , dataAR,dataAZ,dataCA, dataCO, dataFL, dataGA, dataIA, dataID,dataIL,dataIN,dataKS, dataKY, dataLA, dataMI, dataMN, dataMO, dataMS, dataMT, dataNC, dataND, dataNE, dataNJ, dataNM, dataNY, dataOH,dataOK,dataOR,dataPA,dataSC,dataSD, dataTN,dataTX,dataVA,dataWA,dataWI,dataWV)

#counted number of times a determinant appeared in the prtdescombined data frame
count_confirmed<- ldply(prtdescombined,function(c) sum(c=="Confirmed"))
count_active<- ldply(prtdescombined,function(c) sum(c=="Active"))
count_case.fatality<- ldply(prtdescombined,function(c) sum(c=="Case.Fatality_Ratio"))
count_teenbirth<- ldply(prtdescombined,function(c) sum(c=="Teen Birth Rate"))
count_overcrowding<- ldply(prtdescombined,function(c) sum(c=="Overcrowding"))

count_lessthan18<- ldply(prtdescombined,function(c) sum(c=="% less than 18 years of age"))
count_notproficientinenglish<- ldply(prtdescombined,function(c) sum(c=="% Not Proficient in English"))
count_pediatricasthma<- ldply(prtdescombined,function(c) sum(c=="PediatricAsthma"))
count_uninsured1<- ldply(prtdescombined,function(c) sum(c=="% Uninsured_1"))
count_uninsured2<- ldply(prtdescombined,function(c) sum(c=="% Uninsured_2"))

count_meanwintertemp<- ldply(prtdescombined,function(c) sum(c=="mean_winter_temp"))
count_meansummertemp<- ldply(prtdescombined,function(c) sum(c=="mean_summer_temp"))
count_long<- ldply(prtdescombined,function(c) sum(c=="Long_"))
count_olderpecent<- ldply(prtdescombined,function(c) sum(c=="older_pecent"))
count_midpecent<- ldply(prtdescombined,function(c) sum(c=="mid_pecent"))

count_yearspotentiallifelostrate<- ldply(prtdescombined,function(c) sum(c=="Years of Potential Life Lost Rate"))
count_lowbirthweight<- ldply(prtdescombined,function(c) sum(c=="% Low Birthweight"))
count_smokers<- ldply(prtdescombined,function(c) sum(c=="% Smokers"))
count_pctobesity<- ldply(prtdescombined,function(c) sum(c=="pct_obesity"))
count_physicallyinactive<- ldply(prtdescombined,function(c) sum(c=="% Physically Inactive"))

count_excessivedrinking<- ldply(prtdescombined,function(c) sum(c=="% Excessive Drinking"))
count_drivingalcohol<- ldply(prtdescombined,function(c) sum(c=="% Driving Deaths with Alcohol Involvement"))
count_teenbirthhispanic<- ldply(prtdescombined,function(c) sum(c=="Teen Birth Rate (Hispanic)"))
count_teenbirthwhite<- ldply(prtdescombined,function(c) sum(c=="Teen Birth Rate (White)"))
count_incidencerate<- ldply(prtdescombined,function(c) sum(c=="Incidence_Rate"))

#created a new data frame with the determinant name and the number of occurences
#manually inputting name and value leads to many errors and loss of efficiency
significantdeterminants <- data.frame (determinants  = c("Confirmed", "Active", "Case Fatality Rate","Teen Birth Rate","Overcrowding","% less than 18 years of age","% Not Proficient in English","Pediatric Asthma","% Uninsured 1","% Uninsured 2","Mean Winter Temperature","Mean Summer Temperature","Long_","Older Percent","Mid Percent","Years of Potential Life Lost Rate","% Low Birthweight","% Smokers","pct_obesity","% Physically Inactive","% Excessive Drinking","% Driving Deaths with Alcohol Involvement","Teen Birth Rate (Hispanic)","Teen Birth Rate (White)","Incidence Rate"),
                                       frequency = c("10", "8", "21", "2", "3", "4", "6", "4", "5","3","3","4","7","3","3","1","4","2","2","1","3","1","1","1","22")
                                       #prtordes=  
                                         )

#change frequency variable into a number rather than a factor
significantdeterminants$frequency <- as.numeric(as.character(significantdeterminants$frequency))

#bar graph of determinants and its frequency
p <- ggplot(significantdeterminants, aes(x=determinants, y=frequency)) + 
  geom_bar(stat = "identity") +
  xlab("Significant Determinants") + ylab("Frequency") + ggtitle("Frequency of Significant Determinants")
p + coord_flip()


```