---
title: "ahns3ProtoNotebook"
output: html_document
---

from ProtoNotebook
```{r echo = F, results = 'hide',  warning=FALSE, message=FALSE}

#### Library and Data Imports ####
## Load essential R packages
source("Source.R")
## Load in model outputs per state:
source("load_model_output.R")

```

from ProtoNotebook
```{r echo = F}
  
# Normalize MRRs to MR by subtracting 1 and dividing by stdev for each state... output as table

  state_c <- as.data.frame(states.all_c)
  coefs <- state_c$coefficients
  
  coefs_clean <- c("hispanic", "pct_blk", "pct_asian", "pct_white", "pct_native", "pct_age65", "medhouseholdincome", "pct_obesity", "pct_diabetes", "LungCancer", "COPD", "AdultAsthma", "PediatricAsthma", "All.Cause.death_rate", "state")
  states <- c("AL", "AR", "AZ", "CA", "CT","CO", "DE", "FL", "GA", "IA", "ID", "IL", "IN", "KS", "KY",
            "LA", "MA", "MD", "ME", "MI", "MN", "MO", "MS", "MT", "NC", "ND", "NE", "NH", "NM", "NJ", "NV", 
            "NY", "OH", "OK", "OR", "PA", "SC", "SD", "TN", "TX", "UT", "VA", "VT", "WA", "WI", "WV", "WY")
  
  # Split the data on state
  statesplit <- split(model_input, model_input$state)

  # Ignore states with less than 2 counties
  for (name in names(statesplit)) {
    if (nrow(statesplit[[name]]) < 2){
      statesplit <- statesplit[names(statesplit) != name]
    }
  }
  
  state_MRs <- array(dim = c(length(states),length(coefs)))
  
  
  for (i in 1:length(names(statesplit))) {
    name = names(statesplit)[i]
    # Ignore states having issues
    if (name %in% c("AZ", "CT", "DE", "RI"))
      next
    state_data <- statesplit[[name]]
      
    state_data <- subset(state_data, select = c(fips, Deaths, hispanic, pct_blk, pct_asian, pct_white, pct_native, medhouseholdincome, pct_obesity, pct_age65, pct_diabetes, LungCancer, AdultChronicLungDisease, COPD, AdultAsthma, PediatricAsthma,  Despair.death_rate, All.Cause.death_rate, Cardiovascular.death_rate, population))
    
    b <- paste(name, ".summary", sep= "")
    model_output <- eval(as.name(b))
    this_state_Cs <- model_output$coefficients[,1]
    names <- names(this_state_Cs)
    this_state_Cs <- unname(this_state_Cs)
    
    if (!(name %in% states)) {
      print(name)
      next
    }
    
    this_state_MRs <- array(dim = c(length(coefs)))
    
    for ( j in 1:length(names)) {
      coef = names[j] 
      sdev <- case_when (
        coef == "scale(hispanic)"                ~ sd(state_data$hispanic, na.rm = TRUE) ,
        coef == "scale(pct_blk)"                 ~ sd(state_data$pct_blk, na.rm = TRUE) ,
        coef == "scale(pct_asian)"               ~ sd(state_data$pct_asian, na.rm = TRUE) ,
        coef == "scale(pct_white)"               ~ sd(state_data$pct_white, na.rm = TRUE) ,
        coef == "scale(pct_native)"              ~ sd(state_data$pct_native, na.rm = TRUE) ,
        coef == "scale(pct_age65)"               ~ sd(state_data$pct_age65, na.rm = TRUE) ,
        coef == "scale(log(medhouseholdincome))" ~ sd(state_data$medhouseholdincome, na.rm = TRUE) ,
        coef == "scale(pct_obesity)"             ~ sd(state_data$pct_obesity, na.rm = TRUE) ,
        coef == "scale(pct_diabetes)"            ~ sd(state_data$pct_diabetes, na.rm = TRUE) ,
        coef == "scale(LungCancer)"              ~ sd(state_data$LungCancer, na.rm = TRUE) ,
        coef == "scale(COPD)"                    ~ sd(state_data$COPD, na.rm = TRUE) ,
        coef == "scale(AdultAsthma)"             ~ sd(state_data$AdultAsthma, na.rm = TRUE) ,
        coef == "scale(PediatricAsthma)"         ~ sd(state_data$PediatricAsthma, na.rm = TRUE) ,
        coef == "scale(All.Cause.death_rate)"    ~ sd(state_data$All.Cause.death_rate, na.rm = TRUE),
        TRUE                                     ~ -100
      )
      if (!is.na(sdev) && sdev != -100) {
        this_state_MRs[which(coefs %in% c(coef))] = (this_state_Cs[j]-1.0)/sdev
      }
    }
    if (length(state_MRs[which(states %in% c(name)),]) != length(this_state_MRs)) {
      #print(length(state_MRs[which(states %in% c(name)),]))
      #print(length(this_state_MRs))
      stop()
    } else {
      state_MRs[which(states %in% c(name)),] = this_state_MRs
    }
  }
  
  
  t0 <- as.data.frame(state_MRs)
  t1 <- as_tibble(t0)
  
  colnames(t1) <- as.character(coefs)
  t2 <- t1 %>% 
    mutate(state = states)
  
  saveRDS(t2, "states_normalize.rds")


```

from ProtoNotebook
```{r echo = F}
  
    nat <- national
    coefs <- row.names(nat$coefficients)
  
    mo_in <-subset(model_input, select = c(fips, Deaths, hispanic, pct_blk, pct_asian, pct_white, pct_native, medhouseholdincome, pct_obesity, pct_age65, pct_diabetes, LungCancer, AdultChronicLungDisease, COPD, AdultAsthma, PediatricAsthma,  Despair.death_rate, All.Cause.death_rate, Cardiovascular.death_rate, population)) 
  
    nat_Cs <- nat$coefficients[,1]
    names <- names(nat_Cs)
    
    nat_MRs <- array(dim = c(length(coefs)))
    
    for ( j in 1:length(names)) {
      coef = names[j] 
      sdev <- case_when (
        coef == "scale(hispanic)"                ~ sd(mo_in$hispanic, na.rm = TRUE) ,
        coef == "scale(pct_blk)"                 ~ sd(mo_in$pct_blk, na.rm = TRUE) ,
        coef == "scale(pct_asian)"               ~ sd(mo_in$pct_asian, na.rm = TRUE) ,
        coef == "scale(pct_white)"               ~ sd(mo_in$pct_white, na.rm = TRUE) ,
        coef == "scale(pct_native)"              ~ sd(mo_in$pct_native, na.rm = TRUE) ,
        coef == "scale(pct_age65)"               ~ sd(mo_in$pct_age65, na.rm = TRUE) ,
        coef == "scale(log(medhouseholdincome))" ~ sd(mo_in$medhouseholdincome, na.rm = TRUE) ,
        coef == "scale(pct_obesity)"             ~ sd(mo_in$pct_obesity, na.rm = TRUE) ,
        coef == "scale(pct_diabetes)"            ~ sd(mo_in$pct_diabetes, na.rm = TRUE) ,
        coef == "scale(LungCancer)"              ~ sd(mo_in$LungCancer, na.rm = TRUE) ,
        coef == "scale(COPD)"                    ~ sd(mo_in$COPD, na.rm = TRUE) ,
        coef == "scale(AdultAsthma)"             ~ sd(mo_in$AdultAsthma, na.rm = TRUE) ,
        coef == "scale(PediatricAsthma)"         ~ sd(mo_in$PediatricAsthma, na.rm = TRUE) ,
        coef == "scale(All.Cause.death_rate)"    ~ sd(mo_in$All.Cause.death_rate, na.rm = TRUE),
        TRUE                                     ~ -100
      )
      if (!is.na(sdev) && sdev != -100) {
        nat_MRs[which(coefs %in% c(coef))] = (nat_Cs[j]-1.0)/sdev
      }
    }

    t1 <- as_tibble(nat_MRs)
    
    t2 <- t1 %>%
      mutate(coefficients = names)
    saveRDS(t2, "national_normalize.rds")

```

from ProtoNotebook
```{r echo = F}

  # make GWAS per state per 305 vars
  # rerun state models with new variables

    library("leaflet")
    # vars to pick from 
 #   var_i = "Intercept"  "hispanic"  "pct_blk"  "pct_asian"  "pct_white"  "pct_native"  "q_popdensity 2" "q_popdensity 3" "q_popdensity 4" "q_popdensity 5" "medhouseholdincome"   "pct_obesity"  "pct_age65"  "pct_diabetes"  "LungCancer"  "COPD"  "AdultAsthma"  "PediatricAsthma"  "All.Cause.death_rate" 
    var_i = as.name("pct_blk") 
    #state$state_heat$pct_blk
    #colors <- c("grey","#426C85","#67a9cf","#d1e5f0","#f7f7f7","#fddbc7","#ef8a62","#b2182b")
    colors <- c("blue", "grey", "red")
    #bins <- c(5, 2, 1, .2, -.2, -1, -2, -5,-Inf)
    bins <- c(-0.25, 0.25, 0.75, 1.25)
    pal2 <- leaflet::colorBin(colors, domain = state$state_heat$pct_blk, bins = bins, reverse=FALSE)
    labels2 <- sprintf(
      "<strong>%s</strong><br/>
      Mortality Rate P-val: %.2g",
      colnames(state_p), state$state_heat$pct_blk
    ) %>% lapply(htmltools::HTML)
    
    leaflet(states.shapes) %>%
      setView(-96, 37.8, 4) %>% 
      addPolygons(
        fillColor = ~pal2(state$state_heat$pct_blk),
        weight = 2,
        opacity = 1,
        color = "white",
        dashArray = "3",
        fillOpacity = 0.7,
        highlight = highlightOptions(
          weight = 5,
          color = "#666",
          dashArray = "",
          fillOpacity = 0.7,
          bringToFront = TRUE),
        label = labels2,
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>% 
      addLegend(pal = pal2, 
                values = ~state$state_heat$pct_blk, 
                opacity = 0.7, 
                title = paste("Mortality Rate  Ratio per " , var_i, sep = ""),
                position = "bottomright"
                ) %>%
      addProviderTiles("MapBox", options = providerTileOptions(
        id = "mapbox.light",
        accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
```

from ProtoNotebook
```{r echo = F}

  # use GWAS_ADJ_P and GWAS_MRR to say for which states there are significant protective and destructive variables

  s = ""
  for (state in colnames(GWAS_MRR)) {
    s <- paste(s, state, ": ", sep = "")
    
    prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          #des <- c(des, GWAS_MRR[[state]][itr])
          des <- c(des, itr)
        } else {
          #prt <- c(prt, GWAS_MRR[[state]][itr])
          prt <- c(prt, itr)
        }
      }
    }
  
    if (length(prt) > 1) {
      s <- paste(s, "protective variables include: ", sep = "")
      for ( i  in 2:length(prt) ) {
        if (i != length(prt)) {
          s <- paste(s, colnames(model_input)[prt[i]], ", ", sep = "")
        } else {
          s <- paste(s, colnames(model_input)[prt[i]], " ", sep = "")
        }
      }
    } else {
      s <- paste(s, "no protective variables; ", sep = "")
    }
    
    if (length(des) > 1) {
      s <- paste(s, "destructive variables include: ", sep = "")
      for ( i  in 2:length(des) ) {
        if (i != length(des)) {
          s <- paste(s, colnames(model_input)[des[i]], ", ", sep = "")
        } else {
          s <- paste(s, colnames(model_input)[des[i]], "", sep = "")
        }
      }
    } else {
      s <- paste(s, "no destructive variables;", sep = "")
    }
    
    s <- paste(s, "\n", sep ="")
  }

  cat(s)


```

Start of Personal Contribution

Alabama
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
#select state  
  state = "AL"
  state
#sorts determinants as protective or destructive
   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

#create data frame    
    dataAL <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataAL <- dataAL %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataAL$y <- factor(dataAL$y, levels = dataAL$y)

#round MRR to 2 decimal places
x <- dataAL$x
x_num<-round(x,digits=2)
dataAL$x_round = x_num

#plot
p<- ggplot(dataAL, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_round), vjust=0.5,color="black", size=3.5)
}
p
ggsave("AL_desprt.png")
```

Alaska (not enough)

Arizona (MAKE LOOK NEATER)
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "AZ"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataAZ <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataAZ <- dataAZ %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataAZ$y <- factor(dataAZ$y, levels = dataAZ$y)

#plot
x <- dataAZ$x
x_num<-round(x,digits=2)
dataAZ$x_round = x_num

p<-ggplot(dataAZ, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=5, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x), vjust=0.5,color="black", size=3.5)
}
p
ggsave("AZ_desprt.png")
```

Arkansas
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "AR"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataAR <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataAR <- dataAR %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataAR$y <- factor(dataAR$y, levels = dataAR$y)

#plot
x <- dataAR$x
x_num<-round(x,digits=2)
dataAR$x_round = x_num

p<-ggplot(dataAR, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("AR_desprt.png")
```

California
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "CA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataCA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataCA <- dataCA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataCA$y <- factor(dataCA$y, levels = dataCA$y)

# dataCApos <- dataCA[ which(dataCA$'Effect on MRR' =='Protective'), ]
# dataCApos[sapply(dataCApos, is.numeric)] <- dataCApos[sapply(dataCApos, is.numeric)] * -1
# dataCA <-rbind(dataCA, dataCApos)
# dataCA<-dataCA[!(dataCA$x>= 0 | dataCA$`Effect on MRR`=="Protective"),]

#plot
x <- dataCA$x
x_num<-round(x,digits=2)
dataCA$x_round = x_num

p<-ggplot(dataCA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("CA_desprt.png")
```

Colorado
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "CO"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataCO <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataCO <- dataCO %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataCO$y <- factor(dataCO$y, levels = dataCO$y)

#plot
x <- dataCO$x
x_num<-round(x,digits=2)
dataCO$x_round = x_num

p<-ggplot(dataCO, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("CO_desprt.png")
```

Connecticut (Insufficient data or no protective or destructive variables in this state)
Delaware (Insufficient data or no protective or destructive variables in this state)

Florida
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "FL"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataFL <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataFL <- dataFL %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataFL$y <- factor(dataFL$y, levels = dataFL$y)

#plot
x <- dataFL$x
x_num<-round(x,digits=2)
dataFL$x_round = x_num

p<-ggplot(dataFL, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("FL_desprt.png")
```

Georgia
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "GA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataGA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataGA <- dataGA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataGA$y <- factor(dataGA$y, levels = dataGA$y)

#plot
x <- dataGA$x
x_num<-round(x,digits=2)
dataGA$x_round = x_num

p<-ggplot(dataGA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("GA_desprt.png")
```

Hawaii (Insufficient data or no protective or destructive variables in this state)

Idaho  
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "ID"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataID <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataID <- dataID %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataID$y <- factor(dataID$y, levels = dataID$y)

#plot
x <- data$x
x_num<-round(x,digits=2)
data$x_round = x_num

ggplot(data, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}

ggsave("ID_desprt.png")
```

Illinois
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "IL"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataIL <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataIL <- dataIL %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataIL$y <- factor(dataIL$y, levels = dataIL$y)

#plot
x <- dataIL$x
x_num<-round(x,digits=2)
dataIL$x_round = x_num

p<-ggplot(dataIL, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("IL_desprt.png")
```

Indiana
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "IN"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataIN <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataIN <- dataIN %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataIN$y <- factor(dataIN$y, levels = dataIN$y)

#plot
x <- dataIN$x
x_num<-round(x,digits=2)
dataIN$x_round = x_num

p<-ggplot(dataIN, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("IN_desprt.png")
```

Iowa
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "IA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataIA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataIA <- dataIA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataIA$y <- factor(dataIA$y, levels = dataIA$y)

#plot
x <- dataIA$x
x_num<-round(x,digits=2)
dataIA$x_round = x_num

p<-ggplot(dataIA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("IA_desprt.png")
```

Kansas
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "KS"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataKS <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataKS <- dataKS %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataKS$y <- factor(dataKS$y, levels = dataKS$y)

#plot
x <- dataKS$x
x_num<-round(x,digits=2)
dataKS$x_round = x_num

p<-ggplot(dataKS, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("KS_desprt.png")
```

Kentucky
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "KY"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataKY <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataKY <- dataKY %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataKY$y <- factor(dataKY$y, levels = dataKY$y)

#plot
x <- dataKY$x
x_num<-round(x,digits=2)
dataKY$x_round = x_num

p<-ggplot(dataKY, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("KY_desprt.png")
```

Louisiana
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "LA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataLA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataLA <- dataLA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataLA$y <- factor(dataLA$y, levels = dataLA$y)

#plot
x <- dataLA$x
x_num<-round(x,digits=2)
dataLA$x_round = x_num

p<-ggplot(dataLA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("LA_desprt.png")
```

Maine (not enough)
Maryland (not enough)
Massachusetts (not enough)

Michigan
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "MI"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataMI <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataMI <- dataMI %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataMI$y <- factor(dataMI$y, levels = dataMI$y)

#plot
x <- dataMI$x
x_num<-round(x,digits=2)
dataMI$x_round = x_num

p<-ggplot(dataMI, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("MI_desprt.png")
```

Minnesota
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "MN"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataMN <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataMN <- dataMN %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataMN$y <- factor(dataMN$y, levels = dataMN$y)

#plot
x <- dataMN$x
x_num<-round(x,digits=2)
dataMN$x_round = x_num

p<-ggplot(dataMN, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("MN_desprt.png")
```

Mississippi
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "MS"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataMS <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataMS <- dataMS %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataMS$y <- factor(dataMS$y, levels = dataMS$y)

#plot
x <- dataMS$x
x_num<-round(x,digits=2)
dataMS$x_round = x_num

p<-ggplot(dataMS, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("MS_desprt.png")
```

Missouri
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "MO"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataMO <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataMO <- dataMO %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataMO$y <- factor(dataMO$y, levels = dataMO$y)

#plot
x <- dataMO$x
x_num<-round(x,digits=2)
dataMO$x_round = x_num

p<-ggplot(dataMO, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("MO_desprt.png")
```

Montana
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "MT"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataMT <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataMT <- dataMT %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataMT$y <- factor(dataMT$y, levels = dataMT$y)

#plot
x <- dataMT$x
x_num<-round(x,digits=2)
dataMT$x_round = x_num

p<-ggplot(dataMT, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("MT_desprt.png")
```

Nebraska
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "NE"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataNE <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataNE <- dataNE %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataNE$y <- factor(dataNE$y, levels = dataNE$y)

#plot
x <- dataNE$x
x_num<-round(x,digits=2)
dataNE$x_round = x_num

p<-ggplot(dataNE, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("NE_desprt.png")
```

Nevada (not enough)
New Hampshire (not enough)
New Jersey (not enough)

New Mexico
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "NM"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataNM <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataNM <- dataNM %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataNM$y <- factor(dataNM$y, levels = dataNM$y)

#plot
x <- dataNM$x
x_num<-round(x,digits=2)
dataNM$x_round = x_num

p<-ggplot(dataNM, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("NM_desprt.png")
```

New York
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "NY"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataNY <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataNY <- dataNY %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataNY$y <- factor(dataNY$y, levels = dataNY$y)

#plot
x <- dataNY$x
x_num<-round(x,digits=2)
dataNY$x_round = x_num

p<-ggplot(dataNY, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("NY_desprt.png")
```

North Carolina
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "NC"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataNC <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataNC <- dataNC %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataNC$y <- factor(dataNC$y, levels = dataNC$y)

#plot
x <- dataNC$x
x_num<-round(x,digits=2)
dataNC$x_round = x_num

p<-ggplot(dataNC, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("NC_desprt.png")
```


North Dakota
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "ND"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataND <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataND <- dataND %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataND$y <- factor(dataND$y, levels = dataND$y)

#plot
x <- dataND$x
x_num<-round(x,digits=2)
dataND$x_round = x_num

p<-ggplot(dataND, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("ND_desprt.png")
```

Ohio
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "OH"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataOH <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataOH <- dataOH %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataOH$y <- factor(dataOH$y, levels = dataOH$y)

#plot
x <- dataOH$x
x_num<-round(x,digits=2)
dataOH$x_round = x_num

p<-ggplot(dataOH, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("OH_desprt.png")
```

Oklahoma
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = ""
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataOK <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataOK <- dataOK %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataOK$y <- factor(dataOK$y, levels = dataOK$y)

#plot
x <- dataOK$x
x_num<-round(x,digits=2)
dataOK$x_round = x_num

p<-ggplot(dataOK, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("OK_desprt.png")
```

Oregan 
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "OR"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataOR <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataOR <- dataOR %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataOR$y <- factor(dataOR$y, levels = dataOR$y)

#plot
x <- dataOR$x
x_num<-round(x,digits=2)
dataOR$x_round = x_num

p<-ggplot(dataOR, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("OR_desprt.png")
```

Pennsylvania
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "PA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataPA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataPA <- dataPA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataPA$y <- factor(dataPA$y, levels = dataPA$y)

#plot
x <- dataPA$x
x_num<-round(x,digits=2)
dataPA$x_round = x_num

p<- ggplot(dataPA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_round), vjust=0.5,color="black", size=3.5)

ggplot(dataPA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +  
  scale_color_manual(values = c("#bd0026", "#253494")) +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle("PA Protective and Destructive Variables") +
  geom_text(aes(label=x_round, colour=x_round<1), vjust=0.5,color="black", size=3.5,nudge_x = -0.15)


}
p
ggsave("PA_desprt.png")
```

Rhode Island (not enough)

South Carolina
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "SC"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataSC <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataSC <- dataSC %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataSC$y <- factor(dataSC$y, levels = dataSC$y)

#plot
x <- dataSC$x
x_num<-round(x,digits=2)
dataSC$x_round = x_num

p<-ggplot(dataSC, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("SC_desprt.png")
```

South Dakota
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "SD"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataSD <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataSD <- dataSD %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataSD$y <- factor(dataSD$y, levels = dataSD$y)

#plot
x <- dataSD$x
x_num<-round(x,digits=2)
dataSD$x_round = x_num

p<-ggplot(dataSD, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("SD_desprt.png")
```

Tennessee
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "TN"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataTN <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataTN <- dataTN %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataTN$y <- factor(dataTN$y, levels = dataTN$y)

#plot
x <- dataTN$x
x_num<-round(x,digits=2)
dataTN$x_round = x_num

p<-ggplot(dataTN, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("TN_desprt.png")
```

Texas
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "TX"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataTX <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataTX <- dataTX %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataTX$y <- factor(dataTX$y, levels = dataTX$y)

#plot
x <- dataTX$x
x_num<-round(x,digits=2)
dataTX$x_round = x_num

p<-ggplot(dataTX, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("TX_desprt.png")
```

Utah (not enough)
Vermont(not enough)

Virginia
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "VA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataVA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataVA <- dataVA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataVA$y <- factor(dataVA$y, levels = dataVA$y)

#plot
x <- dataVA$x
x_num<-round(x,digits=2)
dataVA$x_round = x_num

p<-ggplot(dataVA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("VA_desprt.png")
```

Washington
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "WA"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataWA <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataWA <- dataWA %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataWA$y <- factor(dataWA$y, levels = dataWA$y)

#plot
x <- dataWA$x
x_num<-round(x,digits=2)
dataWA$x_round = x_num

p<-ggplot(dataWA, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("WA_desprt.png")
```

West Virginia
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "WV"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataWV <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataWV <- dataWV %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataWV$y <- factor(dataWV$y, levels = dataWV$y)

#plot
x <- dataWV$x
x_num<-round(x,digits=2)
dataWV$x_round = x_num

p<-ggplot(dataWV, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("WV_desprt.png")
```


Wisconsin
```{r echo = F}
  # Libraries
  library(ggplot2)
# Create data

for (state in colnames(GWAS_MRR)) {
  
  state = "WI"
  state

   prt <- c(NA)
    des <- c(NA)
    for (itr in 1:length(GWAS_ADJ_P[[state]])) {
      if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
        if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
          des <- c(des, itr)
        } else {
          prt <- c(prt, itr)
        }
      }
    }
    #prt[2:length(prt)]
    vals  <- c(NA)
    names <- c(NA)
    if (length(prt) > 1){
      names <- colnames(model_input)[prt[2:length(prt)]]
      vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
    }
    if (length(des) > 1){
      names <- c(names, colnames(model_input)[des[2:length(des)]])
      vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
    }
    
    if (length(names) == 1) {
      print("Insufficient data or no protective or destructive variables in this state.")
      next
    }

    
    dataWI <- data.frame(
      y=names[2:length(names)], 
      x=vals[2:length(names)]
    )
    
    #view(data)
    title <- paste(state, " Protective and Destructive Variables", sep = "")
    dataWI <- dataWI %>% 
      mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
     
    dataWI$y <- factor(dataWI$y, levels = dataWI$y)

#plot
x <- dataWI$x
x_num<-round(x,digits=2)
dataWI$x_round = x_num

p<-ggplot(dataWI, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=12, alpha=0.9 ) +      
  scale_color_manual(values = c("#bd0026", "#253494")) +
  #      geom_point() +
  ylab("Interested Variable") +
  xlab("MRR of Interested Variable") +
  ggtitle(title) +
  geom_text(aes(label=x_num), vjust=0.5,color="black", size=3.5)
}
p
ggsave("WI_desprt.png")
```

National GWAS
GWAS_MRR
GWAS_ADJ_P

```{r echo = F}
library(ggplot2)

##National Determinants
#data from GWAS_ADJ_P and GWAS_MRR
GWAS_ADJ_P
#remove rows 1-14 
GWAS_ADJ_P_interested <- GWAS_ADJ_P[-c(1:14), ]
#GWAS_ADJ_P_t<-t(GWAS_ADJ_P_interested)
#convert to data frame
GWAS_ADJ_P_t <- as.data.frame(t(GWAS_ADJ_P_interested))
#find significant determinants and create data frame with them
GWAS_ADJ_P_signficant <- subset(GWAS_ADJ_P_t,  Interested_Variable < 0.05)
#GWAS_ADJ_P_signficant <- subset(GWAS_ADJ_P_signficant,  Interested_Variable > 0)
#rownames(GWAS_ADJ_P_t)

GWAS_MRR
#remove rows 1-14
GWAS_MRR_interested <- GWAS_MRR[-c(1:14), ]
#convert to data frame
GWAS_MRR_t <- as.data.frame(t(GWAS_MRR_interested))

#merge GWAS_ADJ and GWAS_MRR data
GWAS_data <- merge(GWAS_ADJ_P_signficant, GWAS_MRR_t, by = 0) 
#mutliply GWAS_MRR data by 100
GWAS_data$MRRX100 <- GWAS_data$Interested_Variable.y * 100 
GWAS_data <- GWAS_data[-c(7),] 

#convert MRRX100 as numeric and Row.names as characters
GWAS_data$MRRX100 <- as.numeric(as.character(GWAS_data$MRRX100))
GWAS_data
GWAS_data$Row.names <- as.character(GWAS_data$Row.names)

GWAS_data$Row.names <- as.character(GWAS_data$Row.names)
GWAS_data$Row.names[GWAS_data$Row.names == "Average Daily PM2.5"] <- "Avg. Daily Air Pollution (PM2.5)"
GWAS_data$Row.names[GWAS_data$Row.names == "Average Number of Physically Unhealthy Days"] <- "Avg. Numer of Physically Unhealthy Days"
GWAS_data$Row.names[GWAS_data$Row.names == "Cancer.death_rate"] <- "Cancer Death Rate"
GWAS_data$Row.names[GWAS_data$Row.names == "% Vaccinated"] <- "% Flu Vaccinated Medicare FFS"
GWAS_data$Row.names[GWAS_data$Row.names == "Suicide Rate (Age-Adjusted)"] <- "Age-Adjusted Suicide Rate"
GWAS_data$Row.names[GWAS_data$Row.names == "Average Grade Performance"] <- "Avg. Grade Performance"

#orders data from highest to lowest value
GWAS_data$Row.names <- factor(GWAS_data$Row.names, levels = GWAS_data$Row.names[order(GWAS_data$MRRX100)])

#round MRRX100 to 2 decimal places for better viewing
MRRX100 <- GWAS_data$MRRX100
MRRX100_num<-round(MRRX100,digits=2)
GWAS_data$MRRX100_round = MRRX100_num

#plot
# ggplot(GWAS_data, aes(x=Row.names, y=MRRX100)) +
#    ggtitle("Significant National Social Determinants")+
#    xlab("Significant Determinants") +
#    ylab("Mortality Rate Ratio") +
#    geom_bar(stat = "identity",aes(fill=MRRX100<0)) +
#    coord_flip()+
#    theme(legend.position='none')+
#    scale_fill_manual(values = c("#bd0026", "#253494"))+
#    geom_text(aes(label=MRRX100_round), vjust=0.5,color="black", size=3.5, nudge_y = 2.75)

 ggplot(GWAS_data, aes(x=Row.names, y=MRRX100)) +
   ggtitle("Significant National Social Determinants")+
   xlab("Significant Determinants") +
   ylab("Mortality Rate Ratio") +
   geom_bar(stat = "identity",aes(fill=MRRX100<0)) +
   coord_flip()+
   theme(legend.position='none')+
   scale_fill_manual(values = c("#bd0026", "#253494"))+
   geom_text(aes(label=MRRX100_round, colour =MRRX100 <0), vjust=0.5, size=3.5, nudge_y = 3)+
   scale_colour_manual(values=c("#000000","#FFFFFF"))

ggsave("national_sd.png")
```

```{r}
##National Coefficients
#Output Wald-test p-values
high_risk_p <- as.data.frame(summary(high.risk.model)[10]$coefficients[2:25,4])
high_risk_p_signficant <- subset(high_risk_p,  high_risk_p$`summary(high.risk.model)[10]$coefficients[2:25, 4]` < 0.05)

#Output MRR
high_risk_MRR <- as.data.frame(exp(summary(high.risk.model)[10]$coefficients[2:25,1]))

#merge high_risk_p and high_rish_mrr
high_risk_data <- merge(high_risk_p_signficant, high_risk_MRR, by = 0) 
#mutliply GWAS_MRR data by 100
high_risk_data$MRRX100 <- high_risk_data$`exp(summary(high.risk.model)[10]$coefficients[2:25, 1])` * 100 

#convert MRRX100 as numeric and Row.names as characters
high_risk_data$MRRX100 <- as.numeric(as.character(high_risk_data$MRRX100))
high_risk_data$Row.names <- as.character(high_risk_data$Row.names)

#change coefficient names for readibility
high_risk_data$Row.names <- as.character(high_risk_data$Row.names)
high_risk_data$Row.names[high_risk_data$Row.names == "scale(date_since_mask)"] <- "Days Since Mask Required"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(AdultAsthma)"] <- "% Adult Asthma"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(date_since)"] <- "Days Since First Infection"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(education)"] <- "% with less than High-School Education"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(hispanic)"] <- "% Hispanic in County"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(log(medhouseholdincome))"] <- "Median Household Income"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(LungCancer)"] <- "% with Lung Cancer"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_asian)"] <- "% Asian"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_blk)"] <- "% African American"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_native)"] <- "% Native American"

#orders data from highest to lowest value
high_risk_data$Row.names <- factor(high_risk_data$Row.names, levels = high_risk_data$Row.names[order(high_risk_data$MRRX100)])

#round MRRX100 to 2 decimal places for better viewing
hrmMRRX100 <- high_risk_data$MRRX100
hrmMRRX100_minus <- hrmMRRX100 - 100
high_risk_data$MRRX100 <- hrmMRRX100_minus
hrmMRRX100_num<-round(hrmMRRX100_minus,digits=2)
high_risk_data$MRRX100_round = hrmMRRX100_num

ggplot(high_risk_data, aes(x=Row.names, y=MRRX100)) +
   ggtitle("Significant National Coefficients")+
   xlab("Significant Coefficients") +
   ylab("Mortality Rate Ratio") +
   geom_bar(stat = "identity",aes(fill=MRRX100<0)) +
   coord_flip()+
   theme(legend.position='none')+
   scale_fill_manual(values = c("#bd0026", "#253494"))+
   geom_text(aes(label=MRRX100_round, colour =MRRX100_round <0), vjust=0.5, size=3.5, nudge_y = 7.0)+
   scale_colour_manual(values=c("#000000","#FFFFFF"))

ggsave("national_coefficients.png")
```


Combined Graph of Coefficients and Determinants(to be used in COVIDMINDER)
```{r}
library(dplyr)
library(ggplot2)

##National Determinants
#data from GWAS_ADJ_P and GWAS_MRR
GWAS_ADJ_P
#remove rows 1-14 
GWAS_ADJ_P_interested <- GWAS_ADJ_P[-c(1:14), ]
#GWAS_ADJ_P_t<-t(GWAS_ADJ_P_interested)
#convert to data frame
GWAS_ADJ_P_t <- as.data.frame(t(GWAS_ADJ_P_interested))
#find significant determinants and create data frame with them
GWAS_ADJ_P_signficant <- subset(GWAS_ADJ_P_t,  Interested_Variable < 0.05)
#GWAS_ADJ_P_signficant <- subset(GWAS_ADJ_P_signficant,  Interested_Variable > 0)
#rownames(GWAS_ADJ_P_t)

GWAS_MRR
#remove rows 1-14
GWAS_MRR_interested <- GWAS_MRR[-c(1:14), ]
#convert to data frame
GWAS_MRR_t <- as.data.frame(t(GWAS_MRR_interested))

#merge GWAS_ADJ and GWAS_MRR data
GWAS_data <- merge(GWAS_ADJ_P_signficant, GWAS_MRR_t, by = 0) 
#mutliply GWAS_MRR data by 100
GWAS_data$MRRX100 <- GWAS_data$Interested_Variable.y * 100 
GWAS_data <- GWAS_data[-c(7),] 

#convert MRRX100 as numeric and Row.names as characters
GWAS_data$MRRX100 <- as.numeric(as.character(GWAS_data$MRRX100))
GWAS_data
GWAS_data$Row.names <- as.character(GWAS_data$Row.names)

GWAS_data$Row.names <- as.character(GWAS_data$Row.names)
GWAS_data$Row.names[GWAS_data$Row.names == "Average Daily PM2.5"] <- "Avg. Daily Air Pollution (PM2.5)"
GWAS_data$Row.names[GWAS_data$Row.names == "Average Number of Physically Unhealthy Days"] <- "Avg. Numer of Physically Unhealthy Days"
GWAS_data$Row.names[GWAS_data$Row.names == "Cancer.death_rate"] <- "Cancer Death Rate"
GWAS_data$Row.names[GWAS_data$Row.names == "% Vaccinated"] <- "% Flu Vaccinated Medicare FFS"
GWAS_data$Row.names[GWAS_data$Row.names == "Suicide Rate (Age-Adjusted)"] <- "Age-Adjusted Suicide Rate"
GWAS_data$Row.names[GWAS_data$Row.names == "Average Grade Performance"] <- "Avg. Grade Performance"

#orders data from highest to lowest value
GWAS_data$Row.names <- factor(GWAS_data$Row.names, levels = GWAS_data$Row.names[order(GWAS_data$MRRX100)])

#round MRRX100 to 2 decimal places for better viewing
MRRX100 <- GWAS_data$MRRX100
MRRX100_num<-round(MRRX100,digits=2)
GWAS_data$MRRX100_round = MRRX100_num


##National Coefficients
#Output Wald-test p-values
high_risk_p <- as.data.frame(summary(high.risk.model)[10]$coefficients[2:25,4])
high_risk_p_signficant <- subset(high_risk_p,  high_risk_p$`summary(high.risk.model)[10]$coefficients[2:25, 4]` < 0.05)

#Output MRR
high_risk_MRR <- as.data.frame(exp(summary(high.risk.model)[10]$coefficients[2:25,1]))

#merge high_risk_p and high_rish_mrr
high_risk_data <- merge(high_risk_p_signficant, high_risk_MRR, by = 0) 
#mutliply GWAS_MRR data by 100
high_risk_data$MRRX100 <- high_risk_data$`exp(summary(high.risk.model)[10]$coefficients[2:25, 1])` * 100 

#convert MRRX100 as numeric and Row.names as characters
high_risk_data$MRRX100 <- as.numeric(as.character(high_risk_data$MRRX100))
high_risk_data$Row.names <- as.character(high_risk_data$Row.names)

#change coefficient names for readibility
high_risk_data$Row.names <- as.character(high_risk_data$Row.names)
high_risk_data$Row.names[high_risk_data$Row.names == "scale(date_since_mask)"] <- "Days Since Mask Required"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(AdultAsthma)"] <- "% Adult Asthma"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(date_since)"] <- "Days Since First Infection"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(education)"] <- "% with less than High-School Education"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(hispanic)"] <- "% Hispanic in County"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(log(medhouseholdincome))"] <- "Median Household Income"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(LungCancer)"] <- "% with Lung Cancer"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_asian)"] <- "% Asian"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_blk)"] <- "% African American"
high_risk_data$Row.names[high_risk_data$Row.names == "scale(pct_native)"] <- "% Native American"

#orders data from highest to lowest value
high_risk_data$Row.names <- factor(high_risk_data$Row.names, levels = high_risk_data$Row.names[order(high_risk_data$MRRX100)])

#round MRRX100 to 2 decimal places for better viewing
hrmMRRX100 <- high_risk_data$MRRX100
hrmMRRX100_minus <- hrmMRRX100 - 100
high_risk_data$MRRX100 <- hrmMRRX100_minus
hrmMRRX100_num<-round(hrmMRRX100_minus,digits=2)
high_risk_data$MRRX100_round = hrmMRRX100_num



##Combinded Coefficients and Determinants
#change column names in high_risk_data dataframe
names(high_risk_data)[names(high_risk_data) == "summary(high.risk.model)[10]$coefficients[2:25, 4]"] <- "Interested_Variable.x"
names(high_risk_data)[names(high_risk_data) == "exp(summary(high.risk.model)[10]$coefficients[2:25, 1])"] <- "Interested_Variable.y"

#combine GWAS_data and high_risk_data
combinded_determinants_data <- rbind(GWAS_data, high_risk_data)

#orders data from highest to lowest value
combinded_determinants_data$Row.names <- factor(combinded_determinants_data$Row.names, levels = combinded_determinants_data$Row.names[order(combinded_determinants_data$MRRX100)])

#plot
ggplot(combinded_determinants_data, aes(x=Row.names, y=MRRX100)) +
   ggtitle("Significant National Determinants")+
   xlab("Significant Determinants") +
   ylab("Mortality Rate Ratio") +
   geom_bar(stat = "identity",aes(fill=MRRX100<0)) +
   coord_flip()+
   theme(legend.position='none')+
   scale_fill_manual(values = c("#bd0026", "#253494"))+
   geom_text(aes(label=MRRX100_round, colour =MRRX100_round <0), vjust=0.5, size=3.0, nudge_y = 6.7)+
   scale_colour_manual(values=c("#000000","#FFFFFF"))

ggsave("combinded_determinants.png")
```

