---
title: "Determinant Visualization for various States"
output: html_notebook
---

## Load library and data

```{r}
# Install and load relevant packages
# install.packages("tidyverse")
library(tidyverse)

# install.packages("ggplot2")
library(ggplot2)

# install.packages("sf")
library(sf)

# install.packages("dplyr")
library(dplyr)

## Load in model outputs per state:
source("Modules/load_model_output.R")
```

## Plot data for a given state
Here, we can specify the two-code label for any state and if the data is sufficient, it will create the relevant plot. We can rename determinants as well which is given by the function before the final code below.

### Function to rename the determinants

```{r}
# Function that renames determinants
renameDeterminants <- function(deter.data){

  deter.data$y[deter.data$y == "Average Daily PM2.5"] <- "Avg. Daily Air Pollution (PM2.5)"
  deter.data$y[deter.data$y == "Average Number of Physically Unhealthy Days"] <- "Avg. Number of Physically Unhealthy Days"
  deter.data$y[deter.data$y == "Cancer.death_rate"] <- "Cancer Death Rate"
  deter.data$y[deter.data$y == "% Vaccinated"] <- "% Influenza Vaccinated Medicare FFS"
  deter.data$y[deter.data$y == "Suicide Rate (Age-Adjusted)"] <- "Age-Adjusted Suicide Rate"
  deter.data$y[deter.data$y == "Average Grade Performance"] <- "Avg. Reading Grade Performance"
  deter.data$y[deter.data$y == "Overcrowding"] <- "% of County with Overcrowded Housing"
  deter.data$y[deter.data$y == "% Uninsured"] <- "% of County Uninsured"
  deter.data$y[deter.data$y == "% Frequent Mental Distress"] <- "% Frequently Mentally Distressed"
  deter.data$y[deter.data$y == "mean_winter_temp"] <- "Mean Winter Temperature"
  deter.data$y[deter.data$y == "mean_summer_temp"] <- "Mean Summer Temperature"
  deter.data$y[deter.data$y == "mean_winter_rm"] <- "Mean Winter Relative Humidity"
  deter.data$y[deter.data$y == "mean_summer_rm"] <- "Mean Summer Relative Humidity"
  deter.data$y[deter.data$y == "PediatricAsthma"] <- "% of County with Pediatric Asthma"
  deter.data$y[deter.data$y == "% less than 18 years of age"] <- "% less than 18 Years of Age"
  deter.data$y[deter.data$y == "Case.Fatality_Ratio"] <- "COVID-19 Case Fatality Ratio"
  deter.data$y[deter.data$y == "Incidence_Rate"] <- "COVID-19 Incidence Rate"
  deter.data$y[deter.data$y == "Active"] <- "Number of Active COVID-19 Cases"
  deter.data$y[deter.data$y == "Lat"] <- "Latitude"
  deter.data$y[deter.data$y == "Long_"] <- "Longitude"
  deter.data$y[deter.data$y == "Confirmed"] <- "Number of Confirmed COVID-19 Cases"
  deter.data$y[deter.data$y == "Deaths"] <- "Number of COVID-19 Deaths"
  deter.data$y[deter.data$y == "Recovered"] <- "Number of People Recovered from COVID-19"
  deter.data$y[deter.data$y == "poverty"] <- "% Living in Poverty"
  deter.data$y[deter.data$y == "popdensity"] <- "Population Density"
  deter.data$y[deter.data$y == "medianhousevalue"] <- "Median House Value"
  deter.data$y[deter.data$y == "pcc_owner_occ"] <- "% Owner-Occupied Housing"
  deter.data$y[deter.data$y == "education"] <- "% with less than High-School Education"
  deter.data$y[deter.data$y == "population"] <- "Overall Population"
  deter.data$y[deter.data$y == "pct_blk"] <- "% African American in County"
  deter.data$y[deter.data$y == "hispanic"] <- "% Hispanic in County"
  deter.data$y[deter.data$y == "pct_asian"] <- "% Asian in County"
  deter.data$y[deter.data$y == "pct_native"] <- "% Native American in County"
  deter.data$y[deter.data$y == "pct_white"] <- "% White in County"
  deter.data$y[deter.data$y == "q_popdensity"] <- "Population Density"
  deter.data$y[deter.data$y == "older_pecent"] <- "% of Population Age 65+"
  deter.data$y[deter.data$y == "young_pecent"] <- "% of Population Ages 0-14"
  deter.data$y[deter.data$y == "prime_pecent"] <- "% of Population Ages 15-44"
  deter.data$y[deter.data$y == "mid_pecent"] <- "% of Population Ages 45-64"
  deter.data$y[deter.data$y == "Average Number of Mentally Unhealthy Days"] <- "Avg. Number of Mentally Unhealthy Days"
  deter.data$y[deter.data$y == "pct_obesity"] <- "% of Adults with Obesity"
  deter.data$y[deter.data$y == "80th Percentile Income"] <- "80th Percentile for Median Household Income"
  deter.data$y[deter.data$y == "20th Percentile Income"] <- "20th Percentile for Median Household Income"
  deter.data$y[deter.data$y == "mean_pm25"] <- "Average Air Quality (PM2.5)"
  deter.data$y[deter.data$y == "pre_covid_deaths"] <- "Deaths before COVID-19 Infection"
  deter.data$y[deter.data$y == "pre_covid_death_rate"] <- "Death Rate before COVID-19 Infection"
  deter.data$y[deter.data$y == "child_deaths"] <- "Number of Children Deaths Under Age of 18"
  deter.data$y[deter.data$y == "infant_deaths"] <- "Number of Infant Deaths"
  deter.data$y[deter.data$y == "pct_diabetes"] <- "% of County with Diabetes"
  deter.data$y[deter.data$y == "# Food Insecure"] <- "# Food Insecurity"
  deter.data$y[deter.data$y == "% Food Insecure"] <- "% Food Insecurity"
  deter.data$y[deter.data$y == "# Limited Access"] <- "# Limited Access to Healthy Foods"
  deter.data$y[deter.data$y == "# Uninsured_1"] <- "# of Adults Under 65 with No Health Insurance"
  deter.data$y[deter.data$y == "% Uninsured_1"] <- "% of Adults Under 65 with No Health Insurance"
  deter.data$y[deter.data$y == "# Uninsured_2"] <- "# of Children with No Health Insurance"
  deter.data$y[deter.data$y == "% Uninsured_2"] <- "% of Children with No Health Insurance"
  deter.data$y[deter.data$y == "Average Grade Performance_1"] <- "Avg. Math Grade Performance"
  deter.data$y[deter.data$y == "Segregation index"] <- "Segregation Index Between Black and White"
  deter.data$y[deter.data$y == "Segregation Index"] <- "Segregation Index Between Non-White and White"
  deter.data$y[deter.data$y == "suicide_deaths"] <- "# of Suicide Deaths"
  deter.data$y[deter.data$y == "Crude Rate"] <- "Not Adjusted Suicide Rate"
  deter.data$y[deter.data$y == "Denominator"] <- "Estimated Number of Juveniles"
  deter.data$y[deter.data$y == "Average Traffic Volume per Meter of Major Roadways"] <- "Avg. Traffic Volume per Meter of Major Roadways"
  deter.data$y[deter.data$y == "pct_age65"] <- "% of Adults Age 65+"
  deter.data$y[deter.data$y == "All.Cause.death_rate"] <- "All Cause Death Rate"
  deter.data$y[deter.data$y == "Assault.death_rate"] <- "Assault Death Rate"
  deter.data$y[deter.data$y == "Cardiovascular.death_rate"] <- "Cardiovascular Disease Death Rate"
  deter.data$y[deter.data$y == "Despair.death_rate"] <- "Despair Death Rate"
  deter.data$y[deter.data$y == "AdultAsthma"] <- "% of County with Adult Asthma"
  deter.data$y[deter.data$y == "COPD"] <- "% of County with COPD"
  deter.data$y[deter.data$y == "AdultChronicLungDisease"] <- "% of County with Adult Chronic Lung Disease"
  deter.data$y[deter.data$y == "LungCancer"] <- "% of County with Lung Cancer"
  
  return (deter.data)
}

```

### The main code to create the plot
It includes a specific vector called **determinants.to.remove** which can be filled with a list of determinants not to be included in the plots.

```{r}

# Specify state's two-letter code for which plot needs to be made
# For example, for Florida, the code is "FL"
state = "FL"

# Specify protective and destructive variables
prt <- c(NA)
des <- c(NA)

# Identify all protective and destructive determinants
for (itr in 1:length(GWAS_ADJ_P[[state]])) {
  if (is.na(GWAS_ADJ_P[[state]][itr]) == FALSE  && GWAS_ADJ_P[[state]][itr] < 0.05 ) {
    if (is.na(GWAS_MRR[[state]][itr]) == FALSE  &&  GWAS_MRR[[state]][itr]  >= 1.0 ) {
      des <- c(des, itr)
    } else {
      prt <- c(prt, itr)
    }
  }
}

# Set the values and names so we can create a dataframe
vals  <- c(NA)
names <- c(NA)

# All protective determinants
if (length(prt) > 1){
  names <- colnames(model_input)[prt[2:length(prt)]]
  vals <- GWAS_MRR[[state]][prt[2:length(prt)]]
}

# All destructive variables
if (length(des) > 1){
  names <- c(names, colnames(model_input)[des[2:length(des)]])
  vals <- c(vals, GWAS_MRR[[state]][des[2:length(des)]])
}
    
if (length(names) == 1) {
  # If we find that there aren't any results, we will not plot the results
  print("Insufficient data or no protective or destructive variables in this state.")
  
} else {
  # We have data to plot
  
  # Create the dataframe
  determinant.data <- data.frame(
    y=names[2:length(names)], 
    x=vals[2:length(names)]
  )
  
  # We set the title
  title <- paste(state, " Protective and Destructive Variables", sep = "")
  
  # Add a new column which specifies if a determinant is protective or destructive
  determinant.data <- determinant.data %>% 
    mutate(`Effect on MRR` = ifelse(x<1,"Protective", "Destructive"))
   
  # Convert the determinant column to a factor
  # determinant.data$y <- factor(determinant.data$y, levels = determinant.data$y)
  
  # Round up the value up to two decimal points
  x_round <- round(determinant.data$x,digits=2)
  determinant.data$x_round <- x_round
  
  # Convert the determinant names column to characters so they can be renamed
  determinant.data$y <- as.character(determinant.data$y)
  
  # Rename determinants
  determinant.data <- renameDeterminants(determinant.data)
  
  # Specify all determinants to be removed inside the vector below
  determinants.to.remove <- c()
  determinant.data <- determinant.data[ !(determinant.data$y %in% determinants.to.remove),]
  
  # Order the determinants based on the destructive/protective values
  determinant.data$y <- factor(determinant.data$y, levels = determinant.data$y[order(determinant.data$x)])
  
  # Create a plot based on the data
  p <- ggplot(determinant.data, aes(x=x, y=y)) +
    geom_segment( aes(x=x, xend=1, y=y, yend=y, color = `Effect on MRR`), size=3, alpha=0.9 ) +      
    scale_color_manual(values = c("#bd0026", "#253494")) +
    ylab("Interested Variable") +
    xlab("MRR of Interested Variable") +
    ggtitle(title) +
    geom_text(aes(label=x_round), vjust=0.5,color="black", size=3.5, nudge_x = .075)+
    geom_segment( aes(x=1, xend=1, y=0, yend = length(vals)), size = 1.0)+
    theme(axis.text = element_text(size = 8))
  
  # Show plot
  print(p)
  
  # Save the plot
  ggsave(paste(state, "_desprt.png", sep=""))
}

```